---
title             : "Measuring Lay Theories of Parenting and Child Development"
shorttitle        : "Measuring Parenting Theories"
author: 
  - name          : "Emily Hembacher"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
  - name          : "Michael C. Frank"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "450 Serra Mall, Stanford, CA 94301"
    email         : "mcfrank@stanford.edu"
affiliation:
  - id            : "1"
    institution   : "Stanford University"
author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["paq.bib"]
figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no
class             : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
---

```{r}
knitr::opts_chunk$set(fig.width = 8, fig.height = 5, echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)
```

```{r load_packages, include = FALSE}
library(tidyverse)
library(psych)
library(langcog) 
library(ggthemes) #plot themes
library(rjson) #for json data
library(lme4) #mixed effects models
library(lmerTest) #nicer lmer output
library(tidyboot) #bootstrapped confidence intervals
library(magrittr)
library(papaja)
library(xtable)
library(gtable)
library(grid)
library(gridExtra)
library(brms)
library(viridis)
library(huxtable)
library(kableExtra)
```


# Survey Construction


## Generation of items

## Revised questionnaire norming

# Survey Validation


##External Validity Study 1: Demographic Factors

```{r}
#get dataframe with subject responses
responses_demo <- read.csv("../cdm_paq.csv", header = TRUE)%>%
  filter(Finished == 1) %>%
  mutate(sid = ResponseId) %>%
  select(sid, Q1:Q28) %>%
  gather("item", "rating", Q1:Q28)
```

```{r}
#get dataframe with survey questions
questions <- read.csv("../cdm_paq.csv", header = TRUE)%>%
  filter(Status == "Response Type") %>%
  select(Q1:Q28) %>%
  gather("item", "sent", Q1:Q28)%>%  
  mutate(sent = stringr::str_replace_all(sent, "’", ""))
```

```{r}
#get dataframe with short sentences
labels_demo <-  read.csv("../analysis/sent_forms_cdm.csv")%>%
  mutate(sent = as.character(sent))
```

```{r}
responses_demo%<>%
  left_join(questions)%>%
  left_join(labels_demo)

#rescore reverse coded items
responses_demo$rating <- as.numeric(responses_demo$rating)
responses_demo$rating[responses_demo$reverse_code == 1] <- 8 -responses_demo$rating[responses_demo$reverse_code == 1]
responses_demo$rating <- responses_demo$rating - 1
```

```{r}
#get dataframe with demographic info
subinfo <- read.csv("../cdm_paq_dem.csv", header = TRUE)%>%
  filter(Finished == "True") %>%
  transmute(sid = ResponseId, ethnicity = Q25.1, parent_ed = Q26.1, parent_age = Q27.1, parent_gender = Q28.1, num_kids = Q29, oldest_kid = Q30, youngest_kid = Q32, only_kid = Q33)%>%
  mutate(parent_age_approx = parent_age,
         parent_ed_years = parent_ed)

#recode parent age to be continuous
subinfo$parent_age_approx <- recode(subinfo$parent_age_approx, "Under 18" = "18", "18 - 24" = "21", "25 - 34" = "30", "35 - 44" = "40", "45 - 54" = "50", "55 - 64" = "60", "65 - 74" = "70")
subinfo$parent_age_approx <- as.numeric(as.character(subinfo$parent_age_approx))

#recode parent ed to be continuous (num years)
subinfo$parent_ed_years <- recode(subinfo$parent_ed_years, "Less than high school" = "12", "High school graduate" = "12", "Some college" = "14", "2 year degree" = "14", "4 year degree" = "16", "Professional degree" = "19", "Doctorate" = "23")
subinfo$parent_ed_years <- as.numeric(as.character(subinfo$parent_ed_years))

subinfo$ethnicity <- as.character(subinfo$ethnicity)
subinfo$ethnicity[str_detect(subinfo$ethnicity, ",")] <- "Multiple Ethnicities"
```

```{r}
#merge questionnaire data with labels and demo info
d_demo <- responses_demo%>%
  left_join(subinfo)
```

```{r}
#create a dataframe that has mean subject scores and demographics
ss <- d_demo %>%
  group_by(sid, category) %>%
  summarise(rating = mean(rating))%>%
  left_join(subinfo)
```

```{r}
#only plot groups that have at least 20 observations
genders <- c("Male", "Female")

ethnicities <- ss%>%
  group_by(ethnicity) %>%
  filter(n() > 20)%>%
  select(ethnicity)%>%
  filter(ethnicity !="",
         ethnicity != "Other")%>%
  unique
ethnicities <- ethnicities$ethnicity

ages <- ss%>%
  group_by(parent_age) %>%
  filter(n() > 20)%>%
  select(parent_age)%>%
  unique
ages <- ages$parent_age

parent_eds <- ss%>%
  group_by(parent_ed) %>%
  filter(n() > 20)%>%
  select(parent_ed)%>%
  unique
parent_eds <- parent_eds$parent_ed

nums_kids <- ss%>%
  group_by(num_kids) %>%
  filter(n() > 20)%>%
  select(num_kids)%>%
  unique
nums_kids <- nums_kids$num_kids
```

```{r}
ms_gender <- d_demo %>% 
  filter(parent_gender %in% genders) %>%
  group_by(parent_gender, category) %>%
  tidyboot_mean(col = rating, na.rm = TRUE)
```

```{r}
p_gender <- ggplot(ms_gender, aes(category, mean, fill=parent_gender)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  theme_base()+
  scale_fill_viridis(discrete = TRUE, name="Parent Gender") +
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  theme(legend.title = element_text(size=10), 
        legend.text = element_text(size=10), 
        axis.title.x=element_blank(),
        axis.text.y  = element_text(vjust=0.5, size=10),
        axis.title.y = element_text(size=12))
```

```{r}
ms_age <- d_demo %>% 
  filter(parent_age %in% ages) %>%
  group_by(parent_age, category) %>%
  tidyboot_mean(col = rating)
```

```{r}
p_age <- ggplot(ms_age, aes(category, mean, fill=parent_age)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  theme_base()+
  scale_fill_viridis(discrete = TRUE, name="Parent Age") +
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  theme(legend.title = element_text(size=10), 
        legend.text = element_text(size=10), 
        axis.title.x=element_blank(),
        axis.text.y  = element_text(vjust=0.5, size=10),
        axis.title.y = element_text(size=12))
```

```{r}
ss$parent_ed <- factor(ss$parent_ed, levels = c("Less than high school","High school graduate","Some college","2 year degree","4 year degree", "Professional degree", "Doctorate"))

ms_ed <- d_demo %>% 
  group_by(parent_ed, category) %>%
  filter(parent_ed %in% parent_eds) %>%
  tidyboot_mean(col = rating)
```

```{r}
p_ed <- ggplot(ms_ed, aes(category, mean, fill=parent_ed)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  theme_base()+
  scale_fill_viridis(discrete = TRUE, name="Parent Education") +
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  theme(legend.title = element_text(size=10), 
        legend.text = element_text(size=10), 
        axis.title.x=element_blank(),
        axis.text.y  = element_text(vjust=0.5, size=10),
        axis.title.y = element_text(size=12))
```

```{r}
ms_ethnic <- d_demo %>% 
  group_by(ethnicity, category) %>%
  filter(ethnicity %in% ethnicities) %>%
  tidyboot_mean(col = rating)
```

```{r}
p_ethnic <- ggplot(ms_ethnic, aes(category, mean, fill=ethnicity)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  theme_base()+
  scale_fill_viridis(discrete = TRUE, name="Parent Ethnicity") +
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  theme(legend.title = element_text(size=10), 
        legend.text = element_text(size=10), 
        axis.title.x=element_blank(),
        axis.text.y  = element_text(vjust=0.5, size=10),
        axis.title.y = element_text(size=12))
```

```{r}
ms_numkids <- d_demo %>% 
  group_by(num_kids, category) %>%
  filter(num_kids %in% nums_kids) %>%
  tidyboot_mean(col = rating)
```

```{r}
p_numkids <- ggplot(ms_numkids, aes(category, mean, fill=num_kids)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  theme_base()+
  scale_fill_viridis(discrete = TRUE, name="Number of Children") +
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  theme(legend.title = element_text(size=10), 
        legend.text = element_text(size=10), 
        axis.title.x=element_blank(),
        axis.text.y  = element_text(vjust=0.5, size=10),
        axis.title.y = element_text(size=12))
```

```{r demographics,  fig.width=10, fig.height=8, fig.cap= "Demographic variability in PAQ scores. Error bars represent +/-95% CI computed by non-parametric bootstrap."}
grid.arrange(p_age, p_ed, p_ethnic, p_gender, p_numkids, nrow = 3)
```

```{r}
#make a new dataframe for regression models
d_demo_mods <- d_demo%>%
  transmute(sid = sid,
            rating = ordered(factor(rating)),
            item = short_sent,
            category = category,
            parent_age = as.numeric(parent_age_approx),
            parent_ed_years = as.numeric(parent_ed_years),
            num_kids = as.numeric(num_kids),
            ethnicity = as.factor(ethnicity),
            parent_gender = as.factor(parent_gender))

d_demo_mods$ethnicity[!d_demo_mods$ethnicity %in% ethnicities] <- NA
d_demo_mods$parent_gender[!d_demo_mods$parent_gender %in% genders] <- NA
```

```{r eval = FALSE}
#bayes ordinal logistic
#takes a long time to run
aa_demo_mod <- brm(rating ~ parent_age + ethnicity + parent_ed_years + num_kids + parent_gender +
                       (1|sid), 
     data=filter(d_demo_mods , category == "AA"),
              family=cumulative("logit"), control = list(adapt_delta = .99))

save(aa_demo_mod, file = "saved_mods/aa_demo_mod.Rdata")
```

```{r eval = FALSE}
#bayes ordinal logistic
#takes a long time to run
el_demo_mod <- brm(rating ~ parent_age + ethnicity + parent_ed_years + num_kids + parent_gender +
                       (1|sid), 
     data=filter(d_demo_mods , category == "EL"),
              family=cumulative("logit"), control = list(adapt_delta = .99))

save(el_demo_mod, file = "saved_mods/el_demo_mod.Rdata")
```

```{r eval = FALSE}
#bayes ordinal logistic
#takes a long time to run
rr_demo_mod <- brm(rating ~ parent_age + ethnicity + parent_ed_years + num_kids + parent_gender +
                       (1|sid), 
     data=filter(d_demo_mods, category == "RR"),
              family=cumulative("logit"), control = list(adapt_delta = .99))

save(rr_demo_mod, file = "saved_mods/rr_demo_mod.Rdata")
```

```{r}
#load saved ordinal logistic regression models
load ("saved_mods/aa_demo_mod.Rdata")
load ("saved_mods/el_demo_mod.Rdata")
load ("saved_mods/rr_demo_mod.Rdata")

aa_d <- summary(aa_demo_mod)
aa_demo <- data.frame(aa_d$fixed)

el_d <- summary(el_demo_mod)
el_demo <- data.frame(el_d$fixed)

rr_d <- summary(rr_demo_mod)
rr_demo <- data.frame(rr_d$fixed)
```

```{r demo_tab, results = "asis"}
factors <- c("Intercept 1", "Intercept 2", "Intercept 3", "Intercept 4", "Intercept 5", "Intercept 6", "Parent Age", "Hispanic or Latino", "Multiple Ethnicities", "White", "Parent Education", "Number of children", "Male", "Intercept 1", "Intercept 2", "Intercept 3", "Intercept 4", "Intercept 5", "Intercept 6", "Parent Age", "Hispanic or Latino", "Multiple Ethnicities", "White", "Parent Education", "Number of children", "Male", "Intercept 1", "Intercept 2", "Intercept 3", "Intercept 4", "Intercept 5", "Intercept 6", "Parent Age", "Hispanic or Latino", "Multiple Ethnicities", "White", "Parent Education", "Number of children", "Male")

subscales <- c("AA", "", "", "", "", "", "", 
               "EL", "", "", "", "", "", "", 
               "RR", "", "", "", "", "", "")

tab_demo_lm <- aa_demo%>%
  bind_rows(el_demo)%>%
  bind_rows(rr_demo)%>%
  mutate(Factor = factors)%>%
  filter(!str_detect(Factor,"Intercept"))%>%  
  mutate(Subscale = subscales)
  
tab_demo_lm  <- tab_demo_lm [,c(8,7,1:4)]

colnames(tab_demo_lm) <- c("Subscale","Factor","Estimate", "Est. Error", "Lower 95% CI", "Upper 95% CI")

demo_tab <- xtable(tab_demo_lm, label = "tab:demo", caption = "Results of separate bayesian ordinal logistic regressions of demographic factors on agreement with AA, EL, and RR attitudes.")

print(demo_tab, type="latex", comment = F, table.placement = "h", hline.after = c(-1, 0, 7, 14, 21), include.rownames=FALSE, align = c("r","l","r","r","r","r"), caption.placement = "top")
```

Approaches to parenting are known to differ across cultures and groups. To better understand whether the parenting attitudes captured by our survey reflect group differences, we examined average scores on the PAQ subscales based on demographic factors. We administered the PAQ to 680 parents who were members of a local children’s museum and subsequently asked them to provide information about their gender, level of education, age, ethnicity, and the number of children they have. Figure \ref{fig:demographics} displays the average PAQ scores for each demographic category.

To quantify any possible group differences, we fit separate Bayesian mixed effects ordinal regression models for each subscale (AA, EL, RR) with the following structure, with likert ratings of agreement for each item (1-6) entered as dependent measures: `agreement rating ~ age + education + ethnicity + gender + number of children + (1 | subject) + (1| item)` Groups with fewer than 20 cases were removed from plots and analyses to avoid overfitting. Although displayed as categorical for visual simplicity in Figure \ref{fig:demographics}, parent age and education in years were entered as continuous variables in the regression models.

Table \ref{tab:demo} displays the results of the regression analyses. We found that stronger agreement with AA attitudes was associated with identifying as Hispanic or Latino ($\beta$ = `r round(aa_demo$Estimate[8], digits = 2)`, 95% CI = `r round(aa_demo$l.95..CI[8], digits = 2)` - `r round(aa_demo$u.95..CI[8], digits = 2)`), White ($\beta$ = `r round(aa_demo$Estimate[10], digits = 2)`, 95% CI = `r round(aa_demo$l.95..CI[10], digits = 2)` - `r round(aa_demo$u.95..CI[10], digits = 2)`), or multiple ethnicities ($\beta$ = `r round(aa_demo$Estimate[9], digits = 2)`, 95% CI = `r round(aa_demo$l.95..CI[9], digits = 2)` - `r round(aa_demo$u.95..CI[9], digits = 2)`) compared to Asian (the comparison level). Having a greater number of children was associated with lower agreement with AA attitudes ($\beta$ = `r round(aa_demo$Estimate[12], digits = 2)`, 95% CI = `r round(aa_demo$l.95..CI[12], digits = 2)` - `r round(aa_demo$u.95..CI[12], digits = 2)`), as was identifying as Male ($\beta$ = `r round(aa_demo$Estimate[13], digits = 2)`, 95% CI = `r round(aa_demo$l.95..CI[13], digits = 2)` - `r round(aa_demo$u.95..CI[13], digits = 2)`). Parent education was not meaningfully associated with AA scores.

We found that stronger agreement with EL scores was associated with identifying as White ($\beta$ = `r round(el_demo$Estimate[10], digits = 2)`, 95% CI = `r round(el_demo$l.95..CI[10], digits = 2)` - `r round(el_demo$u.95..CI[10], digits = 2)`) or multiple ethnicities ($\beta$ = `r round(el_demo$Estimate[9], digits = 2)`, 95% CI = `r round(el_demo$l.95..CI[9], digits = 2)` - `r round(el_demo$u.95..CI[9], digits = 2)`), and having more children was associated with slightly lower agreement with EL scores ($\beta$ = `r round(el_demo$Estimate[12], digits = 2)`, 95% CI = `r round(el_demo$l.95..CI[12], digits = 2)` - `r round(el_demo$u.95..CI[12], digits = 2)`). No other demographic variables were related to EL scores.

Finally, we found that stronger agreement with RR attitudes was associated with having a greater number of children ($\beta$ = `r round(rr_demo$Estimate[12], digits = 2)`, 95% CI = `r round(rr_demo$l.95..CI[12], digits = 2)` - `r round(rr_demo$u.95..CI[12], digits = 2)`), and identifying as White was associated with lower agreement with RR attitudes ($\beta$ = `r round(rr_demo$Estimate[10], digits = 2)`, 95% CI = `r round(rr_demo$l.95..CI[10], digits = 2)` - `r round(rr_demo$u.95..CI[10], digits = 2)`).

## Study 2: Relation to parenting behaviors

```{r}
files <- dir("../production-results/parenting_behaviors_e2/")
attitudes <- data.frame()
behaviors <- data.frame()
subinfo <- data.frame()

for (f in files) {
  jf <- paste("../production-results/parenting_behaviors_e2/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  #paq answers
  attitudes_id <- data.frame(sid = as.factor(jd$WorkerId), 
               sent = jd$answers$data$sentence[1:24],
               rating = as.numeric(jd$answers$data$rating[1:24]))
                   
  attitudes <- bind_rows(attitudes, attitudes_id)
  
  #behaviors
  behaviors_id <- data.frame(sid = as.factor(jd$WorkerId),
                sent = jd$answers$data$sentence[25:36],
                rating = as.numeric(jd$answers$data$rating[25:36]))
                          
  behaviors <- bind_rows(behaviors, behaviors_id)
  
  #demographics
  subinfo_id <- data.frame(sid = as.factor(jd$WorkerId),
                   behave_age = jd$answers$data$behaveAge,
                   children = jd$answers$data$children)
  subinfo <- bind_rows(subinfo, subinfo_id)
}

#Clean up labels.
attitudes$sent <- str_replace_all(as.character(attitudes$sent), "[â‘”“’']", "")
behaviors$sent <- str_replace_all(as.character(behaviors$sent), "[â‘”“’']", "")
```

```{r}
#Read in trial info and questionnaire labels.
labels <- read.csv("../analysis/sent_forms.csv")
labels$sent <- as.character(labels$sent)
behave <- read.csv("../analysis/behaviors_e2.csv")
```

```{r}
dq <- attitudes %>%
  left_join(labels)%>%
  mutate(category_paq = category)%>%
  select(-category)

db <- behaviors%>%
  left_join(behave)%>%
  left_join(subinfo)%>%
  filter(behave_age != "older")%>%
  mutate(category_bev = category)%>%
  select(-category)

#remove items that parents marked as "my child is too young"
db$rating[db$rating == 0] <- NA

#rescore reverse coded items
dq$rating <- as.numeric(dq$rating)
dq$rating[dq$reverse_code == 1] <- 6 - dq$rating[dq$reverse_code == 1]
```

```{r}
#Get means by category.
atts <- dq %>%
  group_by(sid, category_paq) %>% 
  summarise(rating_paq = mean(rating))

bevs <- db %>%
  group_by(sid, category_bev) %>% 
  summarise(rating_bev = mean(rating))

all <- atts %>%
  left_join(bevs)%>%
  left_join(subinfo)%>%
  filter(!children == "0")
```

```{r}
#Recode variables for plotting.
bev <- behaviors %>%
  left_join(behave)%>%
  group_by(category)

bev$rating[bev$rating=="1"] <- "Never"
bev$rating[bev$rating=="2"] <- "Almost never"
bev$rating[bev$rating=="3"] <- "Occasionally"
bev$rating[bev$rating=="4"] <- "Once or twice per week"
bev$rating[bev$rating=="5"] <- "Most days"
bev$rating[bev$rating=="6"] <- "Multiple times every day"

bev$rating <- factor(bev$rating, levels = c("My child is too young", "Never", "Almost never","Occasionally","Once or twice per week","Most days","Multiple times every day"))

bev$short_sent <- factor(bev$short_sent, levels = c("read","practice numbers and letters","make observations", "educational programming","talk about feelings","spend time cuddling","sleep in the same bed","hug and kiss","talk sternly","give time out or punishments","talk about setting limits","help with chores"))

subinfo$behave_age[subinfo$behave_age == "0-6"] <- "0-6 months"
subinfo$behave_age[subinfo$behave_age == "7-12"] <- "7-12 months"

subinfo$behave_age <- factor(subinfo$behave_age, levels = c("0-6 months", "7-12 months", "1-1.5","1.5-2","2-2.5","2.5-3","3-3.5","3.5-4", "4-4.5","4.5-5", "older"))
```

```{r behavefreq, echo = FALSE, fig.width=10, fig.height=6, fig.cap= "Frequencies of different parenting activities reported by parents."}
ggplot(filter(bev, !is.na(rating)), aes(short_sent, fill = rating, shape = category)) + 
  geom_bar(position = "fill")+
  ylab("Proportion responding") +
  theme_base()+
  scale_fill_viridis(name="Frequency", discrete = TRUE, breaks=c("Multiple times every day","Most days","Once or twice per week","Occasionally", "Almost never", "Never"))+
  coord_flip()+
  theme(axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y = element_text(size = 12),
        legend.position="bottom",
        legend.text = element_text(size = 14),
        legend.title=element_blank()) 
```

```{r}
#descriptive labels for behavior categories
all$category_bev <- factor(all$category_bev,
levels = c("AA", "EL", "RR"),
labels = c("AA Behaviors", "EL Behaviors", "RR Behaviors"))
```

```{r behavepaq, fig.cap= "Relations between PAQ scores (Affection and Attachment, Early Learning, and Rules and Respect) and the frequency of parenting behaviors divided into the same categories."}
ggplot(filter(all, !is.na(category_bev)), aes(x= rating_bev, y = rating_paq, colour = category_paq)) +
  geom_jitter(aes(color = category_paq), height = .02, width = 0, alpha= .3) +
  geom_smooth(method="lm", se=TRUE) +
  facet_grid(~category_bev) + 
  xlab("Frequency of behavior") + 
  ylab("PAQ score") + 
  labs(colour="PAQ subscale")+
  theme_base()+
  scale_color_viridis(discrete = TRUE) +
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))
```

```{r}
#Set up dataframes for analyses.
d <- db %>%
  left_join(atts)%>%
  left_join(subinfo)%>%
  filter(!is.na(rating))%>%
  filter(children != 0)%>%
  filter(behave_age != "older")%>%
  filter(behave_age != "")%>%
  select(sid, short_sent, rating, category_paq, category_bev, rating_paq, behave_age)%>%
  spread(category_paq, rating_paq)

d$behave_age <- as.character(d$behave_age)

d$behave_age[d$behave_age == "0-6 months"] <- 1
d$behave_age[d$behave_age == "7-12 months"] <- 7
d$behave_age[d$behave_age == "1-1.5"] <- 13
d$behave_age[d$behave_age == "1.5-2"] <- 19 
d$behave_age[d$behave_age == "2-2.5"] <- 25
d$behave_age[d$behave_age == "2.5-3"] <- 31
d$behave_age[d$behave_age == "3-3.5"] <- 37
d$behave_age[d$behave_age == "3.5-4"] <- 43
d$behave_age[d$behave_age == "4-4.5"] <- 49
d$behave_age[d$behave_age == "4.5-5"] <- 55

d$behave_age <- as.numeric(d$behave_age)

d<- d%>%
  mutate(child_age = behave_age)%>%
  select(-behave_age)%>%
  mutate(rating_bin = rating)

d_aa <- d%>%
  filter(category_bev == "AA")%>%
  filter(!is.na(rating), !is.na(rating_bin))

d_el <- d%>%
  filter(category_bev == "EL")%>%
  filter(!is.na(rating),!is.na(rating_bin))

d_rr <- d%>%
  filter(category_bev == "RR")%>%
  filter(!is.na(rating),!is.na(rating_bin))

d_aa$rating_bin <- as.factor(d_aa$rating_bin)
d_el$rating_bin <- as.factor(d_el$rating_bin)
d_rr$rating_bin <- as.factor(d_rr$rating_bin)
```

```{r}
d$rating <- factor(d$rating,
levels = c(1, 2, 3, 4, 5, 6),
labels = c("1-never", "2-almost-never", "3-occasionally", "4-once-or-twice-per-week", "5-most-days", "6-multiple-times-every-day"))
```

```{r eval = FALSE}
d_aa%<>%
  mutate(rating = ordered(as.factor(rating)))

aa_behave_mod <- brm(rating ~ AA + RR + EL + child_age + 
              (1|sid) + 
              (1|short_sent), data=filter(d_aa, !is.na(rating)),
              family=cumulative("logit"), control = list(adapt_delta = .99))

save(aa_behave_mod, file = "saved_mods/aa_mod_behave.Rdata")
```

```{r eval = FALSE}
d_el%<>%
  mutate(rating = ordered(as.factor(rating)))

el_behave_mod <- brm(rating ~ AA + RR + EL + child_age + 
              (1|sid) + 
              (1|short_sent), data=filter(d_el, !is.na(rating)),
              family=cumulative("logit"), control = list(adapt_delta = .99))

save(el_behave_mod, file = "saved_mods/el_mod_behave.Rdata")
```

```{r eval = FALSE}
d_rr%<>%
  mutate(rating = ordered(as.factor(rating)))

rr_behave_mod <- brm(rating ~ AA + RR + EL + child_age + 
              (1|sid) + 
              (1|short_sent), data=filter(d_rr, !is.na(rating)),
              family=cumulative("logit"), control = list(adapt_delta = .99))

save(rr_behave_mod, file = "saved_mods/rr_mod_behave.Rdata")
```

```{r}
#load saved ordinal logistic regression models
load ("saved_mods/aa_mod_behave.Rdata")
load ("saved_mods/el_mod_behave.Rdata")
load ("saved_mods/rr_mod_behave.Rdata")

aa_b <- summary(aa_behave_mod)
aa_behave <- data.frame(aa_b$fixed)

el_b <- summary(el_behave_mod)
el_behave <- data.frame(el_b$fixed)

rr_b <- summary(rr_behave_mod)
rr_behave <- data.frame(rr_b$fixed)
```

```{r behavetab, results = "asis"}
factors <- c("Intercept 1", "Intercept 2", "Intercept 3", "Intercept 4", "Intercept 5", "AA PAQ score", "RR PAQ score", "EL PAQ score", "Child Age","Intercept 1", "Intercept 2", "Intercept 3", "Intercept 4", "Intercept 5", "AA PAQ score", "RR PAQ score", "EL PAQ score", "Child Age","Intercept 1", "Intercept 2", "Intercept 3", "Intercept 4", "Intercept 5", "AA PAQ score", "RR PAQ score", "EL PAQ score", "Child Age")

behaviors <- c("AA", "", "", "", 
               "EL", "", "", "", 
               "RR", "", "", "")

tab_behave_lm <- aa_behave%>%
  bind_rows(el_behave)%>%
  bind_rows(rr_behave)%>%
  mutate(Factor = factors)%>%
  filter(!str_detect(Factor,"Intercept"))%>%  
  mutate(`Behavior Category` = behaviors)
  
tab_behave_lm  <- tab_behave_lm [,c(8,7,1:4)]

colnames(tab_behave_lm) <- c("Behavior Category","Factor","Estimate", "Est. Error", "Lower 95% CI", "Upper 95% CI")

behave_tab <- xtable(tab_behave_lm, label = "tab:behavetab", caption = "Results of separate bayesian ordinal logistic regressions of PAQ scores and child age on frequency of parenting behaviors in Affection and Attachment (AA), Early Learning (EL), and Rules and Respect (RR) categories.")

print(behave_tab, type="latex", comment = F, table.placement = "h", hline.after = c(-1, 0, 4, 8, 12), include.rownames=FALSE, align = c("r","l","r","r","r","r"), caption.placement = "top")
```

```{r behavesents, results = "asis"}
cat <- c("AA", "", "", "", "EL", "","", "", "RR", "","","")
behaviors_sents <- behave%>%
  arrange(category)%>%
  transmute(Category=cat, `In the last month, how often did...` = str_replace(sent, "In the last month, how often did", ""))
  
kable(behaviors_sents, "latex", caption = "Behaviors that parents were asked to report on, and their corresponding attitude categories.") %>%
  column_spec(2, width = "35em")
```

Another way of assessing the ecological validity of the PAQ is to ask whether the parenting attitudes it assesses are related to actual parenting behaviors. For example, do parents who strongly agree with items on the Early Learning subscale read to their children more often? Do parents who strongly endorse items on the Rules and Respect subscale give more time-outs? To assess this, we asked a sample of 250 parents on Amazon's Mechanical Turk to complete the PAQ and then rate the frequency with which they engaged in a number of parenting behaviors, focusing on the prior month (Table \ref{tab:behavesents}). We elicited responses about 12 different behaviors, with four corresponding to each PAQ category. Parents chose between the following frequency options: "Multiple times per day", "Most days", "Once or twice per week," "Occasionally," "Almost never," "Never," and "My child is too young for this." Parents who did not have children under the age of 5 were excluded from analyses, as were any responses of "My child is too young for this."

The distribution of frequencies that parents reported is displayed in Figure \ref{fig:behavefreq}. To assess whether parenting behaviors are associated with parenting attitudes, we calculated participants' average PAQ subscale scores and fit separate bayesian ordinal logistic mixed effects regressions for the three cateogories of behaviors with the following structure: `behavior frequency ~ AA PAQ score + EL PAQ score + RR PAQ score + child age + (1 | subject) + (1| item)` (Table \ref{tab:behavetab}). The relation between PAQ scores and behavior frequencies are presented in Figure \ref{fig:behavepaq}.

We found that the frequency of AA behaviors was positively associated with AA attitudes ($\beta$ = `r round(aa_behave$Estimate[6], digits = 2)`, 95% CI = `r round(aa_behave$l.95..CI[6], digits = 2)` - `r round(aa_behave$u.95..CI[6], digits = 2)`), but not RR or EL attitudes or child age. Frequency of EL behaviors was positively associated with stronger agreement with both AA ($\beta$ = `r round(el_behave$Estimate[6], digits = 2)`, 95% CI = `r round(el_behave$l.95..CI[6], digits = 2)` - `r round(el_behave$u.95..CI[6], digits = 2)`) and EL attitudes ($\beta$ = `r round(el_behave$Estimate[8], digits = 2)`, 95% CI = `r round(el_behave$l.95..CI[8], digits = 2)` - `r round(el_behave$u.95..CI[8], digits = 2)`). The frequency of RR behaviors was positively associated with stronger RR attitudes ($\beta$ = `r round(rr_behave$Estimate[7], digits = 2)`, 95% CI = `r round(rr_behave$l.95..CI[7], digits = 2)` - `r round(rr_behave$u.95..CI[7], digits = 2)`), and to a lesser extent, child age ($\beta$ = `r round(rr_behave$Estimate[9], digits = 2)`, 95% CI = `r round(rr_behave$l.95..CI[9], digits = 2)` - `r round(rr_behave$u.95..CI[9], digits = 2)`). 

## Study 3: Uptake of new information about parenting and child development

Parents’ attitudes about parenting and child development may be an important consideration for crafting interventions on parenting behaviors or beliefs. There are frequent efforts to intervene on parenting practices, for example, public service announcements telling parents to read to their children; courses aimed at helping fathers engage with their children; messages aimed at encouraging parents and teachers to give children opportunities for free play. There is evidence that existing lay theories can interact in surprising ways with this type of messaging in other domains. Here we asked whether parents' attitudes about parenting and child development would predict how they uptake new information about child development versus an unrelated topic. 

```{r}
files <- dir("../production-results/uptake_e4/")
answers <- data.frame()
attitudes <- data.frame()
subinfo <- data.frame()

for (f in files) {
  jf <- paste("../production-results/uptake_e4/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))

  #uptake responses
  answers_id <- data.frame(
    answer= jd$answers$data$answer,
    item = jd$answers$data$item[jd$answers$data$trial_type =="uptake"],
    sid = jd$WorkerId)
  
  answers <- bind_rows(answers, answers_id)
  
  attitudes_id <- data.frame(sid = jd$WorkerId, 
                   sent = jd$answers$data$sentence[jd$answers$data$trial_type=="attitudes"],
                   rating = as.numeric(jd$answers$data$rating[jd$answers$data$trial_type=="attitudes"])) 
                   
  attitudes <- bind_rows(attitudes, attitudes_id)
  
  #questionnaire and demo
  subinfo_id <- data.frame(sid = jd$WorkerId, 
                   children = jd$answers$data$children,
                   language = jd$answers$data$homelang,
                   ses = jd$answers$data$ladder,
                   gender = jd$answers$data$gender,
                   age = jd$answers$data$age,
                   education = jd$answers$data$education,
                   ethnicity = jd$answers$data$ethnicity,
                   race = as.character(jd$answers$data$race[1]),
                   rt_exp1 = jd$answers$data$target1_rt,
                   rt_exp2 = jd$answers$data$target2_rt,
                   rt_con1 = jd$answers$data$control1_rt,
                   rt_con2 = jd$answers$data$control2_rt)
  subinfo <- bind_rows(subinfo, subinfo_id)
}
```

```{r}
#Read in trial info and questionnaire labels.
labels <- read.csv("../analysis/sent_forms_uptake_e4.csv")
labels$sent <- as.character(labels$sent)

answer_key <- read.csv("../analysis/uptake_key_e4.csv")
```

```{r}
#Clean up labels.
attitudes$sent <- stringr::str_replace_all(as.character(attitudes$sent), "[â‘”“’']", "")
```

```{r}
#Questionnaire attitude means.
dq <- attitudes %>%
  left_join(labels) 

dq$rating[dq$reverse_code == 1] <- 6 - dq$rating[dq$reverse_code == 1]

atts <- dq %>%
  group_by(sid, category) %>% 
  summarise(rating = mean(rating))
```

```{r}
#Setting up exclusion based on reading time. Exclude for less than 15s. 
exclusions <- as_tibble(subinfo) %>%
  select(sid, starts_with("rt")) %>%
  gather(article, rt, rt_exp1, rt_exp2, rt_con1, rt_con2) %>%
  mutate(article = stringr::str_replace(stringr::str_replace(stringr::str_replace(article,"rt_", ""), "exp", "e"), "con","c"),
         exclude = rt <15)
```

```{r}
#Get accuracy data. 
answers$answer <- as.character(answers$answer)
answer_key$answer_cor <- as.character(answer_key$answer_cor)

uptake <- answers %>%
  left_join(answer_key) %>%
  mutate(acc = (answer == answer_cor)) %>%
  select(sid, item, acc, q_type, article) %>%
  left_join(exclusions) %>%
  filter(!exclude)

mss <- uptake %>%
  group_by(sid, q_type) %>% 
  summarise(acc = mean(acc))

ms <- mss %>%
  group_by(q_type) %>%
  multi_boot_standard(col = "acc")
```

```{r}
mss_wide <- spread(mss, q_type, acc) %>%
  filter(!is.na(con) & !is.na(exp))

t_acc_q_type <- t.test(mss_wide$con, mss_wide$exp, paired=TRUE)
```

250 adults on Amazon's Mechanical Turk.

`r signif(mean(exclusions$exclude*100), digits = 2)`% of the data is excluded due to reading time exclusion.

The average accuracy for control questions was `r signif(ms$mean[ms$q_type == "con"], digits = 2)`(CI = `r signif(ms$ci_lower[ms$q_type == "con"], digits = 2)` - `r signif(ms$ci_upper[ms$q_type == "con"], digits = 2)`) and the average accuracy for experimenter questions was `r signif(ms$mean[ms$q_type == "exp"], digits = 2)`(CI = `r signif(ms$ci_lower[ms$q_type == "con"], digits = 2)` - `r signif(ms$ci_upper[ms$q_type == "exp"], digits = 2)`). There was no significant difference in accuracy between conditions, t = `r t_acc_q_type$statistic`, p = `r t_acc_q_type$p.value`.

```{r}
d <- mss %>%
  left_join(atts) %>%
  left_join(subinfo) %>%
  mutate(q_type = fct_recode(q_type, "Control" = "con", "Experimental" = "exp"))
```

```{r uptake, fig.cap= "Relations between PAQ scores (Affection and Attachment, Early Learning, and Rules and Respect) and the uptake of information in experimental (child development-related) and control articles."}
ggplot(d, aes(x = rating, y = acc, colour = q_type)) +
 geom_jitter(height = .02, width = 0, alpha= .3) +
  geom_smooth(method="lm") + 
  facet_grid(.~category) + 
  ylab("Accuracy") +
  xlab("PAQ Rating") + 
  theme(legend.position = "bottom",
        legend.title = element_text(size=16), 
        legend.text = element_text(size=14), 
        axis.text.x  = element_text(vjust=0.5, size=14),
        axis.title.x = element_text(size=16), 
        axis.text.y  = element_text(vjust=0.5, size=14),
        axis.title.y = element_text(size=16),
        strip.text = element_text(size=14))+
  theme_base()+
  scale_color_viridis(name="Condition", discrete = TRUE) 
```



```{r}
#Set up a dataframe for analysis with exclusions.
d_reg <- atts %>%
  left_join(uptake)%>%
  group_by(sid, category, acc, q_type, item, article)%>%
  summarise(rating = mean(rating))%>%
  spread(category, rating)

d_reg_excl <- d_reg %>%
  left_join(exclusions) %>%
  filter(!exclude)
```

```{r eval = FALSE}
uptake_mod <- brm(acc ~ q_type * AA +  
                q_type * RR + 
                q_type * EL +
                (q_type | sid) +
                (1 | item), 
              data = d_reg_excl,
              family = bernoulli())

save(uptake_mod, file ="saved_mods/uptake_mod.Rdata")
```

```{r}
#load saved ordinal logistic regression models
load ("saved_mods/uptake_mod.Rdata")

up <- summary(uptake_mod)
uptake <- data.frame(up$fixed)
```

```{r uptake_tab, results = "asis"}
factors <- c("Intercept", "Condition", "AA PAQ score", "RR PAQ score", "EL PAQ score", "AA PAQ score * Condition", "RR PAQ score * Condition", "EL PAQ score * Condition")

tab_uptake <- uptake%>%
  mutate(Factor = factors)%>%
  filter(!str_detect(Factor,"Intercept"))
  
tab_uptake <- tab_uptake [,c(7,1:4)]

colnames(tab_uptake) <- c("Factor","Estimate", "Est. Error", "Lower 95% CI", "Upper 95% CI")

tab_uptake_ <- xtable(tab_uptake, label = "tab:uptake", caption = "Results of a bayesian logistic regression of PAQ scores and experimental condition on accuracy.")

print(tab_uptake_, type="latex", comment = F, table.placement = "h", include.rownames=FALSE, align = c("l","r","r","r","r"), caption.placement = "top")
```

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
