---
title             : "Measuring Lay Theories of Parenting and Child Development"
shorttitle        : "Measuring Parenting Theories"
author: 
  - name          : "Emily Hembacher"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
  - name          : "Michael C. Frank"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "450 Serra Mall, Stanford, CA 94301"
    email         : "mcfrank@stanford.edu"
affiliation:
  - id            : "1"
    institution   : "Stanford University"
author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["paq.bib"]
figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
class             : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
---

```{r}
knitr::opts_chunk$set(fig.width = 8, fig.height = 5, echo = TRUE, warning = FALSE, message = FALSE, cache = TRUE)
```

```{r load_packages, include = FALSE}
library(tidyverse)
library(psych)
library(langcog) 
library(ggthemes) #plot themes
library(rjson) #for json data
library(lme4) #mixed effects models
library(lmerTest) #nicer lmer output
library(tidyboot) #bootstrapped confidence intervals
library(magrittr)
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion



## Study 1: Demographic Factors

```{r}
data <- read.csv("../cdm_paq.csv", header = TRUE)
dem <- read.csv("../cdm_paq_dem.csv", header = TRUE)
labels <- read.csv("../analysis/sent_forms_cdm.csv")
```

```{r}
#clean up data
questions <- data %>%
  filter(Status == "Response Type") %>%
  select(Q1:Q28) %>%
  gather("item", "sent", Q1:Q28)

d <- data %>%
  filter(Finished == 1) %>%
  mutate(sid = ResponseId) %>%
  select(sid, Q1:Q28) %>%
  gather("item", "rating", Q1:Q28) %>%
  left_join(questions)

subinfo <- dem %>%
  filter(Finished == "True") %>%
  transmute(sid = ResponseId, ethnicity = Q25.1, parent_ed = Q26.1, parent_age = Q27.1, parent_gender = Q28.1, num_kids = Q29, oldest_kid = Q30, youngest_kid = Q32, only_kid = Q33)

d$sent <- stringr::str_replace_all(d$sent, "’", "")
labels$sent <- as.character(labels$sent)
```

```{r}
#merge data with labels
dq <- d %>%
  left_join(labels)

#rescore reverse coded items
dq$rating <- as.numeric(dq$rating)
dq$rating[dq$reverse_code == 1] <- 8 - dq$rating[dq$reverse_code == 1]
dq$rating <- dq$rating - 1
```

```{r}
#create a dataframe that has subject scores and demographics
ss <- dq %>%
  group_by(sid, category) %>%
  summarise(rating = mean(rating))%>%
  left_join(subinfo)%>%
  mutate(parent_age_approx = parent_age,
         parent_ed_years = parent_ed)

#recode parent age to be continuous
ss$parent_age_approx <- recode(ss$parent_age_approx, "Under 18" = "18", "18 - 24" = "21", "25 - 34" = "30", "35 - 44" = "40", "45 - 54" = "50", "55 - 64" = "60", "65 - 74" = "70")
ss$parent_age_approx <- as.numeric(as.character(ss$parent_age_approx))

#recode parent ed to be continuous (num years)
ss$parent_ed_years <- recode(ss$parent_ed_years, "Less than high school" = "12", "High school graduate" = "12", "Some college" = "14", "2 year degree" = "14", "4 year degree" = "16", "Professional degree" = "19", "Doctorate" = "23")
ss$parent_ed_years <- as.numeric(as.character(ss$parent_ed_years))

ss$ethnicity <- as.character(ss$ethnicity)
ss$ethnicity[str_detect(ss$ethnicity, ",")] <- "Multiple Ethnicities"
```

```{r echo = FALSE}
ms_gender <- ss %>% 
  filter(parent_gender %in% c("Male","Female")) %>%
  group_by(parent_gender, category) %>%
  tidyboot_mean(col = rating, na.rm = TRUE)

ggplot(ms_gender, aes(category, mean, fill=parent_gender)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_base()+ 
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  scale_fill_discrete(name="Parent Gender")+ 
  theme(legend.title = element_text(size=16), 
        legend.text = element_text(size=14), 
        axis.text.x  = element_text(vjust=0.5, size=14),
        axis.title.x = element_text(size=16), 
        axis.text.y  = element_text(vjust=0.5, size=14),
        axis.title.y = element_text(size=16))
```

```{r echo = FALSE}
ms_age <- ss %>% 
  group_by(parent_age, category) %>%
  filter(n() > 20)%>%
  tidyboot_mean(col = rating)

ggplot(ms_age, aes(category, mean, fill=parent_age)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_base()+ 
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  scale_fill_discrete(name="Parent Age")+ 
  theme(legend.title = element_text(size=16), 
        legend.text = element_text(size=14), 
        axis.text.x  = element_text(vjust=0.5, size=14),
        axis.title.x = element_text(size=16), 
        axis.text.y  = element_text(vjust=0.5, size=14),
        axis.title.y = element_text(size=16))
```

```{r echo = FALSE}
ss$parent_ed <- factor(ss$parent_ed, levels = c("Less than high school","High school graduate","Some college","2 year degree","4 year degree", "Professional degree", "Doctorate"))

ms_ed <- ss %>% 
  group_by(parent_ed, category) %>%
  filter(n() > 20)%>%
  tidyboot_mean(col = rating)

ggplot(ms, aes(category, mean, fill=parent_ed)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_base()+ 
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  scale_fill_discrete(name="Parent Education")+ 
  theme(legend.title = element_text(size=16), 
        legend.text = element_text(size=14), 
        axis.text.x  = element_text(vjust=0.5, size=14),
        axis.title.x = element_text(size=16), 
        axis.text.y  = element_text(vjust=0.5, size=14),
        axis.title.y = element_text(size=16))
```

```{r echo = FALSE}
ms_ethnic <- ss %>% 
  group_by(ethnicity, category) %>%
  filter(n() > 10)%>%
  tidyboot_mean(col = rating)

ggplot(ms_ethnic, aes(category, mean, fill=ethnicity)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_base()+ 
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  scale_fill_discrete(name="Ethnicity")+ 
  theme(legend.title = element_text(size=16), 
        legend.text = element_text(size=14), 
        axis.text.x  = element_text(vjust=0.5, size=14),
        axis.title.x = element_text(size=16), 
        axis.text.y  = element_text(vjust=0.5, size=14),
        axis.title.y = element_text(size=16))
```

```{r echo = FALSE}
ms_numkids <- ss %>% 
  group_by(num_kids, category) %>%
  filter(n() > 20)%>%
  tidyboot_mean(col = rating)

ggplot(ms_numkids, aes(category, mean, fill=num_kids)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_base()+ 
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  scale_fill_discrete(name="Number of Children")+ 
  theme(legend.title = element_text(size=16), 
        legend.text = element_text(size=14), 
        axis.text.x  = element_text(vjust=0.5, size=14),
        axis.title.x = element_text(size=16), 
        axis.text.y  = element_text(vjust=0.5, size=14),
        axis.title.y = element_text(size=16))
```


```{r}
summary(lm(rating ~ as.numeric(parent_age) + ethnicity + as.numeric(parent_ed_years) + as.numeric(num_kids) + parent_gender, 
     data=filter(ss, category == "AA")))
```

```{r}
summary(lm(rating ~ as.numeric(parent_age) + ethnicity + as.numeric(parent_ed_years) + as.numeric(num_kids) + parent_gender, 
     data=filter(ss, category == "RR")))
```

```{r}
summary(lm(rating ~ as.numeric(parent_age) + ethnicity + as.numeric(parent_ed_years) + as.numeric(num_kids) + parent_gender, 
     data=filter(ss, category == "EL")))
```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
