---
title: "Parenting Project Attitudes Questionnaire Experiment 2"
author: "Emily & Mike"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of basic parenting values/attitudes survey, version 2.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(langcog)
library(dplyr)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(psych)
library(nFactors)
select <- dplyr::select # masked by MASS

theme_set(theme_bw())
```

Read in files and consolidate to the same directory. 

```{r}
files <- dir("../production-results/e2/")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("../production-results/e2/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  # clean up instruction trial
  sent <- jd$answers$data$sentence
  rating <- as.numeric(jd$answers$data$rating)
  trial_type <- jd$answer$data$trial_type
  sent <- sent[trial_type != "2afc_instructions"]
  trial_type <- trial_type[trial_type != "2afc_instructions"]
  
  id <- data.frame(workerid = jd$WorkerId, 
                   sent = sent,
                   rating = rating,
                   children = jd$answers$data$children,
                   language = jd$answer$data$homelang,
                   trial_type = trial_type,
                   ses = jd$answer$data$ladder)
  d.raw <- bind_rows(d.raw, id)
}
```

Map on question short forms so that we can use these instead. 

```{r}
labels <- read.csv("sent_forms_e2.csv")
labels$sent <- as.character(labels$sent)
```

Clean up labels.

```{r}
d.raw$sent <- as.character(d.raw$sent)
d.raw$sent <- str_replace_all(d.raw$sent, "'", "")
d.raw$sent <- str_replace_all(d.raw$sent, "’", "")
d.raw$sent <- str_replace_all(d.raw$sent, "“", "")
d.raw$sent <- str_replace_all(d.raw$sent, "”", "")
d.raw$sent <- str_replace_all(d.raw$sent, "‘", "")
d.raw$sent <- str_replace_all(d.raw$sent, "â", "'")
```

Merge. Only flip the reverse code items for knowledge. 

```{r}
d <- left_join(d.raw, labels) %>%
  mutate(children = grepl("yes", children, ignore.case=TRUE))

d$reverse_code[is.na(d$reverse_code)] <- 0
d$rating[d$reverse_code == 1 & d$instrument == "knowledge"] <- 1 - d$rating[d$reverse_code == 1 & d$instrument == "knowledge"]
```

Note children question is broken.

```{r}
subinfo <- d %>% 
  group_by(workerid) %>%
  summarise(children = children[1],
            ses = ses[1])

qplot(ses, data=subinfo)
```

# Basic analyses

Now look at mean ratings across sentences.

```{r}
ms <- d %>%
  group_by(category, instrument, short_sent) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(instrument, category, desc(mean)) 

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)
```

First plot attitude. 

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, 
      geom = "pointrange",
      data = filter(ms, instrument == "attitudes")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(1,7)) + 
  scale_colour_solarized()
```

Knowledge

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, 
      geom = "pointrange",
      data = filter(ms, instrument == "knowledge")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,1)) + 
  scale_colour_solarized()
```

People are really bad at: counting before math, listen quetly, words predict academic, no prediction, and educational tv good.

# Scale reliability

[Useful chapter here](http://psych.wfu.edu/furr/716/Furr%20SC%26P%20Ch%202.pdf)

## Attitudes

First the attitudes items. 

```{r}
wide.attitudes <- d %>% 
  filter(instrument == "attitudes") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.mat <- as.matrix(select(wide.attitudes, -workerid))
alpha(x = alpha.mat)
```

This time $\alpha = .81$ for the attitudes scale, much higher than e1 (.55).

"Best have few rules" and "unsupervised play" maybe candidates to exclude?

## Knowledge

Now the knowledge items. These are in fact reverse-coded.

```{r}
wide.knowledge <- d %>% 
  filter(instrument == "knowledge") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)

alpha.mat <- as.matrix(select(wide.knowledge, -workerid))
alpha(x = alpha.mat)
```

So $\alpha = .59$ for these items, compared to .71 for e1. The only difference is the removal of three items that were negatively correlated with the scale during e1 (`read all words`, `no vocab bad in school`, and `tv conversation` ). Not sure if it is normal to see such variability across samples.

# Factor analysis

Get eigenvalues for determining number of factors. 

## Knowledge

```{r}
knowl.mat <- select(wide.knowledge, -workerid) # get rid of worker id

ev <- eigen(cor(x=knowl.mat)) # get eigenvalues
ap <- parallel(subject=nrow(knowl.mat), var=ncol(knowl.mat),
               rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```

Now plot factor analysis

```{r}
n.factors <- 6
kf <- factanal(x = knowl.mat, factors = n.factors, scores = "regression")
loadings <- data.frame(kf$loadings[,1:n.factors]) %>%
  mutate(item = rownames(kf$loadings)) %>%
  gather(factor, loading, starts_with("Factor"))

qplot(factor, item, fill=loading, geom="tile", data = loadings) + 
  scale_fill_continuous(low="#000000",high="#FFFFFF")

qplot(factor, item, fill=loading > .5, geom="tile", data = loadings) + 
  scale_fill_solarized()
```

Plot questions on factor loadings.

```{r}
w.loadings <- loadings %>%
  spread(factor, loading)

qplot(Factor1, Factor2, label = item, 
      geom="text", data=w.loadings) + 
  xlim(c(-.2, 1))
```

Merge back in subject id info. 

```{r}
k.scores <- kf$scores %>%
  data.frame %>%
  mutate(workerid = wide.knowledge$workerid) %>%
  left_join(subinfo)
```

Plot 

```{r}
qplot(Factor1, Factor2, col = ses > 5, data=k.scores)
```

And summary:

```{r}
ms <- k.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ses != "") %>%
  mutate(high.ses = ses > 5) %>%
  group_by(high.ses, factor) %>%
  summarise(score = mean(score)) 

qplot(factor, score, fill=high.ses, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms)
```

## Attitudes.

```{r}
att.mat <- select(wide.attitudes, -workerid)
ev <- eigen(cor(x=att.mat)) # get eigenvalues
ap <- parallel(subject=nrow(att.mat), var=ncol(att.mat),
               rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```

Now plot factor analysis

```{r}
n.factors <- 5
af <- factanal(x = att.mat, factors = n.factors, scores = "regression")
loadings <- data.frame(af$loadings[,1:n.factors]) %>%
  mutate(item = rownames(af$loadings)) %>%
  gather(factor, loading, starts_with("Factor"))

qplot(factor, item, fill=loading, geom="tile", data = loadings) + 
  scale_fill_continuous(low="#000000", high="#FFFFFF")

qplot(factor, item, fill=loading > .5, geom="tile", data = loadings) + 
  scale_fill_solarized()
```

Merge back in subject id info. 

```{r}
a.scores <- af$scores %>%
  data.frame %>%
  mutate(workerid = wide.knowledge$workerid) %>%
  left_join(subinfo)
```

And summary:

```{r}
a.factor.names <- c("Early learning", "Affection",
                    "Rules & Respect", "Responsiveness", "Unsupervised")

ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ses != "") %>%
  mutate(high.ses = ses > 5, 
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(high.ses, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=high.ses, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```
 
# Knowledge by SES

```{r}
knowl <- d %>% 
  filter(instrument == "knowledge") %>%
  group_by(workerid) %>%
  summarise(mean = mean(rating)) %>%
  left_join(subinfo) %>%
  filter(ses != "") %>%
  mutate(high_ses = ses > 5) %>%
  group_by(high_ses) %>%
  multi_boot_standard(col = "mean")

qplot(high_ses, mean, ymin = ci_lower, ymax = ci_upper, 
      group = 1,
      geom = c("pointrange","smooth"), method = "lm", data = knowl)
```

# Principal components analysis

Next, let's look at a principal components analysis for the data. This approach tries to understand underlying orthogonal dimensions of variability.

## All items

Explore using PCA to group items. 

I removed the PCA analysis across scales because there were more variables than participants which was causing errors.

```{r}
#pcs <- princomp(x= select(wide.all, -workerid))
#plot(pcs)
```

```{r}
#biplot(pcs)
```

## Attitude items

First the attitude items. 

```{r}
row.names(wide.attitudes) <- wide.attitudes$workerid
pcs <- princomp(x = select(wide.attitudes, -workerid))
plot(pcs)
```


Let's try to plot the items by hand for more detail. 

```{r}
pc.items <- data.frame(pc1 = pcs$loadings[,1],
                      pc2 = pcs$loadings[,2],
                      pc3 = pcs$loadings[,3],
                      short_sent = row.names(pcs$loadings)) %>%
  left_join(labels)

qplot(pc1, pc2, col = category,
      label = short_sent, hjust = 1,
      geom = c("text","point"),
      data = pc.items) + 
  scale_colour_solarized() + 
  xlim(-.15,.35)
```



```{r}
pc.inds <- data.frame(pc1 = as.numeric(pcs$scores[,1]),
                      pc2 = as.numeric(pcs$scores[,2]),
                      pc3 = as.numeric(pcs$scores[,3]),
                      workerid = row.names(pcs$scores)) %>%
  left_join(subinfo)
                      
qplot(pc1, pc2, col = children,
      hjust = 1,
      data = pc.inds) + 
  scale_colour_solarized()
```


## Knowledge items

 

```{r}
pcs <- princomp(x= select(wide.knowledge, -workerid))
plot(pcs)
```

The variance for the components are really small compared to the attitudes scale, and compared to the knowledge scale during e1. 

```{r}
pc.data <- data.frame(pc1 = pcs$loadings[,1],
                      pc2 = pcs$loadings[,2],
                      pc3 = pcs$loadings[,3],
                      short_sent = row.names(pcs$loadings)) %>%
  left_join(labels)

qplot(pc1, pc2, col = category,
      label = short_sent, hjust = 1,
      geom = c("text","point"),
      data = pc.data) + 
  xlim(-.7,.3) +
  scale_colour_solarized()
```

Kind of interesting- seems like principle component 1 might relate to whether or not parents believe they have a critical role in their child's development (e.g., school responsibility vs. words predict academic)..
 
# Other stuff

```{r}
kf <- factanal(x = knowl.mat, factors = 6)
```

# Conclusions

The attitudes scale seems to have 5 distinct factors, 4 of which make sense conceptually (Early learning, Affection, Rules and respect, Responsiveness) and one that makes less sense (Unsupervised play). 

The next iteration will aim to replicate these factors, include more demographic info (income, education), and remove the unsupervised play question that has an unclear conceptual basis.

We will also drop the knowledge scale for now, as we likely will not use it in a way that makes reliability and validity as critical.
