---
title: "Parenting Project Attitudes Questionnaire Experiment 4"
author: "Emily & Mike"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of basic parenting values/attitudes survey, version 2.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}

rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(langcog)
library(plyr); library(dplyr)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(psych)
library(nFactors)

select <- dplyr::select # masked by MASS

theme_set(theme_bw())
```

Read in files and consolidate to the same directory. 


Leaving out variables that are causing issues: race, ethnicity, age of oldest child, age of youngest child. 
```{r}
files <- dir("../production-results/e4/")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("../production-results/e4/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  # clean up instruction trial
  sent <- jd$answers$data$sentence
  rating <- (jd$answers$data$rating) #removed as.numeric to include DU responses
  trial_type <- jd$answer$data$trial_type
  sent <- sent[trial_type != "2afc_instructions"]
  trial_type <- trial_type[trial_type != "2afc_instructions"]
  
  id <- data.frame(workerid = jd$WorkerId, 
                   sent = sent,
                   rating = rating,
                   children = jd$answers$data$children,
                   language = jd$answer$data$homelang,
                   ses = jd$answer$data$ladder,
                   gender = jd$answer$data$gender,
                   age = jd$answer$data$age,
                   education = jd$answer$data$education)
  d.raw <- bind_rows(d.raw, id)
}
```

Map on question short forms so that we can use these instead. 

```{r}
labels <- read.csv("sent_forms_e4.csv")
labels$sent <- as.character(labels$sent)
```

Clean up labels.

```{r}
d.raw$sent <- as.character(d.raw$sent)
d.raw$sent <- str_replace_all(d.raw$sent, "'", "")
d.raw$sent <- str_replace_all(d.raw$sent, "’", "")
d.raw$sent <- str_replace_all(d.raw$sent, "“", "")
d.raw$sent <- str_replace_all(d.raw$sent, "”", "")
d.raw$sent <- str_replace_all(d.raw$sent, "‘", "")
d.raw$sent <- str_replace_all(d.raw$sent, "â", "'")

```

Merge.  

```{r}
d <- left_join(d.raw, labels)

#set up reverse code variables so that items don't get reverse coded a second time. 

d$reverse_code[d$reverse_code == 1 & d$rating == "1"] <- 1
d$reverse_code[d$reverse_code == 1 & d$rating == "2"] <- 2
d$reverse_code[d$reverse_code == 1 & d$rating == "3"] <- 3

d$reverse_code[d$reverse_code == 1 & d$rating == "5"] <- 5
d$reverse_code[d$reverse_code == 1 & d$rating == "6"] <- 6
d$reverse_code[d$reverse_code == 1 & d$rating == "7"] <- 7

#reverse code.
d$rating[d$reverse_code == 1 & d$rating == "1"] <- 7
d$rating[d$reverse_code == 2 & d$rating == "2"] <- 6
d$rating[d$reverse_code == 3 & d$rating == "3"] <- 5

d$rating[d$reverse_code == 5 & d$rating == "5"] <- 3
d$rating[d$reverse_code == 6 & d$rating == "6"] <- 2
d$rating[d$reverse_code == 7 & d$rating == "7"] <- 1
```

Plot demographic info.
```{r}
subinfo <- d %>% 
  group_by(workerid) %>%
  summarise(age = age[1],
            gender = gender[1],
            children = children[1],
            ses = ses[1],
            education = education[1],
            language = language[1])

subinfo$education <- factor(subinfo$education, levels = c("highSchool","someCollege","4year","someGrad","Grad"))

subinfo$gender <- str_replace_all(subinfo$gender, "female|FEMALE|F$|f$|Female ","Female")
subinfo$gender <- str_replace_all(subinfo$gender, "^male|^Male|^MALE|^M$|^m$|^Maleq|Make", "Male")
subinfo$gender <- str_replace_all(subinfo$gender, "29", "")

subinfo$language <- str_replace_all(subinfo$language, "english|eNGLISH|Engliah|ENGLISH|English ", "English")

qplot(ses, data=subinfo)
qplot(children, data=subinfo)
qplot(gender, data=subinfo)
qplot(education, data=subinfo)
qplot(age, data=subinfo)
qplot(language, data=subinfo)

```

# Basic analyses

Now look at mean ratings across sentences.



```{r}
attach(d)
rating_count <- table(d$rating) 
rating_count
prop.table(rating_count) 

#get rid of DU
d$rating <- as.numeric(d$rating)

#added na.rm=TRUE to deal with missing values from DU.
ms <- d %>%
  group_by(category, instrument, short_sent) %>%
  multi_boot_standard(col = "rating", na.rm=TRUE) %>%
  arrange(instrument, category, desc(mean)) 

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)

```

Plot attitude.

Ratings are clearly lower for the reverse coded items.. this could be due to response sets (i.e., participants endorsing all items highly)

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, 
      geom = "pointrange",
      data = filter(ms, instrument == "attitudes")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(1,7)) + 
  scale_colour_solarized()

```


# Scale reliability

## Whole Scale
This analysis is not especially meaningful as it averages across the three subscales. However, it can be used as a comparison with the within subscale alphas. Raw alpha is .72 for the whole scale.
```{r}
wide.attitudes <- d %>% 
  filter(instrument == "attitudes") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.mat <- as.matrix(select(wide.attitudes, -workerid))
alpha(x = alpha.mat)
```

## Rules and Respect Subscale

Raw alpha is .72 here. 

```{r}
wide.rules_respect <- d %>% 
  filter(category == "rules_respect") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.rr <- as.matrix(select(wide.rules_respect, -workerid))
alpha(x = alpha.rr)
```

## Affection and Attachment Subscale

Raw alpha is .57 here, which is pretty low. It looks like removing the items "behavior problems no love" and "don't force activity" would improve things quite a bit.

```{r}
wide.affection <- d %>% 
  filter(category == "affection") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.af <- as.matrix(select(wide.affection, -workerid))
alpha(x = alpha.af)

```

## Active Learning Subscale

Raw alpha is .55, which is again low. Dropping "reward accuracy" will help. 
```{r}
wide.active_learning <- d %>% 
  filter(category == "active_learning") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.al <- as.matrix(select(wide.active_learning, -workerid))
alpha(x = alpha.al)
```


# Factor analysis

Get eigenvalues for determining number of factors. 

```{r}
att.mat <- select(wide.attitudes, -workerid)

ev <- eigen(cor(x=att.mat, use = "complete.obs")) # get eigenvalues, removes NAs
ap <- parallel(subject=nrow(att.mat), var=ncol(att.mat),
               rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```

Now plot factor analysis

FACTOR ANALYSIS BROKEN DUE TO NA

```{r}
n.factors <- 3
af <- factanal(x = att.mat, factors = n.factors, na.rm=TRUE, scores = "regression")
loadings <- data.frame(af$loadings[,1:n.factors]) %>%
  mutate(item = rownames(af$loadings)) %>%
  gather(factor, loading, starts_with("Factor"))

qplot(factor, item, fill=loading, geom="tile", data = loadings) + 
  scale_fill_continuous(low="#000000", high="#FFFFFF")

qplot(factor, item, fill=loading > .35, geom="tile", data = loadings) + 
  scale_fill_solarized()
```

Merge back in subject id info. 

```{r}
a.scores <- af$scores %>%
  data.frame %>%
  mutate(workerid = as.character(wide.attitudes$workerid)) %>%
  left_join(subinfo)
```

And summary:

## Factors by SES
```{r}
a.factor.names <- c("Rules and Respect", "Affection and Attachment", "Active Learning")

ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ses != "") %>%
  mutate(high.ses = ses > 5, 
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(high.ses, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=high.ses, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```


## Factors by Gender
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(gender != "") %>%
  mutate(male.gender = gender == "Male",
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(male.gender, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=male.gender, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```
 
## Factors by Education
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(education != "") %>%
  mutate(high.education = (education == "4year" |education == "someGrad" | education == "Grad"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(high.education, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=high.education, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```

## Factors by Age
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(age != "") %>%
  mutate(young.age = (age == "0-19" |age == "20-29"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(young.age, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=young.age, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```

## Factors by Number of Children
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(n.children = children,
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(n.children, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=n.children, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```

```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(yes.children = (children == "1" | children == "2" | children == "3"| children == "4"| children == "5"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(yes.children, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=yes.children, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```

 
# Conclusions

