---
title: "Parenting Project Attitudes Questionnaire Experiment 4"
author: "Emily & Mike"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of basic parenting values/attitudes survey, version 2.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}

rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(langcog)
library(plyr); library(dplyr)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(psych)
library(nFactors)

select <- dplyr::select # masked by MASS

theme_set(theme_bw())
```

Read in files and consolidate to the same directory. 

```{r}
files <- dir("../production-results/e4/")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("../production-results/e4/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  # clean up instruction trial
  sent <- jd$answers$data$sentence
  rating <- as.numeric(jd$answers$data$rating)
  trial_type <- jd$answer$data$trial_type
  
  id <- data.frame(workerid = jd$WorkerId, 
                   sent = sent,
                   rating = rating,
                   children = jd$answers$data$children,
                   age_youngest_child =    jd$answers$data$childAgeYoung,
                   age_oldest_child = jd$answers$data$childAgeOld,
                   ethnicity = jd$answers$data$ethnicity,
                   race = jd$answers$data$race,
                   language = jd$answer$data$homelang,
                   ses = jd$answer$data$ladder,
                   gender = jd$answer$data$gender,
                   age = jd$answer$data$age,
                   education = jd$answer$data$education)
  d.raw <- bind_rows(d.raw, id)
}
```

Map on question short forms so that we can use these instead. 

```{r}
labels <- read.csv("sent_forms_e4.csv")
labels$sent <- as.character(labels$sent)
```

Clean up labels.

```{r}
d.raw$sent <- as.character(d.raw$sent)
d.raw$sent <- str_replace_all(d.raw$sent, "'", "")
d.raw$sent <- str_replace_all(d.raw$sent, "’", "")
d.raw$sent <- str_replace_all(d.raw$sent, "“", "")
d.raw$sent <- str_replace_all(d.raw$sent, "”", "")
d.raw$sent <- str_replace_all(d.raw$sent, "‘", "")
d.raw$sent <- str_replace_all(d.raw$sent, "â", "'")

```

Merge.  

```{r}
d <- left_join(d.raw, labels)

#set up reverse code variables so that items don't get reverse coded a second time. 

d$reverse_code[d$reverse_code == 1 & d$rating == "1"] <- 1
d$reverse_code[d$reverse_code == 1 & d$rating == "2"] <- 2
d$reverse_code[d$reverse_code == 1 & d$rating == "3"] <- 3

d$reverse_code[d$reverse_code == 1 & d$rating == "5"] <- 5
d$reverse_code[d$reverse_code == 1 & d$rating == "6"] <- 6
d$reverse_code[d$reverse_code == 1 & d$rating == "7"] <- 7

#reverse code.
d$rating[d$reverse_code == 1 & d$rating == "1"] <- 7
d$rating[d$reverse_code == 2 & d$rating == "2"] <- 6
d$rating[d$reverse_code == 3 & d$rating == "3"] <- 5

d$rating[d$reverse_code == 5 & d$rating == "5"] <- 3
d$rating[d$reverse_code == 6 & d$rating == "6"] <- 2
d$rating[d$reverse_code == 7 & d$rating == "7"] <- 1
```

Plot demographic info.
```{r}
subinfo <- d %>% 
  group_by(workerid) %>%
  summarise(age = age[1],
            gender = gender[1],
            children = children[1],
            age_oldest_child = age_oldest_child[1],
            age_youngest_child = age_youngest_child[1],
            ses = ses[1],
            education = education[1],
            language = language[1],
            ethnicity = ethnicity[1],
            race = race[1])

subinfo$education <- factor(subinfo$education, levels = c("highSchool","someCollege","4year","someGrad","Grad"))

subinfo$gender <- str_replace_all(subinfo$gender, "female", "Female")
subinfo$gender <- str_replace_all(subinfo$gender, "FEMALE", "Female")
subinfo$gender <- str_replace_all(subinfo$gender, "F$", "Female")
subinfo$gender <- str_replace_all(subinfo$gender, "f$", "Female")
subinfo$gender <- str_replace_all(subinfo$gender, "Female ", "Female")
subinfo$gender <- str_replace_all(subinfo$gender, "^male", "Male")
subinfo$gender <- str_replace_all(subinfo$gender, "^Male ", "Male")
subinfo$gender <- str_replace_all(subinfo$gender, "^MALE", "Male")
subinfo$gender <- str_replace_all(subinfo$gender, "^M$", "Male")
subinfo$gender <- str_replace_all(subinfo$gender, "^m$", "Male")
subinfo$gender <- str_replace_all(subinfo$gender, "^Maleq", "Male")
subinfo$gender <- str_replace_all(subinfo$gender, "Make", "Male")
subinfo$gender <- str_replace_all(subinfo$gender, "29", "")

subinfo$age_oldest_child <- factor(subinfo$age_oldest_child, levels = c("0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

subinfo$age_youngest_child <- factor(subinfo$age_youngest_child, levels = c("0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

qplot(ses, data=subinfo)
qplot(children, data=subinfo)
qplot(gender, data=subinfo)
qplot(education, data=subinfo)
qplot(age, data=subinfo)
qplot(language, data=subinfo)
qplot(age_oldest_child, data=subinfo)
qplot(age_youngest_child, data=subinfo)
qplot(ethnicity, data=subinfo)
qplot(race, data=subinfo)

```

# Basic analyses

Now look at mean ratings across sentences.

```{r}

attach(d)
rating_count <- table(d$rating) 
rating_count
prop.table(rating_count) 

d$rating[d$rating == "DU"] <- ""

ms <- d %>%
  group_by(category, instrument, short_sent) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(instrument, category, desc(mean)) 

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)

```

Plot attitude. 

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, 
      geom = "pointrange",
      data = filter(ms, instrument == "attitudes")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(1,7)) + 
  scale_colour_solarized()

```


# Scale reliability

[Useful chapter here](http://psych.wfu.edu/furr/716/Furr%20SC%26P%20Ch%202.pdf)
 
Reliability is reduced compared to e2 (alpha = 76 compared to 81 for e2)

```{r}
wide.attitudes <- d %>% 
  filter(instrument == "attitudes") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.mat <- as.matrix(select(wide.attitudes, -workerid))
alpha(x = alpha.mat)


```

# Factor analysis

Get eigenvalues for determining number of factors. 


```{r}
att.mat <- select(wide.attitudes, -workerid)
ev <- eigen(cor(x=att.mat)) # get eigenvalues
ap <- parallel(subject=nrow(att.mat), var=ncol(att.mat),
               rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```

Now plot factor analysis

```{r}
n.factors <- 3
af <- factanal(x = att.mat, factors = n.factors, scores = "regression")
loadings <- data.frame(af$loadings[,1:n.factors]) %>%
  mutate(item = rownames(af$loadings)) %>%
  gather(factor, loading, starts_with("Factor"))

qplot(factor, item, fill=loading, geom="tile", data = loadings) + 
  scale_fill_continuous(low="#000000", high="#FFFFFF")

qplot(factor, item, fill=loading > .35, geom="tile", data = loadings) + 
  scale_fill_solarized()
```

Merge back in subject id info. 

```{r}
a.scores <- af$scores %>%
  data.frame %>%
  mutate(workerid = as.character(wide.attitudes$workerid)) %>%
  left_join(subinfo)
```

And summary:

Note: I re-labeled the factors, because the order appears different this time.

## Factors by SES
```{r}
a.factor.names <- c("Affection and Early Learning", "Rules and Respect", "Spontaneous Play")

ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ses != "") %>%
  mutate(high.ses = ses > 5, 
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(high.ses, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=high.ses, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```


## Factors by Gender
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(gender != "") %>%
  mutate(male.gender = gender == "Male",
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(male.gender, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=male.gender, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```
 
## Factors by Education
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(education != "") %>%
  mutate(high.education = (education == "4year" |education == "someGrad" | education == "Grad"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(high.education, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=high.education, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```

## Factors by Age
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(age != "") %>%
  mutate(young.age = (age == "0-19" |age == "20-29"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(young.age, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=young.age, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```

## Factors by Number of Children
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(n.children = children,
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(n.children, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=n.children, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```

```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(yes.children = (children == "1" | children == "2" | children == "3"| children == "4"| children == "5"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(yes.children, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=yes.children, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```


# Principal components analysis

Next, let's look at a principal components analysis for the data. This approach tries to understand underlying orthogonal dimensions of variability.


```{r}
row.names(wide.attitudes) <- wide.attitudes$workerid
pcs <- princomp(x = select(wide.attitudes, -workerid))
plot(pcs)
```


Let's try to plot the items by hand for more detail. 

```{r}
pc.items <- data.frame(pc1 = pcs$loadings[,1],
                      pc2 = pcs$loadings[,2],
                      pc3 = pcs$loadings[,3],
                      short_sent = row.names(pcs$loadings)) %>%
  left_join(labels)

qplot(pc1, pc2, col = category,
      label = short_sent, hjust = 1,
      geom = c("text","point"),
      data = pc.items) + 
  scale_colour_solarized() + 
  xlim(-.15,.35)
```

```{r}
pc.inds <- data.frame(yes.children = (children == "1" | children == "2" | children == "3"| children == "4"| children == "5"),
                      pc1 = as.numeric(pcs$scores[,1]),
                      pc2 = as.numeric(pcs$scores[,2]),
                      pc3 = as.numeric(pcs$scores[,3]),
                      workerid = row.names(pcs$scores)) %>%
  left_join(subinfo)
                      
qplot(pc1, pc2, col = yes.children,
      hjust = 1,
      data = pc.inds) + 
  scale_colour_solarized()
```


```{r}
pc.data <- data.frame(pc1 = pcs$loadings[,1],
                      pc2 = pcs$loadings[,2],
                      pc3 = pcs$loadings[,3],
                      short_sent = row.names(pcs$loadings)) %>%
  left_join(labels)

qplot(pc1, pc2, col = category,
      label = short_sent, hjust = 1,
      geom = c("text","point"),
      data = pc.data) + 
  xlim(-.7,.3) +
  scale_colour_solarized()
```

 
# Conclusions

