---
title: "Parenting Project Attitudes Questionnaire Experiment 4"
author: "Emily & Mike"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of basic parenting values/attitudes survey, version 2.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}

rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(langcog)
library(plyr); library(dplyr)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(psych)
library(nFactors)

select <- dplyr::select # masked by MASS

theme_set(theme_bw())
```

Read in files and consolidate to the same directory. 

```{r}
files <- dir("../data/e5/")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("../data/e5/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  # clean up instruction trial
  sent <- jd$answers$data$sentence
  rating <- (jd$answers$data$rating) #removed as.numeric to include DU responses
  trial_type <- jd$answer$data$trial_type
  sent <- sent[trial_type != "2afc_instructions"]
  trial_type <- trial_type[trial_type != "2afc_instructions"]
  
  id <- data.frame(workerid = jd$WorkerId, 
                   sent = sent,
                   rating = rating,
                   children = jd$answers$data$children,
                   language = jd$answer$data$homelang,
                   ses = jd$answer$data$ladder,
                   gender = jd$answer$data$gender,
                   age = jd$answer$data$age,
                   education = jd$answer$data$education,
                   ethnicity = jd$answer$data$ethnicity,
                   childAgeYoung = jd$answer$data$childAgeYoung,
                   childAgeOld = jd$answer$data$childAgeOld)
  d.raw <- bind_rows(d.raw, id)
}
```

Map on question short forms so that we can use these instead. 

```{r}
labels <- read.csv("sent_forms_e5.csv")
labels$sent <- as.character(labels$sent)
```

Clean up labels.

```{r}
d.raw$sent <- as.character(d.raw$sent)
d.raw$sent <- str_replace_all(d.raw$sent, "'", "")
d.raw$sent <- str_replace_all(d.raw$sent, "’", "")
d.raw$sent <- str_replace_all(d.raw$sent, "“", "")
d.raw$sent <- str_replace_all(d.raw$sent, "”", "")
d.raw$sent <- str_replace_all(d.raw$sent, "‘", "")
d.raw$sent <- str_replace_all(d.raw$sent, "â", "'")

```

Merge.  

```{r}
d <- left_join(d.raw, labels)

#set up reverse code variables so that items don't get reverse coded a second time. 

d$reverse_code[d$reverse_code == 1 & d$rating == "1"] <- 1
d$reverse_code[d$reverse_code == 1 & d$rating == "0"] <- 0

#reverse code.
d$rating[d$reverse_code == 1 & d$rating == "1"] <- 0
d$rating[d$reverse_code == 0 & d$rating == "0"] <- 1
```

Plot demographic info.

Note: more respondants with children than Experiment 4, but still not a ton.
```{r}
subinfo <- d %>% 
  group_by(workerid) %>%
  summarise(age = age[1],
            gender = gender[1],
            children = children[1],
            ses = ses[1],
            education = education[1],
            language = language[1],
            ethnicity = ethnicity[1],
            childAgeYoung = childAgeYoung[1],
            childAgeOld = childAgeOld[1])

subinfo$education <- factor(subinfo$education, levels = c("highSchool","someCollege","4year","someGrad","Grad"))

subinfo$gender <- str_replace_all(subinfo$gender, "female|FEMALE|F$|f$|Female ","Female")
subinfo$gender <- str_replace_all(subinfo$gender, "^male|^Male|^MALE|^M$|^m$|^Maleq|Make", "Male")

subinfo$language <- str_replace_all(subinfo$language, "english|eNGLISH|Engliah|ENGLISH|English | English| ENglish|^eng$|ENglish| English", "English")
subinfo$language <- str_replace_all(subinfo$language, "SPANISH", "Spanish")
subinfo$language <- str_replace_all(subinfo$language, "vietnamese", "Vietnamese")
subinfo$language <- str_replace_all(subinfo$language, "russian", "Russian")

qplot(ses, data=subinfo)
qplot(children, data=subinfo)
qplot(gender, data=subinfo)
qplot(education, data=subinfo)
qplot(age, data=subinfo)
qplot(language, data=subinfo)
qplot(ethnicity, data=subinfo)
qplot(childAgeYoung, data=subinfo)
qplot(childAgeOld, data=subinfo)
```

# Basic analyses

Now look at mean ratings across sentences.

Need to look at which items were associated with DU.

```{r}
rating_count <- table(d$rating[d$instrument=="attitudes"]) 
rating_count
prop.table(rating_count) 

#get rid of DU
d$rating <- as.numeric(d$rating)

#added na.rm=TRUE to deal with missing values from DU.
ms <- d %>%
  group_by(category, instrument, short_sent) %>%
  multi_boot_standard(col = "rating", na.rm=TRUE) %>%
  arrange(instrument, category, desc(mean)) 

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)

```

Plot attitude. 

People are pretty much endorsing every statement, except for the reverse coded ones, which is likely due to a response set. This seems like a pretty good argument for sticking with Likert for this questionnaire, since we are probably looking for variability in the degree to which people endorse the statements, since all of the statements are more or less reasonable. 

Another thought: maybe we should frame the scale differently, in terms of how much participants AGREE with the scale, from 0-6, since they don't seem to disagree with any of the statements?

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, 
      geom = "pointrange",
      data = filter(ms, instrument == "attitudes")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,1)) + 
  scale_colour_solarized()

```


# Scale reliability

Can't really look at these because there is no variability for a lot of the items...
## Whole Scale

```{r}
wide.attitudes <- d %>% 
  filter(instrument == "attitudes") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.mat <- as.matrix(select(wide.attitudes, -workerid))
alpha(x = alpha.mat)
```

Look for items given "Don't Understand" ratings- they will be missing values here. There are only 10 DU ratings and they are spread across questions- no indication that any items are especially problematic.
```{r}
rating_count <- table(wide.attitudes$`behavior problems no love`) 
rating_count

rating_count <- table(wide.attitudes$`can learn good and bad`) 
rating_count

rating_count <- table(wide.attitudes$`control behavior`) 
rating_count

rating_count <- table(wide.attitudes$`dont force activity`) 
rating_count

rating_count <- table(wide.attitudes$`dont interrupt`) 
rating_count

rating_count <- table(wide.attitudes$`examples are good`) 
rating_count

rating_count <- table(wide.attitudes$`follow-in good`) 
rating_count

rating_count <- table(wide.attitudes$`holding and cradling`) 
rating_count

rating_count <- table(wide.attitudes$`learn before talking`) 
rating_count

rating_count <- table(wide.attitudes$`learn by playing`) 
rating_count

rating_count <- table(wide.attitudes$`not spoiled with too much affection`) 
rating_count

rating_count <- table(wide.attitudes$`parents provide structure`) 
rating_count

rating_count <- table(wide.attitudes$`punish for small rules`) 
rating_count

rating_count <- table(wide.attitudes$`punish misbehavior`) 
rating_count

rating_count <- table(wide.attitudes$`reasons for rules`) 
rating_count

rating_count <- table(wide.attitudes$`respect parents teachers`) 
rating_count

rating_count <- table(wide.attitudes$`reward accuracy`) 
rating_count

rating_count <- table(wide.attitudes$`safe loving environment`) 
rating_count

rating_count <- table(wide.attitudes$`spontaneous play`) 
rating_count

rating_count <- table(wide.attitudes$`strict rules`) 
rating_count

rating_count <- table(wide.attitudes$`strong bond mom`) 
rating_count

rating_count <- table(wide.attitudes$`talk about feelings`) 
rating_count

rating_count <- table(wide.attitudes$`talk about opinions`) 
rating_count

rating_count <- table(wide.attitudes$`wait when told`) 
rating_count
```

## Rules and Respect Subscale

```{r}
wide.rules_respect <- d %>% 
  filter(category == "rules_respect") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.rr <- as.matrix(select(wide.rules_respect, -workerid))
alpha(x = alpha.rr)
```

## Affection and Attachment Subscale

```{r}
wide.affection <- d %>% 
  filter(category == "affection") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.af <- as.matrix(select(wide.affection, -workerid))
alpha(x = alpha.af)

```

## Active Learning Subscale

```{r}
wide.active_learning <- d %>% 
  filter(category == "active_learning") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.al <- as.matrix(select(wide.active_learning, -workerid))
alpha(x = alpha.al)
```


# Factor analysis

Get eigenvalues for determining number of factors. 

Error message for eigenvalues: standard deviation is 0
```{r}
att.mat <- select(wide.attitudes, -workerid)
att.mat <- na.omit(att.mat)
ev <- eigen(cor(x=att.mat)) # get eigenvalues, removes NAs
ap <- parallel(subject=nrow(att.mat), var=ncol(att.mat),
               rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```

Now plot factor analysis

```{r}
n.factors <- 3
x <- na.omit(att.mat) #get rid of NA caused by DU responses

af <- factanal(x, factors = n.factors, scores = "regression")
loadings <- data.frame(af$loadings[,1:n.factors]) %>%
  mutate(item = rownames(af$loadings)) %>%
  gather(factor, loading, starts_with("Factor"))

qplot(factor, item, fill=loading, geom="tile", data = loadings) + 
  scale_fill_continuous(low="#000000", high="#FFFFFF")

qplot(factor, item, fill=loading > .35, geom="tile", data = loadings) + 
  scale_fill_solarized()
```

Merge back in subject id info. 

```{r}
a.scores <- af$scores %>%
  data.frame %>%
  mutate(workerid = as.character(wide.attitudes$workerid)) %>%
  left_join(subinfo)
```

And summary:

Note: I re-labeled the factors, because the order appears different this time.

## Factors by SES
```{r}
a.factor.names <- c("Affection and Early Learning", "Rules and Respect", "Spontaneous Play")

ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ses != "") %>%
  mutate(high.ses = ses > 5, 
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(high.ses, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=high.ses, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```


## Factors by Gender
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(gender != "") %>%
  mutate(male.gender = gender == "Male",
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(male.gender, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=male.gender, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```
 
## Factors by Education
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(education != "") %>%
  mutate(high.education = (education == "4year" |education == "someGrad" | education == "Grad"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(high.education, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=high.education, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```

## Factors by Age
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(age != "") %>%
  mutate(young.age = (age == "0-19" |age == "20-29"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(young.age, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=young.age, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```

## Factors by Number of Children
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(n.children = children,
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(n.children, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=n.children, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```

```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(yes.children = (children == "1" | children == "2" | children == "3"| children == "4"| children == "5"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(yes.children, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=yes.children, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```


# Principal components analysis

Next, let's look at a principal components analysis for the data. This approach tries to understand underlying orthogonal dimensions of variability.


```{r}
row.names(wide.attitudes) <- wide.attitudes$workerid
pcs <- princomp(x = select(wide.attitudes, -workerid))
plot(pcs)
```


Let's try to plot the items by hand for more detail. 

```{r}
pc.items <- data.frame(pc1 = pcs$loadings[,1],
                      pc2 = pcs$loadings[,2],
                      pc3 = pcs$loadings[,3],
                      short_sent = row.names(pcs$loadings)) %>%
  left_join(labels)

qplot(pc1, pc2, col = category,
      label = short_sent, hjust = 1,
      geom = c("text","point"),
      data = pc.items) + 
  scale_colour_solarized() + 
  xlim(-.15,.35)
```

```{r}
pc.inds <- data.frame(yes.children = (children == "1" | children == "2" | children == "3"| children == "4"| children == "5"),
                      pc1 = as.numeric(pcs$scores[,1]),
                      pc2 = as.numeric(pcs$scores[,2]),
                      pc3 = as.numeric(pcs$scores[,3]),
                      workerid = row.names(pcs$scores)) %>%
  left_join(subinfo)
                      
qplot(pc1, pc2, col = yes.children,
      hjust = 1,
      data = pc.inds) + 
  scale_colour_solarized()
```


```{r}
pc.data <- data.frame(pc1 = pcs$loadings[,1],
                      pc2 = pcs$loadings[,2],
                      pc3 = pcs$loadings[,3],
                      short_sent = row.names(pcs$loadings)) %>%
  left_join(labels)

qplot(pc1, pc2, col = category,
      label = short_sent, hjust = 1,
      geom = c("text","point"),
      data = pc.data) + 
  xlim(-.7,.3) +
  scale_colour_solarized()
```

# Conclusions
Should use Likert Scale and anchor from Don't Agree to Agree.
