---
title: "Parenting Project Attitudes Questionnaire Experiment 6"
author: "Emily & Mike"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of basic parenting values/attitudes survey.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}

rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(langcog)
library(plyr); library(dplyr)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(psych)
library(nFactors)

select <- dplyr::select # masked by MASS

theme_set(theme_bw())
```

Read in files and consolidate to the same directory. 

```{r}
files <- dir("../production-results/e6/")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("../production-results/e6/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  # clean up instruction trial
  sent <- jd$answers$data$sentence
  rating <- as.numeric(jd$answers$data$rating) 
  trial_type <- jd$answer$data$trial_type
  sent <- sent[trial_type != "2afc_instructions"]
  trial_type <- trial_type[trial_type != "2afc_instructions"]
  
  #left out race because not sure yet how to deal with list format
  id <- data.frame(workerid = jd$WorkerId, 
                   sent = sent,
                   rating = rating,
                   children = jd$answers$data$children,
                   language = jd$answer$data$homelang,
                   ses = jd$answer$data$ladder,
                   gender = jd$answer$data$gender,
                   age = jd$answer$data$age,
                   education = jd$answer$data$education,
                   ethnicity = jd$answer$data$ethnicity,
                   childAgeYoung = jd$answer$data$childAgeYoung,
                   childAgeOld = jd$answer$data$childAgeOld
                   )
  d.raw <- bind_rows(d.raw, id)
}
```

Map on question short forms so that we can use these instead. 

```{r}
labels <- read.csv("sent_forms_e6.csv")
labels$sent <- as.character(labels$sent)
```

Clean up labels.

```{r}
d.raw$sent <- as.character(d.raw$sent)
d.raw$sent <- str_replace_all(d.raw$sent, "'", "")
d.raw$sent <- str_replace_all(d.raw$sent, "’", "")
d.raw$sent <- str_replace_all(d.raw$sent, "“", "")
d.raw$sent <- str_replace_all(d.raw$sent, "”", "")
d.raw$sent <- str_replace_all(d.raw$sent, "‘", "")
d.raw$sent <- str_replace_all(d.raw$sent, "â", "")
```

Merge.  

```{r}
d <- left_join(d.raw, labels)
d$rating[d$reverse_code == 1] <- 6 - d$rating[d$reverse_code == 1]
```

Plot demographic info.

```{r}
subinfo <- d %>% 
  group_by(workerid) %>%
  summarise(age = age[1],
            gender = gender[1],
            children = children[1],
            ses = ses[1],
            education = education[1],
            language = language[1], 
            ethnicity = ethnicity[1],
            youngestChildAge = childAgeYoung[1],
            oldestChildAge = childAgeOld[1]
            )

subinfo$education <- factor(subinfo$education, levels = c("highSchool","someCollege","4year","someGrad","Grad"))

subinfo$gender <- str_replace_all(subinfo$gender, "female|FEMALE|F$|f$|Femal$|Females|Females","Female")
subinfo$gender <- str_replace_all(subinfo$gender, "^male|^Male|^MALE|^M$|^m$|^Maleq|Make", "Male")
subinfo$gender <- str_replace_all(subinfo$gender, "29|24|25|28|32|33|45", "")
subinfo$gender <- str_replace_all(subinfo$gender, "males", "male")
subinfo$gender <- str_replace_all(subinfo$gender, " ", "")


subinfo$language <- str_replace_all(subinfo$language, "english|eNGLISH|Engliah|ENGLISH|^eng$|Enlgish", "English")
subinfo$language <- str_replace_all(subinfo$language," ", "")
subinfo$language <- str_replace_all(subinfo$language,"arabic", "Arabic")
subinfo$language <- str_replace_all(subinfo$language,"chinese", "Chinese")
subinfo$language <- str_replace_all(subinfo$language,"german", "German")
subinfo$language <- str_replace_all(subinfo$language,"tagalog", "Tagalog")

subinfo$youngestChildAge <- factor(subinfo$youngestChildAge, levels = c("","0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

subinfo$oldestChildAge <- factor(subinfo$oldestChildAge, levels = c("","0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

qplot(ses, data=subinfo)
qplot(children, data=subinfo)
qplot(gender, data=subinfo)
qplot(education, data=subinfo)
qplot(age, data=subinfo)
qplot(language, data=subinfo)
qplot(ethnicity, data=subinfo)
qplot(youngestChildAge, data=subinfo)
qplot(oldestChildAge, data=subinfo)

```

# Basic analyses

Now look at mean ratings across sentences.

```{r}

rating_count <- table(d$rating) 
rating_count
prop.table(rating_count) 

ms <- d %>%
  group_by(category, instrument, short_sent, reverse_code) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(instrument, category, desc(mean)) 

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)

```

Plot attitude.

Ratings are clearly lower for the reverse coded items (the final 2 items in each category); this could be due to response sets (i.e., participants endorsing all items highly). 

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, pch = factor(reverse_code),
      geom = "pointrange",
      data = filter(ms, instrument == "attitudes")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,6)) + 
  scale_colour_solarized()

```


# Scale reliability

## Whole Scale
This analysis is not especially meaningful as it averages across the three subscales. Raw alpha is .88 which is higher than previous runs.
```{r}
wide.attitudes <- d %>% 
  filter(instrument == "attitudes") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.mat <- as.matrix(select(wide.attitudes, -workerid))
alpha(x = alpha.mat)
```

## Rules and Respect Subscale

Raw alpha is .78 here. 

```{r}
wide.rules_respect <- d %>% 
  filter(category == "rules_respect") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.rr <- as.matrix(select(wide.rules_respect, -workerid))
alpha(x = alpha.rr)
```

## Affection and Attachment Subscale

Raw alpha is .80, which is up from .57 previously!

```{r}
wide.affection <- d %>% 
  filter(category == "affection") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.af <- as.matrix(select(wide.affection, -workerid))
alpha(x = alpha.af)

```

## Active Learning Subscale

Raw alpha is .84, which is much higher than previously!

```{r}
wide.active_learning <- d %>% 
  filter(category == "active_learning") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.al <- as.matrix(select(wide.active_learning, -workerid))
alpha(x = alpha.al)
```

# Subscales by demographics

Create a data frame that has subscale scores. 
```{r}
ss <- d %>%
  group_by(workerid, category) %>%
  summarize(rating = mean(rating))

ss <- left_join(ss, subinfo)
```

## By SES

```{r}
ms <- ss %>% 
  filter(ses != "") %>%
  mutate(ses.level = cut(as.numeric(ses), c(0,3,6,10))) %>%
  group_by(ses.level, category) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=ses.level)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Gender

```{r}
ms <- ss %>% 
  filter(gender %in% c("Male","Female")) %>%
  group_by(gender, category) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=gender)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Education

Drop the sparsest groups. 

```{r}
ms <- ss %>% 
  filter(!is.na(education)) %>%
  group_by(education, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=education)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Age

Drop the sparsest groups again. 

```{r}
ms <- ss %>% 
  filter(!is.na(age)) %>%
  group_by(age, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=age)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Children


```{r}
ms <- ss %>% 
  filter(!is.na(children)) %>%
  group_by(children, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=children)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Ethnicity

```{r}
ms <- ss %>% 
  filter(ethnicity != "") %>%
  group_by(ethnicity, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=ethnicity)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

# Factor analysis

Get eigenvalues for determining number of factors. 

```{r}
att.mat <- select(wide.attitudes, -workerid)

ev <- eigen(cor(x=att.mat)) # get eigenvalues

ap <- parallel(subject=nrow(att.mat), var=ncol(att.mat),
               rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```

Now plot factor analysis

Because we predicted 3 factors, I am going with 3 here (confirmatory FA)

In the graph items are organized by category, from Early/Active Learning -> Affection and Attachment -> Rules and Respect. 

Things are looking a bit hazy in terms of individual items mapping onto factors. In particular, most of the Early/Active Learning AND Affection and Attachment items map onto Factor 1. Factor 2 has an almost even mix of all 3 categories. Also, it seems like items related to Rules (Factor 3) are separate from those ostensibly related to Respect (Factor 2). It seems that items related to strict rules are most consistently hanging together across experiments. 

```{r}
item.levels <- c("respect parents teachers","punish misbehavior",
                 "dont interrupt","wait when told","control behavior", 
                 "children should be grateful", "strict rules", 
                 "punish for small rules", "worry about misbehavior", 
                 "dont impose structure","rules prevent tantrums", 
                 "kids should not decide", "strong bond mom", 
                 "safe loving environment", "holding and cradling", 
                 "talk about opinions", "give children comfort", 
                 "talk about emotions", "talk about feelings before mature", 
                 "not spoiled with too much attention", 
                 "too much affection does not harm", 
                 "control emotions if comforted", 
                 "examples are good", "can learn good and bad ", 
                 "follow-in good", "spontaneous play", 
                 "learn before talking", "learn by playing", 
                 "learn contingencies", "learn from repetetive behaviors", 
                 "play pretend", "simple toys", "reasons for rules", 
                 "learn math before school", "learn from other children", 
                 "play with friends", "new experiences", 
                 "reading before school", "nonsense games", 
                 "play freely", "parents choose toys", "reading before speaking")

n.factors <- 3

af <- factanal(x=att.mat, factors = n.factors, scores = "regression")
loadings <- data.frame(af$loadings[,1:n.factors]) %>%
  mutate(item = rownames(af$loadings)) %>%
  gather(factor, loading, starts_with("Factor"))
#
loadings$item <- factor(loadings$item, item.levels)

labels$item <- labels$short_sent
loadings <- join(loadings, labels, by = "item")

qplot(factor, item, fill=loading, geom="tile", data = loadings) + 
  scale_fill_continuous(low="#000000", high="#FFFFFF") + 
  facet_grid(category ~ ., scales = "free_y")

qplot(factor, item, fill=loading > .4, geom="tile", data = loadings) + 
  scale_fill_solarized() + 
  facet_grid(category ~ ., scales = "free_y")
```

Now with four factors, based on the exploratory analyses. 

```{r}
n.factors <- 4

af <- factanal(x=att.mat, factors = n.factors, scores = "regression")
loadings <- data.frame(af$loadings[,1:n.factors]) %>%
  mutate(item = rownames(af$loadings)) %>%
  gather(factor, loading, starts_with("Factor"))

loadings$item <- factor(loadings$item, levels = item.levels)
loadings <- join(loadings, labels, by = "item")

qplot(factor, item, fill=loading, geom="tile", data = loadings) + 
  scale_fill_continuous(low="#000000", high="#FFFFFF") + 
  facet_grid(category ~ ., scales = "free_y")

qplot(factor, item, fill=loading > .4, geom="tile", data = loadings) + 
  scale_fill_solarized() + 
  facet_grid(category ~ ., scales = "free_y")
```

Merge back in subject id info. 

```{r}
a.scores <- af$scores %>%
  data.frame %>%
  mutate(workerid = as.character(wide.attitudes$workerid)) %>%
  left_join(subinfo)
```

## Factors by SES

```{r}
a.factor.names <- c("Early Learning", "Affection", "Rules", "Spoiling kids")

ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ses != "") %>%
  mutate(ses.level = cut(as.numeric(ses), c(0,3,6,10)),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(ses.level, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(ms, aes(factor.name, mean, fill=ses.level)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Gender

```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(gender %in% c("Male","Female")) %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(gender, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(ms, aes(factor.name, mean, fill=gender)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()

```
 
## Factors by Education

```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(education != "") %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(education, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(ms, aes(factor.name, mean, fill=education)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Age

```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(age != "") %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(age, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(ms, aes(factor.name, mean, fill=age)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Children

Do you have children?

```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(children = children %in% c("1","2","3","4","5","morethan5"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(children, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(ms, aes(factor.name, mean, fill=children)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

How many?

```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(n.children = children,
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(n.children, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(ms, aes(factor.name, mean, fill=n.children)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Ethnicity

```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ethnicity != "") %>%
  mutate(hispanic = ethnicity== "Hispanic",
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(hispanic, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(ms, aes(factor.name, mean, fill=hispanic)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
``` 
 
# Conclusions

...