---
title: "Parenting Project Attitudes Questionnaire Experiment 6"
author: "Emily & Mike"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of basic parenting values/attitudes survey, version 2.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}

rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(langcog)
library(plyr); library(dplyr)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(psych)
library(nFactors)

select <- dplyr::select # masked by MASS

theme_set(theme_bw())
```

Read in files and consolidate to the same directory. 

```{r}
files <- dir("../production-results/e6/")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("../production-results/e6/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  # clean up instruction trial
  sent <- jd$answers$data$sentence
  rating <- as.numeric(jd$answers$data$rating) 
  trial_type <- jd$answer$data$trial_type
  sent <- sent[trial_type != "2afc_instructions"]
  trial_type <- trial_type[trial_type != "2afc_instructions"]
  
  #left out race because not sure yet how to deal with list format
  id <- data.frame(workerid = jd$WorkerId, 
                   sent = sent,
                   rating = rating,
                   children = jd$answers$data$children,
                   language = jd$answer$data$homelang,
                   ses = jd$answer$data$ladder,
                   gender = jd$answer$data$gender,
                   age = jd$answer$data$age,
                   education = jd$answer$data$education,
                   ethnicity = jd$answer$data$ethnicity,
                   childAgeYoung = jd$answer$data$childAgeYoung,
                   childAgeOld = jd$answer$data$childAgeOld
                   )
  d.raw <- bind_rows(d.raw, id)
}
```

Map on question short forms so that we can use these instead. 

```{r}
labels <- read.csv("sent_forms_e6.csv")
labels$sent <- as.character(labels$sent)
```

Clean up labels.

```{r}
d.raw$sent <- as.character(d.raw$sent)
d.raw$sent <- str_replace_all(d.raw$sent, "'", "")
d.raw$sent <- str_replace_all(d.raw$sent, "’", "")
d.raw$sent <- str_replace_all(d.raw$sent, "“", "")
d.raw$sent <- str_replace_all(d.raw$sent, "”", "")
d.raw$sent <- str_replace_all(d.raw$sent, "‘", "")
d.raw$sent <- str_replace_all(d.raw$sent, "â", "")

```

Merge.  

```{r}
d <- left_join(d.raw, labels)

#set up reverse code variables so that items don't get reverse coded a second time. 

d$reverse_code[d$reverse_code == 1 & d$rating == "0"] <- 0
d$reverse_code[d$reverse_code == 1 & d$rating == "1"] <- 1
d$reverse_code[d$reverse_code == 1 & d$rating == "2"] <- 2

d$reverse_code[d$reverse_code == 1 & d$rating == "4"] <- 4
d$reverse_code[d$reverse_code == 1 & d$rating == "5"] <- 5
d$reverse_code[d$reverse_code == 1 & d$rating == "6"] <- 6

#reverse code.
d$rating[d$reverse_code == 0 & d$rating == "0"] <- 6
d$rating[d$reverse_code == 1 & d$rating == "1"] <- 5
d$rating[d$reverse_code == 2 & d$rating == "2"] <- 4

d$rating[d$reverse_code == 4 & d$rating == "4"] <- 2
d$rating[d$reverse_code == 5 & d$rating == "5"] <- 1
d$rating[d$reverse_code == 6 & d$rating == "6"] <- 0
```

Plot demographic info.

```{r}
subinfo <- d %>% 
  group_by(workerid) %>%
  summarise(age = age[1],
            gender = gender[1],
            children = children[1],
            ses = ses[1],
            education = education[1],
            language = language[1], 
            ethnicity = ethnicity[1],
            youngestChildAge = childAgeYoung[1],
            oldestChildAge = childAgeOld[1]
            )

subinfo$education <- factor(subinfo$education, levels = c("highSchool","someCollege","4year","someGrad","Grad"))

subinfo$gender <- str_replace_all(subinfo$gender, "female|FEMALE|F$|f$|Femal$|Females|Females","Female")
subinfo$gender <- str_replace_all(subinfo$gender, "^male|^Male|^MALE|^M$|^m$|^Maleq|Make", "Male")
subinfo$gender <- str_replace_all(subinfo$gender, "29|24|25|28|32|33|45", "")
subinfo$gender <- str_replace_all(subinfo$gender, "males", "male")
subinfo$gender <- str_replace_all(subinfo$gender, " ", "")


subinfo$language <- str_replace_all(subinfo$language, "english|eNGLISH|Engliah|ENGLISH|^eng$|Enlgish", "English")
subinfo$language <- str_replace_all(subinfo$language," ", "")
subinfo$language <- str_replace_all(subinfo$language,"arabic", "Arabic")
subinfo$language <- str_replace_all(subinfo$language,"chinese", "Chinese")
subinfo$language <- str_replace_all(subinfo$language,"german", "German")
subinfo$language <- str_replace_all(subinfo$language,"tagalog", "Tagalog")

subinfo$youngestChildAge <- factor(subinfo$youngestChildAge, levels = c("","0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

subinfo$oldestChildAge <- factor(subinfo$oldestChildAge, levels = c("","0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

qplot(ses, data=subinfo)
qplot(children, data=subinfo)
qplot(gender, data=subinfo)
qplot(education, data=subinfo)
qplot(age, data=subinfo)
qplot(language, data=subinfo)
qplot(ethnicity, data=subinfo)
qplot(youngestChildAge, data=subinfo)
qplot(oldestChildAge, data=subinfo)

```

# Basic analyses

Now look at mean ratings across sentences.

```{r}

rating_count <- table(d$rating) 
rating_count
prop.table(rating_count) 

ms <- d %>%
  group_by(category, instrument, short_sent) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(instrument, category, desc(mean)) 

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)

```

Plot attitude.

Ratings are clearly lower for the reverse coded items (the final 2 items in each category); this could be due to response sets (i.e., participants endorsing all items highly). 

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, 
      geom = "pointrange",
      data = filter(ms, instrument == "attitudes")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,6)) + 
  scale_colour_solarized()

```


# Scale reliability

## Whole Scale
This analysis is not especially meaningful as it averages across the three subscales. Raw alpha is .88 which is higher than previous runs.
```{r}
wide.attitudes <- d %>% 
  filter(instrument == "attitudes") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.mat <- as.matrix(select(wide.attitudes, -workerid))
alpha(x = alpha.mat)
```

## Rules and Respect Subscale

Raw alpha is .74 here. 

```{r}
wide.rules_respect <- d %>% 
  filter(category == "rules_respect") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.rr <- as.matrix(select(wide.rules_respect, -workerid))
alpha(x = alpha.rr)
```

## Affection and Attachment Subscale

Raw alpha is .81, which is up from .57 previously!

```{r}
wide.affection <- d %>% 
  filter(category == "affection") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.af <- as.matrix(select(wide.affection, -workerid))
alpha(x = alpha.af)

```

## Active Learning Subscale

Raw alpha is .86, which is much higher than previously!

```{r}
wide.active_learning <- d %>% 
  filter(category == "active_learning") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.al <- as.matrix(select(wide.active_learning, -workerid))
alpha(x = alpha.al)
```


# Factor analysis

Get eigenvalues for determining number of factors. 

```{r}
att.mat <- select(wide.attitudes, -workerid)

ev <- eigen(cor(x=att.mat)) # get eigenvalues

ap <- parallel(subject=nrow(att.mat), var=ncol(att.mat),
               rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```

Now plot factor analysis

Because we predicted 3 factors, I am going with 3 here (confirmatory FA)

In the graph items are organized by category, from Early/Active Learning -> Affection and Attachment -> Rules and Respect. 

Things are looking a bit hazy in terms of individual items mapping onto factors. In particular, most of the Early/Active Learning AND Affection and Attachment items map onto Factor 1. Factor 2 has an almost even mix of all 3 categories. Also, it seems like items related to Rules (Factor 3) are separate from those ostensibly related to Respect (Factor 2). It seems that items related to strict rules are most consistently hanging together across experiments. 

```{r}
n.factors <- 3

af <- factanal(x=att.mat, factors = n.factors, scores = "regression")
loadings <- data.frame(af$loadings[,1:n.factors]) %>%
  mutate(item = rownames(af$loadings)) %>%
  gather(factor, loading, starts_with("Factor"))

labels$item <- labels$short_sent
loadings <- join(loadings, labels, by = "item")

qplot(factor, item, fill=loading, geom="tile", data = loadings) + 
  scale_fill_continuous(low="#000000", high="#FFFFFF") + facet_grid(. ~ category)

qplot(factor, item, fill=loading > .35, geom="tile", data = loadings) + 
  scale_fill_solarized()+ facet_grid(. ~ category)

```

Now with the suggested 5 factors. 

```{r}
n.factors <- 5

af <- factanal(x=att.mat, factors = n.factors, scores = "regression")
loadings <- data.frame(af$loadings[,1:n.factors]) %>%
  mutate(item = rownames(af$loadings)) %>%
  gather(factor, loading, starts_with("Factor"))

loadings <- join(loadings, labels, by = "item")

qplot(factor, item, fill=loading, geom="tile", data = loadings) + 
  scale_fill_continuous(low="#000000", high="#FFFFFF")+ facet_grid(. ~ category)

qplot(factor, item, fill=loading > .35, geom="tile", data = loadings) + 
  scale_fill_solarized()+ facet_grid(. ~ category)+ facet_grid(. ~ category)
```

Merge back in subject id info. 

```{r}
a.scores <- af$scores %>%
  data.frame %>%
  mutate(workerid = as.character(wide.attitudes$workerid)) %>%
  left_join(subinfo)
```

And summary:

## Factors by SES
```{r}
a.factor.names <- c("Active Learning and Affection", "Early Learning, Affection, Respect", "Strict Rules")

ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ses != "") %>%
  mutate(high.ses = ses > 5, 
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(high.ses, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=high.ses, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```


## Factors by Gender
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(gender != "") %>%
  mutate(male.gender = gender == "Male",
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(male.gender, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=male.gender, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```
 
## Factors by Education
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(education != "") %>%
  mutate(high.education = (education == "4year" |education == "someGrad" | education == "Grad"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(high.education, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=high.education, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```

## Factors by Age
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(age != "") %>%
  mutate(young.age = (age == "0-19" |age == "20-29"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(young.age, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=young.age, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```

## Factors by Children
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(n.children = children,
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(n.children, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=n.children, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```

```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(yes.children = (children == "1" | children == "2" | children == "3"| children == "4"| children == "5"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(yes.children, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=yes.children, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

```
 
## Factors by Ethnicity
```{r}
ms <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ethnicity != "") %>%
  mutate(hispanic = ethnicity== "Hispanic",
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(hispanic, factor.name) %>%
  multi_boot_standard(col = "score") 

qplot(factor.name, mean, fill=hispanic, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=ms) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
``` 
 
# Conclusions

Our predicted factor structure did not hold up well. The items that consistently hang together and form their own factor are those related to strict rules. 

Might need to rethink the organization of attitudes. Something separating out parents who see their kids as "projects" versus believing they will naturally thrive might make sense. The grouping of early learning and affection items into one factor might reflect this latent theory.