---
title: "Parenting Project Attitudes Questionnaire Experiment 6"
author: "Emily & Mike"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of basic parenting values/attitudes survey.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}

rm(list=ls())
setwd("~/Desktop/parenting_proj/analysis")
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(langcog)
library(tidyverse)
library(rjson)
library(psych)
library(nFactors)
library(lme4)
library(xtable)

select <- dplyr::select # masked by MASS

theme_set(theme_bw())
```

Read in files and consolidate to the same directory. 

```{r}
files <- dir("../production-results/e9/")
d.raw <- data.frame()


for (f in files) {
  jf <- paste("../production-results/e9/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  # clean up different tasks
  trial_type <- jd$answer$data$trial_type
  
  #parenting questionnaire 
  sent <- jd$answers$data$sentence
  rating <- as.numeric(jd$answers$data$rating)
                       
  sent <- sent[sent != ""]
  # sent <- sent[trial_type != "priorities_instruct"]
  rating <- rating[sent != ""] 
  # rating <- rating[trial_type != "priorities_instruct"] 
  
  #demographics
  race <- as.character(jd$answers$data$race[1])
  
  id <- data.frame(workerid = jd$WorkerId, 
                   sent = sent,
                   rating = rating,
                   children = jd$answers$data$children,
                   language = jd$answers$data$homelang,
                   ses = jd$answers$data$ladder,
                   gender = jd$answers$data$gender,
                   age = jd$answers$data$age,
                   education = jd$answers$data$education,
                   ethnicity = jd$answers$data$ethnicity,
                   childAgeYoung = jd$answers$data$childAgeYoung,
                   childAgeOld = jd$answers$data$childAgeOld,
                   race = race)
  d.raw <- bind_rows(d.raw, id)
}
```


Map on question short forms so that we can use these instead. 

```{r}
labels <- read.csv("sent_forms_e9.csv")
labels$sent <- as.character(labels$sent)
```

Clean up labels.

```{r}
d.raw$sent <- as.character(d.raw$sent)
d.raw$sent <- stringr::str_replace_all(d.raw$sent, "'", "")
d.raw$sent <- stringr::str_replace_all(d.raw$sent, "’", "")
d.raw$sent <- stringr::str_replace_all(d.raw$sent, "“", "")
d.raw$sent <- stringr::str_replace_all(d.raw$sent, "”", "")
d.raw$sent <- stringr::str_replace_all(d.raw$sent, "‘", "")
d.raw$sent <- stringr::str_replace_all(d.raw$sent, "â", "")
```

Merge.  

```{r}
d <- left_join(d.raw, labels)
d$rating[d$reverse_code == 1] <- 6 - d$rating[d$reverse_code == 1]

d_full_e9 <- d
save(d_full_e9, file = "e9_full.RData")
```

Plot demographic info.

```{r}
subinfo <- d %>% 
  group_by(workerid) %>%
  select(workerid, age, gender, children, ses, education, language, 
         ethnicity, childAgeYoung, childAgeOld) %>%
  summarise(age = age[1],
            gender = gender[1],
            children = children[1],
            ses = ses[1],
            education = education[1],
            language = language[1], 
            ethnicity = ethnicity[1],
            childAgeYoung = childAgeYoung[1],
            childAgeOld = childAgeOld[1])

subinfo$education <- factor(subinfo$education, levels = c("highSchool","someCollege","4year","someGrad","Grad"))

subinfo$gender <- stringr::str_replace_all(subinfo$gender, "female|FEMALE|F$|f$|Femal$|Females|Females","Female")
subinfo$gender <- stringr::str_replace_all(subinfo$gender, "^male|^Male|^MALE|^M$|^m$|^Maleq|Make", "Male")
subinfo$gender <- stringr::str_replace_all(subinfo$gender, "29|24|25|28|32|33|45", "")
subinfo$gender <- stringr::str_replace_all(subinfo$gender, "males", "male")
subinfo$gender <- stringr::str_replace_all(subinfo$gender, " ", "")


subinfo$language <- stringr::str_replace_all(subinfo$language, "english|eNGLISH|Engliah|ENGLISH|^eng$|Enlgish", "English")
subinfo$language <- stringr::str_replace_all(subinfo$language," ", "")
subinfo$language <- stringr::str_replace_all(subinfo$language,"arabic", "Arabic")
subinfo$language <- stringr::str_replace_all(subinfo$language,"chinese", "Chinese")
subinfo$language <- stringr::str_replace_all(subinfo$language,"german", "German")
subinfo$language <- stringr::str_replace_all(subinfo$language,"tagalog", "Tagalog")

subinfo$childAgeYoung <- factor(subinfo$childAgeYoung, levels = c("","0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

subinfo$childAgeOld <- factor(subinfo$childAgeOld, levels = c("","0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

subinfo$ses <- factor(subinfo$ses, levels = c("1","2","3","4","5","6","7","8","9","10"))

qplot(ses, data=subinfo)
qplot(children, data=subinfo)
qplot(gender, data=subinfo)
qplot(education, data=subinfo)
qplot(age, data=subinfo)
qplot(language, data=subinfo)
qplot(ethnicity, data=subinfo)
qplot(childAgeYoung, data=subinfo)
qplot(childAgeOld, data=subinfo)
```

# Basic analyses

Now look at mean ratings across sentences.

```{r}
rating_count <- table(d$rating[d$instrument != "priorities"]) 
rating_count

ms <- d %>%
  group_by(category, instrument, short_sent, reverse_code) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(instrument, category, desc(mean)) 

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)

#for comparison with CDM data
e9 <- ms
save(e9, file = "e9.RData")
```

Plot attitude.

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, pch = factor(reverse_code),
      geom = "pointrange",
      data = filter(ms, instrument == "attitudes")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,6)) + 
  scale_colour_solarized()

qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, pch = factor(reverse_code),
      geom = "pointrange",
      data = filter(ms, instrument == "priorities")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,6)) + 
  scale_colour_solarized()

```

Plot mean subscale scores.

```{r}
mc <- d %>%
  group_by(category) %>%
  filter(instrument == "attitudes")%>%
  multi_boot_standard(col = "rating") %>%
  arrange(category, desc(mean)) 

ggplot(mc, aes(x = category, y = mean)) + 
  geom_bar(stat = "identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

mp <- d %>%
  group_by(category) %>%
  filter(instrument == "priorities")%>%
  multi_boot_standard(col = "rating") %>%
  arrange(category, desc(mean)) 

ggplot(mp, aes(x = category, y = mean)) + 
  geom_bar(stat = "identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```


# Scale reliability

## Whole Scale

```{r}
wide.attitudes <- d %>% 
  filter(instrument == "attitudes") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.mat <- as.matrix(select(wide.attitudes, -workerid))
alpha(x = alpha.mat)
```

## Rules and Respect Subscale

```{r}
wide.rules_respect <- d %>% 
  filter(category == "RR") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.rr <- as.matrix(select(wide.rules_respect, -workerid))
alpha(x = alpha.rr)
```

## Affection and Attachment Subscale



```{r}
wide.affection <- d %>% 
  filter(category == "AA") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.af <- as.matrix(select(wide.affection, -workerid))
alpha(x = alpha.af)

```

## Active Learning Subscale


```{r}
wide.active_learning <- d %>% 
  filter(category == "EL") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.al <- as.matrix(select(wide.active_learning, -workerid))
alpha(x = alpha.al)
```

# Subscales by demographics

Create a data frame that has subscale scores. 
```{r}
ss <- d %>%
  filter(instrument == "attitudes")%>%
  dplyr::group_by(workerid, category) %>%
  dplyr::summarise(rating = mean(rating))

ss <- left_join(ss, subinfo)
```

correlation of subscale scores.
```{r}
ss_wide <- ss %>%
  spread(category, rating)%>%
  select(EL, AA, RR)

ctab <- cor(ss_wide)
round(ctab, 2)

```

## Does Subscale Score Predict Parenting Goals?

```{r}
ds <- d
ds$rating <- ave(ds$rating, ds$category, FUN=scale)

ss.goals <- ds %>%
  group_by(workerid, category) %>%
  summarize(rating = mean(rating)) %>%
  spread(category, rating) %>%
  gather("subscale","rating_subscale",AA, EL, RR) %>%
  gather("goal","rating_goal",AA_goals, EL_goals, RR_goals)

ggplot(ss.goals, aes(x = rating_subscale, y = rating_goal, col = subscale)) +
  geom_jitter() + 
  geom_smooth(method="lm", se=FALSE) + 
  facet_wrap(~goal)

```

```{r}

ss.goals <- ds %>%
  group_by(workerid, category) %>%
  summarize(rating = mean(rating)) %>%
  spread(category, rating) %>%
  gather("goal","rating_goal",AA_goals, EL_goals, RR_goals)

lm <- lm(rating_goal ~ 
                 EL*goal +
                 AA*goal +
                 RR*goal, data = ss.goals)

summary(lm)
```


## By SES

```{r}
ms <- ss %>% 
  filter(ses != "") %>%
  mutate(ses.level = cut(as.numeric(ses), c(0,3,6,10))) %>%
  group_by(ses.level, category) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=ses.level)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Gender

```{r}
ms <- ss %>% 
  filter(gender %in% c("Male","Female")) %>%
  group_by(gender, category) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=gender)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()

knitr::kable(coef(summary(lmer(rating ~ category * gender + (1|workerid), 
     data =   ss %>% filter(gender %in% c("Male","Female"))))), digits = 2)
```


## By Parent Status

```{r}
ms <- ss %>% 
  filter(!is.na(children), children != "") %>%
  mutate(parent = children != "0") %>%
  group_by(parent, category) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=parent)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()

```

## By Education

Drop the sparsest groups. 

```{r}
ms <- ss %>% 
  filter(!is.na(education)) %>%
  group_by(education, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=education)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()

ms <- ss %>% 
  filter(!is.na(education)) %>%
  mutate(college_grad = education == "Grad"| education =="4year" | education =="someGrad") %>%
  group_by(college_grad, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=college_grad)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Age

Drop the sparsest groups again. 

```{r}
ms <- ss %>% 
  filter(!is.na(age)) %>%
  group_by(age, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=age)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Children


```{r}
ms <- ss %>% 
  filter(!is.na(children)) %>%
  group_by(children, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=children)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Ethnicity

```{r}
ms <- ss %>% 
  filter(ethnicity != "") %>%
  group_by(ethnicity, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=ethnicity)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

# Factor analysis

Get eigenvalues for determining number of factors. 

```{r}
att.mat <- select(wide.attitudes, -workerid)

ev <- eigen(cor(x=att.mat)) # get eigenvalues

ap <- parallel(subject=nrow(att.mat), var=ncol(att.mat),
               rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```

Now plot factor analysis


```{r}

n.factors <- 3

af <- factanal(x=att.mat, factors = n.factors, scores = "regression")
loadings <- data.frame(af$loadings[,1:n.factors]) %>%
  mutate(item = rownames(af$loadings)) %>%
  gather(factor, loading, starts_with("Factor"))

loadings$item <- factor(loadings$item)

labels$item <- labels$short_sent
loadings <- left_join(loadings, labels, by = "item")

qplot(factor, item, fill=loading, geom="tile", data = loadings) + 
  scale_fill_continuous(low="#000000", high="#FFFFFF") + 
  facet_grid(category ~ ., scales = "free_y")

qplot(factor, item, fill=loading > .35, geom="tile", data = loadings) + 
  scale_fill_solarized() + 
  facet_grid(category ~ ., scales = "free_y")
```


Merge back in subject id info. 

```{r}
a.scores <- af$scores %>%
  data.frame %>%
  mutate(workerid = as.character(wide.attitudes$workerid)) %>%
  left_join(subinfo)
```

## Factors by SES

```{r}
a.factor.names <- c("Affection and Attachment","Early Learning", "Rules and Respect")

mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ses != "") %>%
  mutate(ses.level = cut(as.numeric(ses), c(0,3,6,10)),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(ses.level, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=ses.level)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Gender

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(gender %in% c("Male","Female")) %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(gender, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=gender)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()

```
 
## Factors by Education

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(education != "") %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(education, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=education)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()

mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(education != "") %>%
  mutate(college_grad = education == "Grad"| education =="4year" | education =="someGrad") %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(college_grad, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=college_grad)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()

```

## Factors by Age

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(age != "") %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(age, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=age)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Children

Do you have children?

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(children = children %in% c("1","2","3","4","5","morethan5"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(children, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=children)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

How many?

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(n.children = children,
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(n.children, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=n.children)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Ethnicity

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ethnicity != "") %>%
  mutate(hispanic = ethnicity== "Hispanic",
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(hispanic, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=hispanic)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
``` 
 
 
 
 
 
 
 
# Conclusions


...