---
title: "Parenting behaviors"
author: "Emily"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

# Data preprocessing

Preliminaries.

```{r echo=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(rjson)
library(forcats)
library(tibble)
library(lme4)
library(lmerTest)
library(lavaan)
library(MVN)

select <- dplyr::select # masked by MASS
theme_set(theme_few())
```

Read in participant data.

```{r}
data <- read.csv("../cdm_paq.csv", header =TRUE)
dem <- read.csv("../cdm_paq_dem.csv", header =TRUE)
labels <- read.csv("sent_forms.csv")
labels$sent <- as.character(labels$sent)

questions <- data %>%
  filter(Status == "Response Type")%>%
  select(Q1:Q28)%>%
  gather("item", "sent", Q1:Q28)

d <- data %>%
  filter(Finished == 1)%>%
  mutate(sid = ResponseId)%>%
  select(-Status, -StartDate, - EndDate, - IPAddress, -Progress, -Duration..in.seconds., -Finished, - ResponseId, - RecordedDate, -RecipientLastName, -RecipientFirstName, - RecipientEmail, -ExternalReference, -LocationLatitude, -LocationLongitude, - DistributionChannel)%>%
  select(sid, Q1:Q28)%>%
  gather("item", "rating", Q1:Q28)%>%
  left_join(questions)

subinfo <- dem %>%
  filter(Finished == "True")%>%
  transmute(sid = ResponseId, ethnicity = Q25.1, parent_ed = Q26.1, parent_age = Q27.1, parent_gender = Q28.1, num_kids = Q29, oldest_kid = Q30, youngest_kid = Q32, only_kid = Q33)
```

Make data frames. 

```{r}
d$sent <- stringr::str_replace_all(d$sent, "’", "")

dq <- d %>%
  left_join(labels)

#rescore reverse coded items
dq$rating <- as.numeric(dq$rating)
dq$rating[dq$reverse_code == 1] <- 8 - dq$rating[dq$reverse_code == 1]
```

# PAQ

Test for normality.

```{r}
dq_wide <- dq %>%
  select(sid, short_sent, rating)%>%
  spread(short_sent, rating)

x_vars <- dq_wide %>%
  select(-sid)

uniPlot(x_vars[1:10], type = "histogram")
uniPlot(x_vars[11:20], type = "histogram")
uniPlot(x_vars[21:24], type = "histogram")

#histograms for CDM
 
 #get subset for plotting
 hist_items <- c("Q8", "Q22", "Q12", "Q16") 

 hist <- d %>%
   select(sid, item, rating)%>%
   filter(item %in% hist_items)%>%
   spread(item, rating)
 
 ggplot(hist, aes(Q8, fill = Q8)) +
  geom_histogram(stat = "count") 

 ggplot(hist, aes(Q22, fill = Q22)) +
  geom_histogram(stat = "count") 
 
  ggplot(hist, aes(Q12, fill = Q12)) +
  geom_histogram(stat = "count") 
  
   ggplot(hist, aes(Q16, fill = Q16)) +
  geom_histogram(stat = "count") 
 
#get highest and lowest rated items   
d$sent <- stringr::str_replace_all(d$sent, "’", "")

dqg <- d %>%
  left_join(labels)

dqg$rating <- as.numeric(dqg$rating)   

ms <- dqg %>%
  group_by(category, short_sent, reverse_code) %>%
  multi_boot_standard(col = "rating", na.rm = TRUE) 
```

Get mean ratings for sentences.
```{r}
dq$rating <- dq$rating - 1

ms <- dq %>%
  group_by(category, short_sent, reverse_code) %>%
  multi_boot_standard(col = "rating", na.rm = TRUE) %>%
  arrange(category, desc(mean)) 

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)

short_sent_ord <- ms$short_sent_ord
```

Plot responses to individual questionnaire items.

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, pch = factor(reverse_code),
      geom = "pointrange",
      data = ms) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,6)) + 
  scale_colour_solarized()
```

Compare to Mturk samples. We are comparing the data collected from CDM parents to experiment 9 (parents and non-parents) of the questionnaire norming study and the data from the parenting behaviors study (self-reported parents).

```{r}
cdm <- ms %>%
  ungroup()%>%
  select(category, short_sent, mean, ci_upper, ci_lower)%>%
  mutate(sample = "cdm")

load("e9.RData")
load("beh.RData")
load("e9_full.RData")
load("beh_dq.RData")

beh_d <- beh %>%
  ungroup()%>%
  mutate(category = category_paq)%>%
  select(category, short_sent, mean, ci_upper, ci_lower)%>%
  mutate(sample = "mturk1")
  
atts <- c("AA", "EL","RR")

e9_d <- e9 %>%
  filter(category %in% atts)%>%
  ungroup()%>%
  select(category, short_sent, mean, ci_upper, ci_lower)%>%
  mutate(sample = "mturk2")

ss_cdm <- dq %>%
  dplyr::group_by(sid, category) %>%
  dplyr::summarise(rating = mean(rating))%>%
  mutate(sample = "cdm")

ss_e9 <- d_full_e9 %>%
  filter(category %in% atts)%>%
  mutate(sid = workerid)%>%
  select(-workerid)%>%
  dplyr::group_by(sid, category) %>%
  dplyr::summarise(rating = mean(rating)) %>%
  mutate(sample = "mturk1")

ss_beh <- beh_dq %>%
  dplyr::group_by(sid, category_paq) %>%
  dplyr::summarise(rating = mean(rating)) %>%
  mutate(category = category_paq)%>%
  select(-category_paq)%>%
  mutate(sample = "mturk2")

ss_cdm$rating <- as.numeric(ss_cdm$rating)
ss_beh$rating <- as.numeric(ss_beh$rating)
ss_e9$rating <- as.numeric(ss_e9$rating)

ss_cdm$category <- as.factor(as.character(ss_cdm$category))
ss_beh$category <- as.factor(as.character(ss_beh$category))
ss_e9$category <- as.factor(as.character(ss_e9$category))

ss_compare<- bind_rows(ss_cdm, ss_beh)%>%
  bind_rows(ss_e9)

samp_compare <- e9_d %>%
  bind_rows(cdm)%>%
  bind_rows(beh_d)

samp_compare$short_sent <- factor(samp_compare$short_sent, levels = short_sent_ord)

samp_compare$sample <- factor(samp_compare$sample, levels = c("cdm","mturk1","mturk2"))

ss_compare$sample <- factor(ss_compare$sample, levels = c("cdm","mturk1","mturk2"))
ss_compare$category <- factor(ss_compare$category, levels = c("AA","EL","RR"))

qplot(short_sent, mean, col = sample,
      ymin = ci_lower, ymax = ci_upper,
      geom = "pointrange",
      data = samp_compare) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,6)) + 
  scale_colour_solarized()

#plot subset of questions for delivery to CDM parents.

cdm_items <- c("learn before speaking", "read to kids", "learn by playing", "explore and experiment")

ggplot(filter(samp_compare, short_sent %in% cdm_items), aes(short_sent, mean, fill=sample)) +
  geom_bar(stat="identity", position = "dodge")
```

CDM parents agree more with EL items related to exploration and play but less on teaching math before school compared to Mturk. They also rate RR items quite a bit lower than Mturk samples. 

In general there is a bit more variability in agreement with items within subscales compared to Mturk samples. 

Plot mean subscale scores.

```{r}
atts_m <- dq %>%
  group_by(category) %>%
  multi_boot_standard(col = "rating", na.rm = TRUE) %>%
  arrange(category, desc(mean)) 

ggplot(atts_m, aes(x = category, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+ 
  ylim(c(0,6)) 
```


# Scale reliability

## Whole Scale

```{r}
wide.paq <- dq %>% 
  select(sid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.rr <- as.matrix(select(wide.paq, -sid))
psych::alpha(x = alpha.rr)
```

## Rules and Respect Subscale

```{r}
wide.paq <- dq %>% 
  filter(category == "RR") %>%
  select(sid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.rr <- as.matrix(select(wide.paq, -sid))
psych::alpha(x = alpha.rr)
```

## Affection and Attachment Subscale

```{r}
wide.paq <- dq %>% 
  filter(category == "AA") %>%
  select(sid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.aa <- as.matrix(select(wide.paq, -sid))
psych::alpha(x = alpha.aa)
```

## Early Learning Subscale

```{r}
wide.paq <- dq %>% 
  filter(category == "EL") %>%
  select(sid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.el <- as.matrix(select(wide.paq, -sid))
psych::alpha(x = alpha.el)
```

# Demographics

Create a data frame that has subscale scores. 
```{r}
ss <- dq %>%
  dplyr::group_by(sid, category) %>%
  dplyr::summarise(rating = mean(rating))

ss <- left_join(ss, subinfo)
```

## By Gender
  
```{r echo = FALSE}

gender <- c("Male", "Female")
qplot(parent_gender, data=filter(subinfo, parent_gender %in% gender), fill = parent_gender)

ms <- ss %>% 
  filter(parent_gender %in% c("Male","Female")) %>%
  group_by(parent_gender, category) %>%
  multi_boot_standard(col = "rating")

ggplot(ms, aes(category, mean, fill=parent_gender)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few()+ 
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  scale_fill_discrete(name="Parent Gender")+ 
  theme(legend.title = element_text(size=16), 
        legend.text = element_text(size=14), 
        axis.text.x  = element_text(vjust=0.5, size=14),
        axis.title.x = element_text(size=16), 
        axis.text.y  = element_text(vjust=0.5, size=14),
        axis.title.y = element_text(size=16))

ss$category <- relevel(ss$category, ref = "EL")
ss$parent_gender <- relevel(ss$parent_gender, ref = "Male")

knitr::kable(coef(summary(lmer(rating ~ category * parent_gender + (1|sid), 
     data =   ss %>% filter(parent_gender %in% c("Male","Female"))))))
```

Women agree with AA items more than men.

## By Parent Age
  
```{r echo = FALSE}
qplot(parent_age, data= filter(subinfo, parent_age != "", parent_age != "Under 18"), fill = parent_age)

ms <- ss %>% 
  group_by(parent_age, category) %>%
  filter(n() > 20)%>%
  multi_boot_standard(col = "rating")

ggplot(ms, aes(category, mean, fill=parent_age)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few()+ 
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  scale_fill_discrete(name="Parent Age")+ 
  theme(legend.title = element_text(size=16), 
        legend.text = element_text(size=14), 
        axis.text.x  = element_text(vjust=0.5, size=14),
        axis.title.x = element_text(size=16), 
        axis.text.y  = element_text(vjust=0.5, size=14),
        axis.title.y = element_text(size=16))

ss_age <- ss%>%
  group_by(parent_age, category)%>%
  filter(n() > 20)%>%
  mutate(parent_age_con = "")

ss_age$category <- relevel(ss_age$category, ref = "EL")

ss_age$parent_age_con[ss_age$parent_age == "Under 18"] <- 18
ss_age$parent_age_con[ss_age$parent_age == "18 - 24"] <- 21
ss_age$parent_age_con[ss_age$parent_age == "25 - 34"] <- 30
ss_age$parent_age_con[ss_age$parent_age == "35 - 44"] <- 40
ss_age$parent_age_con[ss_age$parent_age == "45 - 54"] <- 50
ss_age$parent_age_con[ss_age$parent_age == "65 - 74"] <- 60

ss_age$parent_age_con <- as.numeric(ss_age$parent_age_con)

knitr::kable(coef(summary(lmer(rating ~ category * parent_age_con + (1|sid), 
     data =   ss_age))))
```

There is a small effect of age such that older parents agree less with AA items.

## By Education
  
Unfortunately there is not much variability in Parent Education- most respondants have at least a college education.   
```{r echo = FALSE}
subinfo$parent_ed <- factor(subinfo$parent_ed, levels = c("Less than high school","High school graduate","Some college","2 year degree","4 year degree", "Professional degree", "Doctorate"))

qplot(parent_ed, data=filter(subinfo, !is.na(parent_ed)), fill = parent_ed)

ss_ed <- ss %>%
  group_by(parent_ed, category)%>%
  filter(n() > 20)%>%
  mutate(parent_ed_con = "")

ss_ed$parent_ed_con[ss_ed$parent_ed == "Less than high school"] <- 12
ss_ed$parent_ed_con[ss_ed$parent_ed == "High school graduate"] <- 12
ss_ed$parent_ed_con[ss_ed$parent_ed == "Some college"] <-14
ss_ed$parent_ed_con[ss_ed$parent_ed == "2 year degree"] <- 14
ss_ed$parent_ed_con[ss_ed$parent_ed == "4 year degree"] <- 16
ss_ed$parent_ed_con[ss_ed$parent_ed == "Professional degree"] <- 19
ss_ed$parent_ed_con[ss_ed$parent_ed == "Doctorate"] <- 23

ss_ed$parent_ed_con <- as.numeric(ss_ed$parent_ed_con)

ss$parent_ed <- factor(ss$parent_ed, levels = c("Less than high school","High school graduate","Some college","2 year degree","4 year degree", "Professional degree", "Doctorate"))

ms <- ss %>% 
  group_by(parent_ed, category) %>%
  filter(n() > 20)%>%
  multi_boot_standard(col = "rating")

ggplot(ms, aes(category, mean, fill=parent_ed)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few()+ 
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  scale_fill_discrete(name="Parent Education")+ 
  theme(legend.title = element_text(size=16), 
        legend.text = element_text(size=14), 
        axis.text.x  = element_text(vjust=0.5, size=14),
        axis.title.x = element_text(size=16), 
        axis.text.y  = element_text(vjust=0.5, size=14),
        axis.title.y = element_text(size=16))

knitr::kable(coef(summary(lmer(rating ~ category * scale(parent_ed_con) + (1|sid), 
     data =ss_ed))))
```

There is a small effect of parent education such that parents with higher levels of education agree more with EL items.

## By Number of Kids
  
```{r echo = FALSE}
qplot(num_kids, data=filter(subinfo, num_kids != ""), fill = num_kids)

ms <- ss %>% 
  group_by(num_kids, category) %>%
  filter(n() > 5)%>%
  multi_boot_standard(col = "rating")

ms$num_kids <- as.factor(ms$num_kids)

ggplot(ms, aes(category, mean, fill=num_kids)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few()+ 
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  scale_fill_discrete(name="Number of Children")+ 
  theme(legend.title = element_text(size=16), 
        legend.text = element_text(size=14), 
        axis.text.x  = element_text(vjust=0.5, size=14),
        axis.title.x = element_text(size=16), 
        axis.text.y  = element_text(vjust=0.5, size=14),
        axis.title.y = element_text(size=16))

ss <- ss%>%
  group_by(num_kids, category)%>%
  filter(n() > 20)

ss$num_kids <- as.numeric(as.character(ss$num_kids))


ss$category <- relevel(ss$category, ref = "EL")

knitr::kable(coef(summary(lmer(rating ~ category * num_kids + (1|sid), 
     data =ss))))
```

With more kids, parents agree more with RR itmes and less with AA and EL items. 

## By Ethnicity
  
```{r echo = FALSE}
eth <- c("Black or African American", "White", "Asian", "Native Hawaiian or Pacific Islander", "American Indian or Alaska Native", "Hispanic or Latino")

top <- c ("White", "Asian", "Hispanic or Latino")
qplot(ethnicity, data=filter(subinfo, ethnicity %in% eth), fill = ethnicity)

ms <- ss %>% 
  group_by(ethnicity, category) %>%
  filter(n() > 5)%>%
  filter(ethnicity %in% eth)%>%
  multi_boot_standard(col = "rating")

ggplot(ms, aes(category, mean, fill=ethnicity)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few()+ 
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  scale_fill_discrete(name="Ethnicity")+ 
  theme(legend.title = element_text(size=16), 
        legend.text = element_text(size=14), 
        axis.text.x  = element_text(vjust=0.5, size=14),
        axis.title.x = element_text(size=16), 
        axis.text.y  = element_text(vjust=0.5, size=14),
        axis.title.y = element_text(size=16))

ss$ethnicity <- relevel(ss$ethnicity, ref = "White")

knitr::kable(coef(summary(lmer(rating ~ category * ethnicity + (1|sid), 
     data =filter(ss, ethnicity %in% top)))))
```

## By Sample
  
```{r echo = FALSE}
ms_compare <- ss_compare %>% 
  filter(sample == "cdm") %>%
  group_by(category)%>%
  multi_boot_standard(col = "rating")%>%
  mutate(sample = "cdm")

ms_compare_1 <- ss_compare %>% 
  filter(sample == "mturk1") %>%
  group_by(category)%>%
  multi_boot_standard(col = "rating")%>%
  mutate(sample = "mturk1")

ms_compare_2 <- ss_compare %>% 
  filter(sample == "mturk2") %>%
  group_by(category)%>%
  multi_boot_standard(col = "rating")%>%
  mutate(sample = "mturk2")

ms_comp <- bind_rows(ms_compare, ms_compare_1)%>%
  bind_rows(ms_compare_2)

ggplot(ms_comp, aes(category, mean, fill=sample)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  xlab("PAQ Subscale") + 
  ylab("PAQ Score") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few()+ 
  scale_y_continuous(limits=c(0,6), breaks=c(0,2,4,6))+ 
  scale_fill_discrete(name="Sample")+ 
  theme(legend.title = element_text(size=16), 
        legend.text = element_text(size=14), 
        axis.text.x  = element_text(vjust=0.5, size=14),
        axis.title.x = element_text(size=16), 
        axis.text.y  = element_text(vjust=0.5, size=14),
        axis.title.y = element_text(size=16))

knitr::kable(coef(summary(lmer(rating ~ category * sample + (1|sid), 
     data =   ss_compare))))

t.test(ss_compare$rating[ss_compare$sample == "cdm" & ss_compare$category == "AA"],
       ss_compare$rating[ss_compare$sample == "mturk1" & ss_compare$category == "AA"],
       paired = FALSE)

t.test(ss_compare$rating[ss_compare$sample == "cdm" & ss_compare$category == "AA"],
       ss_compare$rating[ss_compare$sample == "mturk2" & ss_compare$category == "AA"],
       paired = FALSE)

t.test(ss_compare$rating[ss_compare$sample == "mturk1" & ss_compare$category == "AA"],
       ss_compare$rating[ss_compare$sample == "mturk2" & ss_compare$category == "AA"],
       paired = FALSE)

t.test(ss_compare$rating[ss_compare$sample == "cdm" & ss_compare$category == "EL"],
       ss_compare$rating[ss_compare$sample == "mturk1" & ss_compare$category == "EL"],
       paired = FALSE)

t.test(ss_compare$rating[ss_compare$sample == "cdm" & ss_compare$category == "EL"],
       ss_compare$rating[ss_compare$sample == "mturk2" & ss_compare$category == "EL"],
       paired = FALSE)

t.test(ss_compare$rating[ss_compare$sample == "mturk1" & ss_compare$category == "EL"],
       ss_compare$rating[ss_compare$sample == "mturk2" & ss_compare$category == "EL"],
       paired = FALSE)

t.test(ss_compare$rating[ss_compare$sample == "cdm" & ss_compare$category == "RR"],
       ss_compare$rating[ss_compare$sample == "mturk1" & ss_compare$category == "RR"],
       paired = FALSE)

t.test(ss_compare$rating[ss_compare$sample == "cdm" & ss_compare$category == "RR"],
       ss_compare$rating[ss_compare$sample == "mturk2" & ss_compare$category == "RR"],
       paired = FALSE)

t.test(ss_compare$rating[ss_compare$sample == "mturk1" & ss_compare$category == "RR"],
       ss_compare$rating[ss_compare$sample == "mturk2" & ss_compare$category == "RR"],
       paired = FALSE)
```