---
title: "Parenting Project Attitudes Questionnaire Experiment 6"
author: "Emily & Mike"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of basic parenting values/attitudes survey.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}

rm(list=ls())

setwd("~/Desktop/parenting_proj/analysis")

knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(psych)
library(langcog)
library(dplyr)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
<<<<<<< HEAD
library(psych)
library(nFactors)
library(lme4)
=======
# library(nFactors)
>>>>>>> 03bd8486849bcf00b2318d10da550f6cf66fb645

select <- dplyr::select # masked by MASS

theme_set(theme_bw())
```

Read in files and consolidate to the same directory. 

```{r}
files <- dir("../production-results/uptake_e1/")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("../production-results/uptake_e1/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  # clean up different tasks
  trial_type <- jd$answer$data$trial_type
  
  #parenting questionnaire 
  sent <- jd$answers$data$sentence[trial_type != "uptake"]
  rating <- as.numeric(jd$answers$data$rating[trial_type != "uptake"]) 
  
  #uptake experiment
  control_recall_1 = jd$answers$data$answer[1]
  control_recall_2 = jd$answers$data$answer[2]
  control_recall_3 = jd$answers$data$answer[3]
  control_recall_4 = jd$answers$data$answer[4]
  control_recall_5 = jd$answers$data$answer[5]
  target_generalize_1 = jd$answers$data$answer[6]
  target_generalize_2 = jd$answers$data$answer[7]
  target_generalize_3 = jd$answers$data$answer[8]
  target_generalize_4 = jd$answers$data$answer[9]
  target_generalize_5 = jd$answers$data$answer[10]
  target_recall_1 = jd$answers$data$answer[11]
  target_recall_2 = jd$answers$data$answer[12]
  target_recall_3 = jd$answers$data$answer[13]
  target_recall_4 = jd$answers$data$answer[14]
  target_recall_5 = jd$answers$data$answer[15]
  reading_time_target = jd$answers$data$target_rt[1]
  reading_time_control = jd$answers$data$control_rt[1]
  time_questionnaire = jd$answers$data$questionnaire_rt[1]
  
  
  #demographics
  race <- as.character(jd$answers$data$race[1])
  
  id <- data.frame(workerid = jd$WorkerId, 
                   sent = sent,
                   rating = rating,
                   enjoy_target = jd$answers$data$enjoy_target,
                   enjoy_control = jd$answers$data$enjoy_control,
                   reading_ease_target = jd$answers$data$reading_ease_target,
                   reading_ease_control = jd$answers$data$reading_ease_control,
                   target_recall_1 = target_recall_1,
                   target_recall_2 = target_recall_2,
                   target_recall_3 = target_recall_3,
                   target_recall_4 = target_recall_4,
                   target_recall_5 = target_recall_5,
                   target_generalize_1 = target_generalize_1,
                   target_generalize_2 = target_generalize_2,
                   target_generalize_3 = target_generalize_3,
                   target_generalize_4 = target_generalize_4,
                   target_generalize_5 = target_generalize_5,
                   control_recall_1 = control_recall_1,
                   control_recall_2 = control_recall_2,
                   control_recall_3 = control_recall_3,
                   control_recall_4 = control_recall_4,
                   control_recall_5 = control_recall_5,
                   children = jd$answers$data$children,
                   language = jd$answers$data$homelang,
                   ses = jd$answers$data$ladder,
                   gender = jd$answers$data$gender,
                   age = jd$answers$data$age,
                   education = jd$answers$data$education,
                   ethnicity = jd$answers$data$ethnicity,
                   childAgeYoung = jd$answers$data$childAgeYoung,
                   childAgeOld = jd$answers$data$childAgeOld,
                   race = race,
                   reading_time_target = reading_time_target,
                   reading_time_control = reading_time_control,
                   time_questionnaire = time_questionnaire)
  d.raw <- bind_rows(d.raw, id)
}
```

Map on question short forms so that we can use these instead. 

```{r}
labels <- read.csv("sent_forms_e7.csv")
labels$sent <- as.character(labels$sent)
```

Clean up labels.

```{r}
d.raw$sent <- as.character(d.raw$sent)
d.raw$sent <- str_replace_all(d.raw$sent, "'", "")
d.raw$sent <- str_replace_all(d.raw$sent, "’", "")
d.raw$sent <- str_replace_all(d.raw$sent, "“", "")
d.raw$sent <- str_replace_all(d.raw$sent, "”", "")
d.raw$sent <- str_replace_all(d.raw$sent, "‘", "")
d.raw$sent <- str_replace_all(d.raw$sent, "â", "")
```

Merge. Recode uptake answers by accuracy.  

```{r}
d <- left_join(d.raw, labels)
d$rating[d$reverse_code == 1] <- 6 - d$rating[d$reverse_code == 1]

d$target_generalize_1 <- str_replace(d$target_generalize_1, "b","1")
d$target_generalize_1 <- str_replace(d$target_generalize_1, "a|c","0")
d$target_generalize_2 <- str_replace(d$target_generalize_2, "a","1")
d$target_generalize_2 <- str_replace(d$target_generalize_2, "b|c","0")
d$target_generalize_3 <- str_replace(d$target_generalize_3, "b","1")
d$target_generalize_3 <- str_replace(d$target_generalize_3, "a|c","0")
d$target_generalize_4 <- str_replace(d$target_generalize_4, "c","1")
d$target_generalize_4 <- str_replace(d$target_generalize_4, "a|b","0")
d$target_generalize_5 <- str_replace(d$target_generalize_5, "c","1")
d$target_generalize_5 <- str_replace(d$target_generalize_5, "a|b","0")

d$target_recall_1 <- str_replace(d$target_recall_1, "b","1")
d$target_recall_1 <- str_replace(d$target_recall_1, "a|c","0")
d$target_recall_2 <- str_replace(d$target_recall_2, "a","1")
d$target_recall_2 <- str_replace(d$target_recall_2, "b|c","0")
d$target_recall_3 <- str_replace(d$target_recall_3, "a","1")
d$target_recall_3 <- str_replace(d$target_recall_3, "b|c","0")
d$target_recall_4 <- str_replace(d$target_recall_4, "a","1")
d$target_recall_4 <- str_replace(d$target_recall_4, "b|c","0")
d$target_recall_5 <- str_replace(d$target_recall_5, "c","1")
d$target_recall_5 <- str_replace(d$target_recall_5, "a|b","0")

d$control_recall_1 <- str_replace(d$control_recall_1, "a","1")
d$control_recall_1 <- str_replace(d$control_recall_1, "b|c","0")
d$control_recall_2 <- str_replace(d$control_recall_2, "c","1")
d$control_recall_2 <- str_replace(d$control_recall_2, "a|b","0")
d$control_recall_3 <- str_replace(d$control_recall_3, "a","1")
d$control_recall_3 <- str_replace(d$control_recall_3, "b|c","0")
d$control_recall_4 <- str_replace(d$control_recall_4, "c","1")
d$control_recall_4 <- str_replace(d$control_recall_4, "a|b","0")
d$control_recall_5 <- str_replace(d$control_recall_5, "b","1")
d$control_recall_5 <- str_replace(d$control_recall_5, "a|c","0")
```

Plot demographic info.

```{r}
subinfo <- d %>%
  group_by(workerid) %>%
  select(-short_sent, -category, -instrument, -reverse_code) %>%
  distinct 

questions <- subinfo %>%
  select(workerid, starts_with("target"), starts_with("control")) %>%
  gather(question, correct, starts_with("target"), starts_with("control")) %>%
  separate(question, c("passage","trial_type","q_num"), sep = "_") %>%
  group_by(workerid, passage, trial_type) %>%
  summarise(correct = mean(as.numeric(correct))) %>%
  unite(trialtype, passage, trial_type) %>%
  spread(trialtype, correct)

subinfo <- subinfo %>%
  select(-starts_with("target"), -starts_with("control")) %>%
  left_join(questions)
```

Awful recoding. 

```{r}
subinfo$education <- factor(subinfo$education, 
                            levels = c("highSchool","someCollege","4year","someGrad","Grad"))

subinfo$gender <- str_replace_all(subinfo$gender, 
                              "female|FEMALE|F$|f$|Femal$|Females|Females","Female")
subinfo$gender <- str_replace_all(subinfo$gender, 
                                  "^male|^Male|^MALE|^M$|^m$|^Maleq|Make", "Male")
subinfo$gender <- str_replace_all(subinfo$gender, 
                                  "29|24|25|28|32|33|45", "")
subinfo$gender <- str_replace_all(subinfo$gender, 
                                  "males", "male")
subinfo$gender <- str_replace_all(subinfo$gender, " ", "")

subinfo$language <- str_replace_all(subinfo$language, "english|eNGLISH|Engliah|ENGLISH|^eng$|Enlgish", "English")
subinfo$language <- str_replace_all(subinfo$language," ", "")
subinfo$language <- str_replace_all(subinfo$language,"arabic", "Arabic")
subinfo$language <- str_replace_all(subinfo$language,"chinese", "Chinese")
subinfo$language <- str_replace_all(subinfo$language,"german", "German")
subinfo$language <- str_replace_all(subinfo$language,"tagalog", "Tagalog")

subinfo$youngestChildAge <- factor(subinfo$childAgeYoung, levels = c("","0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

subinfo$oldestChildAge <- factor(subinfo$childAgeOld, levels = c("","0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

subinfo$reading_ease_target <- factor(subinfo$reading_ease_target, levels = c("Very Difficult", "Somewhat Difficult", "Somewhat Easy", "Very Easy"))

subinfo$reading_ease_control <- factor(subinfo$reading_ease_control, levels = c("Very Difficult", "Somewhat Difficult", "Somewhat Easy", "Very Easy"))

subinfo$enjoy_target <- factor(subinfo$enjoy_target, levels = c("Very Unenjoyable", "Somewhat Unenjoyable", "Somewhat Enjoyable", "Very Enjoyable"))

subinfo$enjoy_control <- factor(subinfo$enjoy_control, levels = c("Very Unenjoyable", "Somewhat Unenjoyable", "Somewhat Enjoyable", "Very Enjoyable"))
```

```{r}
qplot(ses, data=subinfo)
qplot(children, data=subinfo)
qplot(gender, data=subinfo)
qplot(education, data=subinfo)
qplot(age, data=subinfo)
qplot(language, data=subinfo)
qplot(ethnicity, data=subinfo)
qplot(race, data=subinfo)
qplot(youngestChildAge, data=subinfo)
qplot(oldestChildAge, data=subinfo)
qplot(reading_ease_target, data=subinfo)
qplot(reading_ease_control, data=subinfo)
qplot(enjoy_target, data=subinfo)
qplot(enjoy_control, data=subinfo)

describe(subinfo$target_recall, skew=FALSE, check=FALSE)
describe(subinfo$control_recall, skew=FALSE, check=FALSE)
describe(subinfo$target_generalize, skew=FALSE, check=FALSE)
describe(subinfo$reading_time_target, skew=FALSE, check=FALSE)
describe(subinfo$reading_time_control, skew=FALSE, check=FALSE)

qplot(reading_time_target, mean_target_recall, data=subinfo)
qplot(reading_time_target, mean_target_generalize, data=subinfo)
qplot(reading_time_control, mean_control_recall, data=subinfo)

```

# Basic analyses

Now look at mean ratings across sentences.

```{r}
rating_count <- table(d$rating) 
rating_count
prop.table(rating_count) 

ms <- d %>%
  group_by(category, instrument, short_sent, reverse_code) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(instrument, category, desc(mean)) 

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)

```

Plot attitude.

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, pch = factor(reverse_code),
      geom = "pointrange",
      data = filter(ms, instrument == "attitudes")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,6)) + 
  scale_colour_solarized()

```

Plot mean subscale scores.

```{r}
mc <- d %>%
  group_by(category) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(category, desc(mean)) 

ggplot(mc, aes(x = category, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```

```{r}
mcl <- d %>%
  group_by(category, workerid) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(category, desc(mean))%>%
  spread(category, mean) 
  
```

# Scale reliability

## Whole Scale

```{r}
wide.attitudes <- d %>% 
  filter(instrument == "attitudes") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.mat <- as.matrix(select(wide.attitudes, -workerid))
summary(alpha(x = alpha.mat))
```

## Rules and Respect Subscale

```{r}
wide.rules_respect <- d %>% 
  filter(category == "rules_respect") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.rr <- as.matrix(select(wide.rules_respect, -workerid))
summary(alpha(x = alpha.rr))
```

## Affection and Attachment Subscale

```{r}
wide.affection <- d %>% 
  filter(category == "affection") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.af <- as.matrix(select(wide.affection, -workerid))
<<<<<<< HEAD
alpha(x = alpha.af)
=======
summary(alpha(x = alpha.af))
>>>>>>> 03bd8486849bcf00b2318d10da550f6cf66fb645
```

## Active Learning Subscale

```{r}
wide.active_learning <- d %>% 
  filter(category == "active_learning") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.al <- as.matrix(select(wide.active_learning, -workerid))
summary(alpha(x = alpha.al))
```

# Information Uptake Analyses

Create a data frame that has subscale scores. 
```{r}
ss <- d %>%
  group_by(workerid, category) %>%
  summarize(rating = mean(rating))

ss <- left_join(ss, subinfo)

```

## Separate Regressions of Recall and Generalization on Subscale Scores

Visually it appears that active learning subscore is most predictive of generalization and recall of the target article, but no difference for the control article!
```{r}
#Separate regressions of recall on subscale score for each category
qplot(rating, mean_control_recall, data=ss, geom=c("point", "smooth"), 
   method="lm", formula=y~x, color=category, 
   main="Regression of control recall on subscale score", 
   xlab="Subscale Score", ylab="Mean Target Recall")

#Separate regressions of generalization on subscale score for each category
qplot(rating, mean_target_recall, data=ss, geom=c("point", "smooth"), 
   method="lm", formula=y~x, color=category, 
   main="Regression of target recall on subscale score", 
   xlab="Subscale Score", ylab="Mean Target Recall")

#Separate regressions of generalization on subscale score for each category
qplot(rating, mean_target_generalize, data=ss, geom=c("point", "smooth"), 
   method="lm", formula=y~x, color=category, 
   main="Regression of target generalization on subscale score", 
   xlab="Subscale Score", ylab="Mean Target Recall")
```

Mixed Effects Model.
Gather recall types.
```{r}
ssr <- ss %>%
  gather(task, accuracy, mean_target_recall:mean_control_recall)%>%
  spread(category, rating)

#glmer( accuracy ~task * category + (1 | workerid), family = "binomial") 

```

Create a wide data frame that has subscale scores. 

In these seperate multiple regressions, active learning and affection scores predict target recall; only active learning scores predict target generalization; no subscale predicts control recall. 
```{r}
wide_ss <- ss %>%
  spread(category, rating)

# Multiple Linear Regression of Recall on Subscale Scores
fit <- lm(mean_control_recall ~ active_learning + affection + rules_respect, data=wide_ss)
summary(fit) # show results

# Multiple Linear Regression of Recall on Subscale Scores
fit <- lm(mean_target_recall ~ active_learning + affection + rules_respect, data=wide_ss)
summary(fit) # show results

# Multiple Linear Regression of Recall on Subscale Scores
fit <- lm(mean_target_generalize ~ active_learning + affection + rules_respect, data=wide_ss)
summary(fit) # show results

```

## Median Splits on Subscales.
Perform median splits on subscales.

```{r}
rr_med <-describe(wide_ss$rules_respect)
al_med <-describe(wide_ss$active_learning)
a_med <-describe(wide_ss$affection)

wide_ss$rr_split[wide_ss$rules_respect <= rr_med$median] <- "low"
wide_ss$rr_split[wide_ss$rules_respect > rr_med$median] <- "high"

wide_ss$al_split[wide_ss$active_learning <= al_med$median] <- "low"
wide_ss$al_split[wide_ss$active_learning > al_med$median] <- "high"

wide_ss$a_split[wide_ss$affection <= a_med$median] <- "low"
wide_ss$a_split[wide_ss$affection > a_med$median] <- "high"

describeBy(wide_ss$mean_control_recall, group=wide_ss$rr_split)
describeBy(wide_ss$mean_target_recall, group=wide_ss$rr_split)
describeBy(wide_ss$mean_target_generalize, group=wide_ss$rr_split)

describeBy(wide_ss$mean_control_recall, group=wide_ss$al_split)
describeBy(wide_ss$mean_target_recall, group=wide_ss$al_split)
describeBy(wide_ss$mean_target_generalize, group=wide_ss$al_split)

describeBy(wide_ss$mean_control_recall, group=wide_ss$a_split)
describeBy(wide_ss$mean_target_recall, group=wide_ss$a_split)
describeBy(wide_ss$mean_target_generalize, group=wide_ss$a_split)
```


# Subscales by demographics
## By SES

```{r}
ms <- ss %>% 
  filter(ses != "") %>%
  mutate(ses.level = cut(as.numeric(ses), c(0,3,6,10))) %>%
  group_by(ses.level, category) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=ses.level)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Race

Drop the sparsest groups. 

```{r}
ms <- ss %>% 
  filter(race != "NULL") %>%
  group_by(race, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating")
  
ggplot(ms, aes(category, mean, fill=race)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Gender

```{r}
ms <- ss %>% 
  filter(gender %in% c("Male","Female")) %>%
  group_by(gender, category) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=gender)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Education

Drop the sparsest groups. 

```{r}
ms <- ss %>% 
  filter(!is.na(education)) %>%
  group_by(education, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=education)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Age

Drop the sparsest groups again. 

```{r}
ms <- ss %>% 
  filter(!is.na(age)) %>%
  group_by(age, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=age)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Children

```{r}
ms <- ss %>% 
  filter(!is.na(children)) %>%
  group_by(children, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=children)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Ethnicity

```{r}
ms <- ss %>% 
  filter(ethnicity != "") %>%
  group_by(ethnicity, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=ethnicity)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

# Factor analysis

Get eigenvalues for determining number of factors. 

```{r}
att.mat <- select(wide.attitudes, -workerid)

ev <- eigen(cor(x=att.mat)) # get eigenvalues

ap <- parallel(subject=nrow(att.mat), var=ncol(att.mat),
               rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```

It still looks like Active/Early Learning and Affection are grouping together (with a separate factor that seems to focus on physical affection perhaps?), while Rules and Respect is separate. I'm still wondering if we need to re-think the structure of the subscales. It might be that Early Learning and Affection are not fully differentiated latent theories, and that they group together into a "child development is a project" theory.

```{r}
item.levels <- c("respect parents teachers", "wait when told","children should be grateful","punish for small rules", "dont impose structure", "kids should not decide", "safe loving environment", "holding and cradling", "give children comfort", "talk about emotions", "not spoiled with too much attention","too much affection does not harm", "can learn good and bad", "learn by playing", "learn from repetetive behaviors", "reasons for rules", "learn math before school", "reading before speaking")

n.factors <- 3

af <- factanal(x=att.mat, factors = n.factors, scores = "regression")
loadings <- data.frame(af$loadings[,1:n.factors]) %>%
  mutate(item = rownames(af$loadings)) %>%
  gather(factor, loading, starts_with("Factor"))
loadings$item <- factor(loadings$item, item.levels)

labels$item <- labels$short_sent
loadings <- join(loadings, labels, by = "item")

qplot(factor, item, fill=loading, geom="tile", data = loadings) + 
  scale_fill_continuous(low="#000000", high="#FFFFFF") + 
  facet_grid(category ~ ., scales = "free_y")

qplot(factor, item, fill=loading > .4, geom="tile", data = loadings) + 
  scale_fill_solarized() + 
  facet_grid(category ~ ., scales = "free_y")
```

Merge back in subject id info. 

```{r}
a.scores <- af$scores %>%
  data.frame %>%
  mutate(workerid = as.character(wide.attitudes$workerid)) %>%
  left_join(subinfo)
```

## Factors by SES

```{r}
a.factor.names <- c("Affection and Early Learning","Rules and Respect", "Affection 2")

mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ses != "") %>%
  mutate(ses.level = cut(as.numeric(ses), c(0,3,6,10)),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(ses.level, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=ses.level)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Gender

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(gender %in% c("Male","Female")) %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(gender, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=gender)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()

```
 
## Factors by Education

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(education != "") %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(education, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=education)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Age

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(age != "") %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(age, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=age)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Children

Do you have children?

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(children = children %in% c("1","2","3","4","5","morethan5"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(children, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=children)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

How many?

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(n.children = children,
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(n.children, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=n.children)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Ethnicity

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ethnicity != "") %>%
  mutate(hispanic = ethnicity== "Hispanic",
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(hispanic, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=hispanic)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
``` 
 
## Factors by Race

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(race != "NULL") %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(race, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=race)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
``` 

# Conclusions


...