---
title: "Parenting Project Attitudes Questionnaire Uptake with Control Group"
author: "Emily & Mike"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of basic parenting values/attitudes survey.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}

rm(list=ls())

setwd("~/Desktop/parenting_proj/analysis")

knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(psych)
library(langcog)
library(dplyr)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(psych)
library(nFactors)
library(lme4)
# library(nFactors)

select <- dplyr::select # masked by MASS

theme_set(theme_bw())
```

Read in files and consolidate to the same directory. 

```{r}
files <- dir("../production-results/uptake_e3/")
d.raw <- data.frame()
answers <- data.frame()

for (f in files) {
  jf <- paste("../production-results/uptake_e3/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  # get trial type
  trial_type <- jd$answers$data$trial_type
  
  #uptake responses
  answers_id <- data.frame(
     trial= jd$answers$data$trial_number_block[trial_type == "uptake"],
     answer= jd$answers$data$answer,
     workerid = jd$WorkerId)
  answers <- bind_rows(answers, answers_id)
  
  #questionnaire and demo
  id <- data.frame(workerid = jd$WorkerId, 
                   sent = jd$answers$data$sentence[trial_type == "attitudes"],
                   rating = as.numeric(jd$answers$data$rating[trial_type == "attitudes"]) ,
                   children = jd$answers$data$children,
                   language = jd$answers$data$homelang,
                   ses = jd$answers$data$ladder,
                   gender = jd$answers$data$gender,
                   age = jd$answers$data$age,
                   education = jd$answers$data$education,
                   ethnicity = jd$answers$data$ethnicity,
                   race = as.character(jd$answers$data$race[1]),
                   reading_time_1 = jd$answers$data$target1_rt,
                   reading_time_2 = jd$answers$data$target2_rt,
                   reading_time_3 = jd$answers$data$target3_rt,
                   time_questionnaire = jd$answers$data$questionnaire_rt,
                   prior_exposure_1 = jd$answers$data$prior_exposure_1,
                   prior_exposure_2 = jd$answers$data$prior_exposure_2,
                   prior_exposure_3 = jd$answers$data$prior_exposure_3)
  d.raw <- bind_rows(d.raw, id)
}
```

```{r}
labels <- read.csv("sent_forms_e7.csv")
labels$sent <- as.character(labels$sent)

answer_key <- read.csv("uptake_key_e3.csv")
```

Clean up labels.

```{r}
d.raw$sent <- as.character(d.raw$sent)
d.raw$sent <- str_replace_all(d.raw$sent, "'", "")
d.raw$sent <- str_replace_all(d.raw$sent, "’", "")
d.raw$sent <- str_replace_all(d.raw$sent, "“", "")
d.raw$sent <- str_replace_all(d.raw$sent, "”", "")
d.raw$sent <- str_replace_all(d.raw$sent, "‘", "")
d.raw$sent <- str_replace_all(d.raw$sent, "â", "")
```

Merge. Recode uptake answers by accuracy.  

```{r}
d <- d.raw %>%
  left_join(answers) %>%
  left_join(labels) %>%
  left_join(answer_key) %>%
  mutate(answer = as.character(answer))%>%
  mutate(answer_cor = as.character(answer_cor))%>%
  mutate(acc = (answer == answer_cor))

d$acc[d$acc == "TRUE"] <- "1"
d$acc[d$acc == "FALSE"] <- "0"

d$rating[d$reverse_code == 1] <- 6 - d$rating[d$reverse_code == 1]
```

Plot demographic info.

```{r}
subinfo <- d %>%
  group_by(workerid) %>%
  select(workerid, age, ses, gender, ethnicity, education, children, language, reading_time_1, reading_time_2, reading_time_3) %>%
  distinct 
```


```{r}
subinfo$education <- factor(subinfo$education, 
                            levels = c("highSchool","someCollege","4year","someGrad","Grad"))
```

```{r}
qplot(ses, data=subinfo)
qplot(children, data=subinfo)
qplot(gender, data=subinfo)
qplot(education, data=subinfo)
qplot(age, data=subinfo)
qplot(language, data=subinfo)
qplot(ethnicity, data=subinfo)
```

# Basic analyses

Now look at mean ratings across sentences.

```{r}
ms <- d %>%
  group_by(category, instrument, short_sent, reverse_code) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(instrument, category, desc(mean)) 

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)
```

Plot attitude.

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, pch = factor(reverse_code),
      geom = "pointrange",
      data = filter(ms, instrument == "attitudes")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,6)) + 
  scale_colour_solarized()
```

Plot mean subscale scores.

```{r}
mc <- d %>%
  group_by(category) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(category, desc(mean)) 

ggplot(mc, aes(x = category, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```

# Information Uptake Analyses

Standardize ratings within participant.
```{r}
d$rating_centered <- scale(d$rating, center = TRUE, scale = FALSE)
```

Plot mean recall and generalization scores.
```{r}
d$acc <- as.numeric(d$acc)
ms <- d %>%
  group_by(q_type) %>%
  multi_boot_standard(col = "acc")

ggplot(ms, aes(x = q_type, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```


Create a data frame that has individuals' subscale scores and accuracy by question type. 

```{r}
ms <- d %>%
  group_by(workerid, q_type) %>%
  multi_boot_standard(col = "acc")

ss_rating <- d%>%
  group_by(workerid, category) %>%
  summarize(rating = mean(rating)) 

ss_acc <- d%>%
  group_by(workerid, q_type) %>%
  summarize(acc = mean(acc)) 

ss <- ss_rating %>%
  left_join(ss_acc)

```

## Plots

```{r}
ggplot(ss, aes(x = rating, y = acc, col = category)) +
  geom_jitter() + 
  geom_smooth(method="lm", se=FALSE) + 
  facet_wrap(~q_type)
```

Setting up exclusion based on reading time.

```{r}
exclude <- subinfo$workerid[subinfo$reading_time_1 < 30 | subinfo$reading_time_2 < 30 | subinfo$reading_time_3 < 30 ]
length(exclude)
qplot(subinfo$reading_time_1, binwidth = 15) + 
  geom_vline(xintercept =15, lty =2, col="red")
qplot(subinfo$reading_time_2, binwidth = 15) + 
  geom_vline(xintercept =15, lty =2, col="red")
qplot(subinfo$reading_time_3, binwidth = 15) + 
  geom_vline(xintercept =15, lty =2, col="red")
```

Exclusions.

```{r}
ggplot(filter(ss, !workerid %in% exclude), 
       aes(x = rating, y = acc, colour = category)) +
  geom_jitter() +  
  geom_smooth(method="lm", se=FALSE) + 
  facet_grid(~q_type)
```

```{r}
d.reg <- d %>%
  select(workerid, acc, q_type, trial, category, rating)%>%
  unique %>%
  spread(category, rating)
```


## Stats 


```{r}
summary(glmer(correct ~ q_type * rules_respect + 
                q_type * early_learning +
                q_type * affection +
                (1|workerid) + 
                (1|q_num), 
              data = filter(d.reg, !workerid %in% exclude), 
              family = "binomial"))
```

