---
title: "Parenting Project Attitudes Questionnaire Uptake"
author: "Emily & Mike"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of uptake experiment for parenting attitudes questionnaire. Do scores on the PAQ subscales predict uptake of experimental content compared to control content?

# Data preprocessing

Preliminaries.

```{r echo=FALSE}

rm(list=ls())

setwd("~/Desktop/parenting_proj/analysis")

knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(psych)
library(langcog)
library(dplyr)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(psych)
library(nFactors)
library(lme4)
# library(nFactors)

select <- dplyr::select # masked by MASS

theme_set(theme_bw())
```

Read in participant data.

```{r}
files <- dir("../production-results/uptake_e4/")
answers <- data.frame()
attitudes <- data.frame()
subinfo <- data.frame()

f <- files[1]

for (f in files) {
  jf <- paste("../production-results/uptake_e4/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))

  #uptake responses
  answers_id <- data.frame(
    answer= jd$answers$data$answer,
    item = jd$answers$data$item[jd$answers$data$trial_type =="uptake"],
    workerid = jd$WorkerId)
  
  answers <- bind_rows(answers, answers_id)
  
  attitudes_id <- data.frame(workerid = jd$WorkerId, 
                   sent = jd$answers$data$sentence[jd$answers$data$trial_type=="attitudes"],
                   rating = as.numeric(jd$answers$data$rating[jd$answers$data$trial_type=="attitudes"])) 
                   
  attitudes <- bind_rows(attitudes, attitudes_id)
  
  #questionnaire and demo
  subinfo_id <- data.frame(workerid = jd$WorkerId, 
                   children = jd$answers$data$children,
                   language = jd$answers$data$homelang,
                   ses = jd$answers$data$ladder,
                   gender = jd$answers$data$gender,
                   age = jd$answers$data$age,
                   education = jd$answers$data$education,
                   ethnicity = jd$answers$data$ethnicity,
                   race = as.character(jd$answers$data$race[1]),
                   rt_exp1 = jd$answers$data$target1_rt,
                   rt_exp2 = jd$answers$data$target2_rt,
                   rt_con1 = jd$answers$data$control1_rt,
                   rt_con2 = jd$answers$data$control2_rt)
  subinfo <- bind_rows(subinfo, subinfo_id)
}
```

Read in trial info and questionnaire labels.

```{r}
labels <- read.csv("sent_forms_uptake_e4.csv")
labels$sent <- as.character(labels$sent)

answer_key <- read.csv("uptake_key_e4.csv")
```

Clean up labels.

```{r}
attitudes$sent <- as.character(attitudes$sent)
attitudes$sent <- str_replace_all(attitudes$sent, "'", "")
attitudes$sent <- str_replace_all(attitudes$sent, "’", "")
attitudes$sent <- str_replace_all(attitudes$sent, "“", "")
attitudes$sent <- str_replace_all(attitudes$sent, "”", "")
attitudes$sent <- str_replace_all(attitudes$sent, "‘", "")
attitudes$sent <- str_replace_all(attitudes$sent, "â", "")
```

Plot demographic info.

```{r}
subinfo$education <- factor(subinfo$education, 
                            levels = c("highSchool","someCollege","4year","someGrad","Grad"))

qplot(ses, data=subinfo)
qplot(children, data=subinfo)
qplot(gender, data=subinfo)
qplot(education, data=subinfo)
qplot(age, data=subinfo)
qplot(language, data=subinfo)
qplot(ethnicity, data=subinfo)
```

# Questionnaire

Look at mean ratings across sentences.

```{r}
dq <- attitudes %>%
  left_join(labels) 

dq$rating[dq$reverse_code == 1] <- 6 - dq$rating[dq$reverse_code == 1]

ms <- dq %>%
  group_by(category, short_sent, reverse_code) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(category, desc(mean)) 

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)
```

Plot responses to individual questionnaire items.

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, pch = factor(reverse_code),
      geom = "pointrange",
      data = ms) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,6)) + 
  scale_colour_solarized()
```

Plot mean subscale scores.

```{r}
atts_m <- dq %>%
  group_by(category) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(category, desc(mean)) 

atts <- dq %>%
  group_by(workerid, category) %>% 
  summarise(rating = mean(rating))

ggplot(atts_m, aes(x = category, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```

# Information Uptake Analyses

Get accuracy data. 

```{r}
answers$answer <- as.character(answers$answer)
answer_key$answer_cor <- as.character(answer_key$answer_cor)

uptake <- answers %>%
  left_join(answer_key) %>%
  mutate(acc = (answer == answer_cor))%>%
  select(workerid, item, acc, q_type)

mss<- uptake%>%
  group_by(workerid, q_type) %>% 
  summarise(acc = mean(acc))

ms <- uptake %>%
  group_by(q_type) %>%
  multi_boot_standard(col = "acc")
ms
```

Plot mean uptake accuracy for control and experimental articles. Is one question type harder than the other?

```{r}
ggplot(ms, aes(x = q_type, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))

t.test(mss$acc[mss$q_type == 'con'],mss$acc[mss$q_type == 'exp'],paired=TRUE)
```

##Plots

Create a data frame that has individuals' subscale scores and accuracy by question type. 

```{r}
d <- atts %>%
  left_join(mss) 
```

```{r}
ggplot(d, aes(x = rating, y = acc, col = category)) +
  geom_jitter(height = .02, width = 0, alpha= .3) + 
  geom_smooth(method="lm", se=FALSE) + 
  facet_wrap(~q_type)
```

Setting up exclusion based on reading time.

```{r}
exclude <- subinfo$workerid[subinfo$rt_exp1 < 30 | subinfo$rt_exp2 < 30 | subinfo$rt_con1 < 30 | subinfo$rt_con2 < 30]
length(exclude)

qplot(subinfo$rt_exp1, binwidth = 15) + 
  geom_vline(xintercept =15, lty =2, col="red")
qplot(subinfo$rt_exp2, binwidth = 15) + 
  geom_vline(xintercept =15, lty =2, col="red")
qplot(subinfo$rt_con1, binwidth = 15) + 
  geom_vline(xintercept =15, lty =2, col="red")
qplot(subinfo$rt_con2, binwidth = 15) + 
  geom_vline(xintercept =15, lty =2, col="red")
```

Exclusions.

```{r}
ggplot(filter(d, !workerid %in% exclude), 
       aes(x = rating, y = acc, colour = category)) +
 geom_jitter(height = .02, width = 0, alpha= .3) + 
  geom_smooth(method="lm", se=FALSE) + 
  facet_wrap(~q_type) + 
  ylim(0,1)
```

##Psychometrics

```{r}
wide.attitudes <- d %>% 
  filter(instrument == "attitudes") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
```

```{r}
att.mat <- select(wide.attitudes, -workerid)

ev <- eigen(cor(x=att.mat)) # get eigenvalues

ap <- parallel(subject=nrow(att.mat), var=ncol(att.mat),
               rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
# plotnScree(nS)
```

```{r loadings, fig.height=3, fig.width=7, fig.env='figure*', fig.align='center', fig.pos='', fig.cap='Factor loadings for subscale items. EL = Early Learning, AA = Affection and Attachment, RR = Rules and Respect. *Indicates reverse-coded items.'}

n.factors <- 3

af <- factanal(x=att.mat, factors = n.factors, scores = "regression")
loadings <- data.frame(af$loadings[,1:n.factors]) %>%
  mutate(item = rownames(af$loadings)) %>%
  gather(factor, loading, starts_with("Factor"))

labels$item <- labels$short_sent
loadings <- left_join(loadings, labels, by = "item")

loadings$Category <- factor(loadings$category, 
                            levels = c("early_learning","affection_attachment",
                                       "rules_respect"),
                            labels = c("EL", 
                                       "AA", 
                                       "RR"))
qplot(factor, item, fill=loading, geom="tile", data = loadings) + 
  scale_fill_continuous(low="#000000", high="#FFFFFF") + 
  facet_grid(Category ~ ., scales = "free_y")
```

# Scale reliability

## Whole Scale

```{r}
wide.attitudes <- d %>% 
  filter(instrument == "attitudes") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.mat <- as.matrix(select(wide.attitudes, -workerid))
alpha(x = alpha.mat)
```

## Rules and Respect Subscale

```{r}
wide.rules_respect <- d %>% 
  filter(category == "RR") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.rr <- as.matrix(select(wide.rules_respect, -workerid))
alpha(x = alpha.rr)
```

## Affection and Attachment Subscale



```{r}
wide.affection <- d %>% 
  filter(category == "AA") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.af <- as.matrix(select(wide.affection, -workerid))
alpha(x = alpha.af)

```

## Active Learning Subscale


```{r}
wide.active_learning <- d %>% 
  filter(category == "EL") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.al <- as.matrix(select(wide.active_learning, -workerid))
alpha(x = alpha.al)
```

# Subscales by demographics

Create a data frame that has subscale scores. 
```{r}
ss <- d %>%
  filter(instrument == "attitudes")%>%
  dplyr::group_by(workerid, category) %>%
  dplyr::summarise(rating = mean(rating))

ss <- left_join(ss, subinfo)
```

correlation of subscale scores.
```{r}
ss_wide <- ss %>%
  spread(category, rating)%>%
  select(EL, AA, RR)

ctab <- cor(ss_wide)
round(ctab, 2)

```

## Stats 

Set up a dataframe for analysis with exclusions.

```{r}
d.reg <- atts %>%
  left_join(uptake)%>%
  group_by(workerid, category, acc, q_type, item)%>%
  summarise(rating = mean(rating))%>%
  spread(category, rating)

d_an <- d.reg %>%
  filter(!workerid %in% exclude)
```

```{r eval = FALSE}
summary(glmer(acc ~ q_type * rules_respect + q_type * early_learning +
                (1|workerid) +
                (1|item), 
              data = d_an, 
              family = "binomial"))
```
