---
title: "Parenting Project Attitudes Questionnaire Experiment 6"
author: "Emily & Mike"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of basic parenting values/attitudes survey.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}

rm(list=ls())

setwd("~/Desktop/parenting_proj/analysis")

knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(psych)
library(langcog)
library(dplyr)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(psych)
library(nFactors)
library(lme4)
# library(nFactors)


select <- dplyr::select # masked by MASS

theme_set(theme_bw())
```

Read in files and consolidate to the same directory. 

```{r}
files <- dir("../production-results/uptake_e1/")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("../production-results/uptake_e1/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  # clean up different tasks
  trial_type <- jd$answer$data$trial_type
  
  #parenting questionnaire 
  sent <- jd$answers$data$sentence[trial_type != "uptake"]
  rating <- as.numeric(jd$answers$data$rating[trial_type != "uptake"]) 
  
  #uptake experiment
  control_recall_1 = jd$answers$data$answer[1]
  control_recall_2 = jd$answers$data$answer[2]
  control_recall_3 = jd$answers$data$answer[3]
  control_recall_4 = jd$answers$data$answer[4]
  control_recall_5 = jd$answers$data$answer[5]
  target_generalize_1 = jd$answers$data$answer[6]
  target_generalize_2 = jd$answers$data$answer[7]
  target_generalize_3 = jd$answers$data$answer[8]
  target_generalize_4 = jd$answers$data$answer[9]
  target_generalize_5 = jd$answers$data$answer[10]
  target_recall_1 = jd$answers$data$answer[11]
  target_recall_2 = jd$answers$data$answer[12]
  target_recall_3 = jd$answers$data$answer[13]
  target_recall_4 = jd$answers$data$answer[14]
  target_recall_5 = jd$answers$data$answer[15]
  reading_time_target = jd$answers$data$target_rt[1]
  reading_time_control = jd$answers$data$control_rt[1]
  time_questionnaire = jd$answers$data$questionnaire_rt[1]
  
  
  #demographics
  race <- as.character(jd$answers$data$race[1])
  
  id <- data.frame(workerid = jd$WorkerId, 
                   sent = sent,
                   rating = rating,
                   enjoy_target = jd$answers$data$enjoy_target,
                   enjoy_control = jd$answers$data$enjoy_control,
                   reading_ease_target = jd$answers$data$reading_ease_target,
                   reading_ease_control = jd$answers$data$reading_ease_control,
                   target_recall_1 = target_recall_1,
                   target_recall_2 = target_recall_2,
                   target_recall_3 = target_recall_3,
                   target_recall_4 = target_recall_4,
                   target_recall_5 = target_recall_5,
                   target_generalize_1 = target_generalize_1,
                   target_generalize_2 = target_generalize_2,
                   target_generalize_3 = target_generalize_3,
                   target_generalize_4 = target_generalize_4,
                   target_generalize_5 = target_generalize_5,
                   control_recall_1 = control_recall_1,
                   control_recall_2 = control_recall_2,
                   control_recall_3 = control_recall_3,
                   control_recall_4 = control_recall_4,
                   control_recall_5 = control_recall_5,
                   children = jd$answers$data$children,
                   language = jd$answers$data$homelang,
                   ses = jd$answers$data$ladder,
                   gender = jd$answers$data$gender,
                   age = jd$answers$data$age,
                   education = jd$answers$data$education,
                   ethnicity = jd$answers$data$ethnicity,
                   childAgeYoung = jd$answers$data$childAgeYoung,
                   childAgeOld = jd$answers$data$childAgeOld,
                   race = race,
                   reading_time_target = reading_time_target,
                   reading_time_control = reading_time_control,
                   time_questionnaire = time_questionnaire)
  d.raw <- bind_rows(d.raw, id)
}
```

Map on question short forms so that we can use these instead. 

```{r}
labels <- read.csv("sent_forms_e7.csv")
labels$sent <- as.character(labels$sent)
```

Clean up labels.

```{r}
d.raw$sent <- as.character(d.raw$sent)
d.raw$sent <- str_replace_all(d.raw$sent, "'", "")
d.raw$sent <- str_replace_all(d.raw$sent, "’", "")
d.raw$sent <- str_replace_all(d.raw$sent, "“", "")
d.raw$sent <- str_replace_all(d.raw$sent, "”", "")
d.raw$sent <- str_replace_all(d.raw$sent, "‘", "")
d.raw$sent <- str_replace_all(d.raw$sent, "â", "")
```

Merge. Recode uptake answers by accuracy.  

```{r}
d <- left_join(d.raw, labels)
d$rating[d$reverse_code == 1] <- 6 - d$rating[d$reverse_code == 1]

d$target_generalize_1 <- str_replace(d$target_generalize_1, "b","1")
d$target_generalize_1 <- str_replace(d$target_generalize_1, "a|c","0")
d$target_generalize_2 <- str_replace(d$target_generalize_2, "a","1")
d$target_generalize_2 <- str_replace(d$target_generalize_2, "b|c","0")
d$target_generalize_3 <- str_replace(d$target_generalize_3, "b","1")
d$target_generalize_3 <- str_replace(d$target_generalize_3, "a|c","0")
d$target_generalize_4 <- str_replace(d$target_generalize_4, "c","1")
d$target_generalize_4 <- str_replace(d$target_generalize_4, "a|b","0")
d$target_generalize_5 <- str_replace(d$target_generalize_5, "c","1")
d$target_generalize_5 <- str_replace(d$target_generalize_5, "a|b","0")

d$target_recall_1 <- str_replace(d$target_recall_1, "b","1")
d$target_recall_1 <- str_replace(d$target_recall_1, "a|c","0")
d$target_recall_2 <- str_replace(d$target_recall_2, "a","1")
d$target_recall_2 <- str_replace(d$target_recall_2, "b|c","0")
d$target_recall_3 <- str_replace(d$target_recall_3, "a","1")
d$target_recall_3 <- str_replace(d$target_recall_3, "b|c","0")
d$target_recall_4 <- str_replace(d$target_recall_4, "a","1")
d$target_recall_4 <- str_replace(d$target_recall_4, "b|c","0")
d$target_recall_5 <- str_replace(d$target_recall_5, "c","1")
d$target_recall_5 <- str_replace(d$target_recall_5, "a|b","0")

d$control_recall_1 <- str_replace(d$control_recall_1, "a","1")
d$control_recall_1 <- str_replace(d$control_recall_1, "b|c","0")
d$control_recall_2 <- str_replace(d$control_recall_2, "c","1")
d$control_recall_2 <- str_replace(d$control_recall_2, "a|b","0")
d$control_recall_3 <- str_replace(d$control_recall_3, "a","1")
d$control_recall_3 <- str_replace(d$control_recall_3, "b|c","0")
d$control_recall_4 <- str_replace(d$control_recall_4, "c","1")
d$control_recall_4 <- str_replace(d$control_recall_4, "a|b","0")
d$control_recall_5 <- str_replace(d$control_recall_5, "b","1")
d$control_recall_5 <- str_replace(d$control_recall_5, "a|c","0")
```

Plot demographic info.

```{r}
subinfo <- d %>%
  group_by(workerid) %>%
  select(-short_sent, -category, -instrument, -reverse_code) %>%
  distinct 

questions <- subinfo %>%
  select(workerid, starts_with("target"), starts_with("control")) %>%
  gather(question, correct, starts_with("target"), starts_with("control")) %>%
  separate(question, c("passage","trial_type","q_num"), sep = "_") %>%
  group_by(workerid, passage, trial_type) %>%
  summarise(correct = mean(as.numeric(correct))) %>%
  unite(trialtype, passage, trial_type) %>%
  spread(trialtype, correct)

subinfo <- subinfo %>%
  select(-starts_with("target"), -starts_with("control")) %>%
  left_join(questions) %>%
  select(-sent, -rating)
```

Awful recoding. 

```{r}
subinfo$education <- factor(subinfo$education, 
                            levels = c("highSchool","someCollege","4year","someGrad","Grad"))

subinfo$gender <- str_replace_all(subinfo$gender, 
                              "female|FEMALE|F$|f$|Femal$|Females|Females","Female")
subinfo$gender <- str_replace_all(subinfo$gender, 
                                  "^male|^Male|^MALE|^M$|^m$|^Maleq|Make", "Male")
subinfo$gender <- str_replace_all(subinfo$gender, 
                                  "29|24|25|28|32|33|45", "")
subinfo$gender <- str_replace_all(subinfo$gender, 
                                  "males", "male")
subinfo$gender <- str_replace_all(subinfo$gender, " ", "")

subinfo$language <- str_replace_all(subinfo$language, "english|eNGLISH|Engliah|ENGLISH|^eng$|Enlgish", "English")
subinfo$language <- str_replace_all(subinfo$language," ", "")
subinfo$language <- str_replace_all(subinfo$language,"arabic", "Arabic")
subinfo$language <- str_replace_all(subinfo$language,"chinese", "Chinese")
subinfo$language <- str_replace_all(subinfo$language,"german", "German")
subinfo$language <- str_replace_all(subinfo$language,"tagalog", "Tagalog")

subinfo$youngestChildAge <- factor(subinfo$childAgeYoung, levels = c("","0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

subinfo$oldestChildAge <- factor(subinfo$childAgeOld, levels = c("","0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

subinfo$reading_ease_target <- factor(subinfo$reading_ease_target, levels = c("Very Difficult", "Somewhat Difficult", "Somewhat Easy", "Very Easy"))

subinfo$reading_ease_control <- factor(subinfo$reading_ease_control, levels = c("Very Difficult", "Somewhat Difficult", "Somewhat Easy", "Very Easy"))

subinfo$enjoy_target <- factor(subinfo$enjoy_target, levels = c("Very Unenjoyable", "Somewhat Unenjoyable", "Somewhat Enjoyable", "Very Enjoyable"))

subinfo$enjoy_control <- factor(subinfo$enjoy_control, levels = c("Very Unenjoyable", "Somewhat Unenjoyable", "Somewhat Enjoyable", "Very Enjoyable"))
```

```{r}
qplot(ses, data=subinfo)
qplot(children, data=subinfo)
qplot(gender, data=subinfo)
qplot(education, data=subinfo)
qplot(age, data=subinfo)
qplot(language, data=subinfo)
qplot(ethnicity, data=subinfo)
qplot(race, data=subinfo)
qplot(youngestChildAge, data=subinfo)
qplot(oldestChildAge, data=subinfo)
qplot(reading_ease_target, data=subinfo)
qplot(reading_ease_control, data=subinfo)
qplot(enjoy_target, data=subinfo)
qplot(enjoy_control, data=subinfo)

describe(subinfo$target_recall, skew=FALSE, check=FALSE)
describe(subinfo$control_recall, skew=FALSE, check=FALSE)
describe(subinfo$target_generalize, skew=FALSE, check=FALSE)
describe(subinfo$reading_time_target, skew=FALSE, check=FALSE)
describe(subinfo$reading_time_control, skew=FALSE, check=FALSE)

qplot(reading_time_target, target_recall, data=subinfo)
qplot(reading_time_target, target_generalize, data=subinfo)
qplot(reading_time_control, control_recall, data=subinfo)

```

# Basic analyses

Now look at mean ratings across sentences.

```{r}
rating_count <- table(d$rating) 
rating_count
prop.table(rating_count) 

ms <- d %>%
  group_by(category, instrument, short_sent, reverse_code) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(instrument, category, desc(mean)) 

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)

```

Plot attitude.

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, pch = factor(reverse_code),
      geom = "pointrange",
      data = filter(ms, instrument == "attitudes")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,6)) + 
  scale_colour_solarized()

```

Plot mean subscale scores.

```{r}
mc <- d %>%
  group_by(category) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(category, desc(mean)) 

ggplot(mc, aes(x = category, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```

```{r}
mcl <- d %>%
  group_by(category, workerid) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(category, desc(mean))%>%
  spread(category, mean) 
  
```

# Scale reliability

## Whole Scale

```{r}
wide.attitudes <- d %>% 
  filter(instrument == "attitudes") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.mat <- as.matrix(select(wide.attitudes, -workerid))
summary(alpha(x = alpha.mat))
```

## Rules and Respect Subscale

```{r}
wide.rules_respect <- d %>% 
  filter(category == "rules_respect") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.rr <- as.matrix(select(wide.rules_respect, -workerid))
summary(alpha(x = alpha.rr))
```

## Affection and Attachment Subscale

```{r}
wide.affection <- d %>% 
  filter(category == "affection") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.af <- as.matrix(select(wide.affection, -workerid))
summary(alpha(x = alpha.af))
```

## Active Learning Subscale

```{r}
wide.active_learning <- d %>% 
  filter(category == "active_learning") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.al <- as.matrix(select(wide.active_learning, -workerid))
summary(alpha(x = alpha.al))
```

# Information Uptake Analyses

Create a data frame that has subscale scores. 

Standardize ratings within subscale.
```{r}

ds <- d
ds$srating <- ave(ds$rating, ds$category, FUN=scale)

ss <- ds %>%
  group_by(workerid, category) %>%
  summarize(srating = mean(srating)) %>%
  spread(category, srating) %>% 
  left_join(subinfo) %>%
  gather(trial_type, correct, control_recall, target_recall, target_generalize)

ss.long <- ss %>%
  gather(subscale, srating, active_learning, affection, rules_respect)

```

## Plots


```{r}
ggplot(ss.long, aes(x = srating, y = correct, col = subscale)) +
  geom_jitter() + 
  geom_smooth(method="lm", se=FALSE) + 
  facet_wrap(~trial_type)
```

Now with some exclusions, exploratory. 

```{r}
exclude <- subinfo$workerid[subinfo$reading_time_target < 30 | subinfo$reading_time_control < 30]
length(exclude)
qplot(subinfo$reading_time_target, binwidth = 15) + 
  geom_vline(xintercept =15, lty =2, col="red")
qplot(subinfo$reading_time_control, binwidth = 15) + 
  geom_vline(xintercept =15, lty =2, col="red")
```

Replot with exclusions. 

```{r}
ggplot(filter(ss.long, !workerid %in% exclude), 
       aes(x = srating, y = correct, col = subscale)) +
  geom_jitter() + 
  geom_smooth(method="lm", se=FALSE) + 
  facet_wrap(~trial_type)
```

## Stats 

```{r}
subscales <- ds %>%
  group_by(workerid, category) %>%
  summarize(srating = mean(srating)) %>%
  spread(category, srating) 

ratings <- d %>% 
  select(workerid, starts_with("target"), starts_with("control")) %>%
  gather(question, correct, starts_with("target"), starts_with("control")) %>%
  separate(question, c("passage","trial_type","q_num"), sep = "_") %>%
  mutate(correct = as.numeric(correct), 
         q_num = as.numeric(q_num) + 
           as.numeric(factor(passage)) * 10 + 
           as.numeric(factor(trial_type)) * 100)

d.reg <- left_join(ratings, subscales) %>%
  unite(question_type, passage, trial_type)
```

Now regression. 

```{r}
summary(glmer(correct ~ question_type + 
                (1|workerid) + 
                (1|q_num), 
              data = d.reg, 
              family = "binomial"))
```

With exclusions. 

```{r}
summary(glmer(correct ~ question_type + 
                (1|workerid) + 
                (1|q_num), 
              data = filter(d.reg, !workerid %in% exclude), 
              family = "binomial"))

# check against means
filter(d.reg, !workerid %in% exclude) %>%
  group_by(question_type) %>%
  summarise(correct = mean(correct))
```

Naive interaction. 

```{r}
summary(glmer(correct ~ question_type * active_learning + 
                (1|workerid) + 
                (1|q_num), 
              data = filter(d.reg, !workerid %in% exclude), 
              family = "binomial"))
```

```{r}
summary(glmer(correct ~ question_type * affection + 
                (1|workerid) + 
                (1|q_num), 
              data = filter(d.reg, !workerid %in% exclude), 
              family = "binomial"))
```

```{r}
summary(glmer(correct ~ question_type * rules_respect + 
                (1|workerid) + 
                (1|q_num), 
              data = filter(d.reg, !workerid %in% exclude), 
              family = "binomial"))
```


```{r}
summary(glmer(correct ~ question_type * rules_respect + 
                question_type * active_learning + 
                question_type * affection + 
                (1|workerid) + 
                (1|q_num), 
              data = filter(d.reg, !workerid %in% exclude), 
              family = "binomial"))
```

The analysis suggested by stats consultant:
```{r}

fit <- lm(correct ~ question_type + active_learning + rules_respect + question_type*active_learning + question_type*rules_respect, 
              data = filter(d.reg, !workerid %in% exclude))
summary(fit) 
```

## Median Splits on Subscales.
Perform median splits on subscales.

```{r}
# rr_med <-describe(wide_ss$rules_respect)
# al_med <-describe(wide_ss$active_learning)
# a_med <-describe(wide_ss$affection)
# 
# wide_ss$rr_split[wide_ss$rules_respect <= rr_med$median] <- "low"
# wide_ss$rr_split[wide_ss$rules_respect > rr_med$median] <- "high"
# 
# wide_ss$al_split[wide_ss$active_learning <= al_med$median] <- "low"
# wide_ss$al_split[wide_ss$active_learning > al_med$median] <- "high"
# 
# wide_ss$a_split[wide_ss$affection <= a_med$median] <- "low"
# wide_ss$a_split[wide_ss$affection > a_med$median] <- "high"
# 
# describeBy(wide_ss$mean_control_recall, group=wide_ss$rr_split)
# describeBy(wide_ss$mean_target_recall, group=wide_ss$rr_split)
# describeBy(wide_ss$mean_target_generalize, group=wide_ss$rr_split)
# 
# describeBy(wide_ss$mean_control_recall, group=wide_ss$al_split)
# describeBy(wide_ss$mean_target_recall, group=wide_ss$al_split)
# describeBy(wide_ss$mean_target_generalize, group=wide_ss$al_split)
# 
# describeBy(wide_ss$mean_control_recall, group=wide_ss$a_split)
# describeBy(wide_ss$mean_target_recall, group=wide_ss$a_split)
# describeBy(wide_ss$mean_target_generalize, group=wide_ss$a_split)
```

