---
title: "A performance model for early word learning"
bibliography: parenting.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: 
    \author{{\large \bf Emily Hembacher} \\ \texttt{ehembach@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

abstract: 
    "..."

keywords:
    "Parenting attitudes; implicit theories"

output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3.5, fig.height=3, fig.crop = FALSE, 
fig.pos = "ht", fig.path='figs/',
echo=FALSE, warning=FALSE, cache=TRUE, 
message=FALSE, sanitize=TRUE)
```

```{r, libraries}
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(psych)
library(rjson)
library(tidyr)
library(psych)
library(nFactors)
library(lme4)

library(ggplot2)
library(dplyr)
library(langcog)
library(directlabels)
library(stringr)
library(magrittr)
library(readr)
library(ggrepel)
```

Child development research is constantly generating information that can be brought to bear on best-practices for parenting. For example, research on children’s learning has demonstrated that pedagogy can improve learning in some contexts and limit it in others, suggesting that allowing children to play freely and explore is critical for learning (Bonawitz et al., 2011; Buchsbaum, Gopnik, Griffiths, & Shafto, 2011). Likewise, a great deal of research has demonstrated the importance of engaging young children in elaborative conversations for language development and future academic success (Hart & Risley, 1995; Hoff, 2003; Huttenlocher, Waterfall, Vasilyeva, Vevea, & Hedges, 2010). A fundamental challenge we face is how to communicate the results of such scientific inquiry to a diverse public in a way that maximizes uptake and improves people’s daily and long-term decision making. 

One critical parameter that may mediate parenting behavior is parents’ implicit lay theories about child development and parenting. Lay theories reflect the core beliefs that people hold in different domains, which may or may not be explicitly articulated, but organize the processing of new information and decision-making (Dweck & Legget, 1988; Ong, Zaki, & Goodman, 2015). For example, people with an entity theory of personality tend to interpret people’s behaviors as stemming from fixed personality traits rather than situational factors such as needs, goals, or emotional states (Dweck, Chiu, & Hong, 1995). There are two reasons to focus on parents’ lay theories. First, parents’ lay theories might be an important explanatory factor for many of the behaviors parents engage in with their child. For example, a parent who believes that building a strong emotional bond with their baby is one of the most important goals of parenting might have more physical contact with their child than a parent who does not hold this theory. Secondly, parents’ lay theories may moderate the uptake of new information about parenting. It is well-established that people more easily encode new information that is consistent with an existing schema or mental model they hold (Bransford & Johnson, 1972). In addition, previous research has found that interventions on public health beliefs are more successful when they take into account people’s existing belief structures in the domain (Kumar et al. 2015). 

There is some evidence supporting the notion that parents’ behaviors are mediated by implicit lay theories about child development, which vary by SES and across cultures. For example, cross-cultural studies have found profound differences in how parents interact with infants; Richman, Miller & LeVine (1992) found that mothers in the Gusii community of Kenya primarily engaged with their children to soothe them when upset, but did not often speak to them with the goal of engaging or stimulating them, as did Caucasian parents in the United States. The authors attribute this to cultural conventions stemming from the belief that there is no purpose in speaking to infants as they will not understand what is being said (Richman, Miller & LeVine, 1992; LeVine, 2004).

There are also important differences in how parents within western cultures interact with their children. Numerous studies have identified SES disparities in the amount that parents talk to their children, which predicts children’s language and academic outcomes (Hoff, 2003; Huttenlocher et al. 2002). In an effort to identify the source of this disparity, Rowe (2008) discovered that parents’ knowledge of child development (as indexed by their scores on the Knowledge of Infant Development Inventory; KIDI) predicted their child-directed language, with more knowledgeable parents speaking to their children more even when controlling for the amount of speech directed at another adult. Although this study examined parents’ knowledge, and not their lay theories per se, it provides evidence that people’s domain knowledge has real consequences for their interactions with their children. 

There are other examples of parenting beliefs on which parents differ; Lareau’s (2003) theory of “concerned cultivation” suggests that higher SES parents are more likely to view their child’s development as a project that requires a great deal of coordination in the form of activities and learning experiences, while lower SES parents are more likely to view their job as keeping their children safe from harm, with the assumption that they will naturally thrive if given independence. There have also been hundreds of studies based on Baumrind’s (1971) framework that identifies parents as authoritative, authoritarian, or permissive, based on their levels of responsiveness and control in their interactions with their children. Thus, parents’ approaches to parenting appear to vary in predictable ways based on their knowledge and perceptions about children’s learning and development. 

Although these previous studies provide preliminary evidence that parents’ beliefs about parenting and child development affect their parenting behaviors, no previous research has attempted to identify the underlying theories that might organize their behavior and decision-making. Previous research has generally relied on observation of parent-child interactions or self-report of specific activities and behaviors. To our knowledge there is not an existing measure of parents’ more general attitudes about parenting and child development, which might drive behavior and predict the uptake of interventions. To address this gap, the present work establishes a self-report scale that captures adults’ lay theories about child development and parenting. We generated a questionnaire measuring the degree to which parents endorse three potential lay theories: a “rules and respect” theory, an “affection and attachment” theory, and an “early learning” theory. As an initial test of the external validity of the questionnaire, we conducted an experiment to investigate whether parents’ scores on the theory subscales would differentially predict their uptake of parenting information presented via a popular press article about children’s early learning from free play (Gopnick, 2011). We found that higher scores on the “early learning” subscale, but not the “rules and respect” subscale, predicted recall and generalization from the target article (about free play) but not a control article that was unrelated to child development. Thus, parents’ lay theories about parenting and child development as measured by our questionnaire may be a meaningful factor in parents’ behavior and information uptake.


# Experiment 1

## Methods

### Participants

### Procedure


## Results


## Discussion

```{r}
files <- dir("../production-results/uptake_e2/")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("../production-results/uptake_e2/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  # clean up different tasks
  trial_type <- jd$answer$data$trial_type
  
  #parenting questionnaire 
  sent <- jd$answers$data$sentence[trial_type != "uptake"]
  rating <- as.numeric(jd$answers$data$rating[trial_type != "uptake"]) 
  
  #uptake experiment
  control_recall_1 = as.character(jd$answers$data$answer[1])
  control_recall_2 = as.character(jd$answers$data$answer[2])
  control_recall_3 = as.character(jd$answers$data$answer[3])
  control_recall_4 = as.character(jd$answers$data$answer[4])
  control_recall_5 = as.character(jd$answers$data$answer[5])
  target_generalize_1 = as.character(jd$answers$data$answer[6])
  target_generalize_2 = as.character(jd$answers$data$answer[7])
  target_generalize_3 = as.character(jd$answers$data$answer[8])
  target_generalize_4 = as.character(jd$answers$data$answer[9])
  target_generalize_5 = as.character(jd$answers$data$answer[10])
  target_recall_1 = as.character(jd$answers$data$answer[11])
  target_recall_2 = as.character(jd$answers$data$answer[12])
  target_recall_3 = as.character(jd$answers$data$answer[13])
  target_recall_4 = as.character(jd$answers$data$answer[14])
  target_recall_5 = as.character(jd$answers$data$answer[15])
  reading_time_target = jd$answers$data$target_rt[1]
  reading_time_control = jd$answers$data$control_rt[1]
  time_questionnaire = jd$answers$data$questionnaire_rt[1]
  
  
  #demographics
  race <- as.character(jd$answers$data$race[1])
  
  id <- data.frame(workerid = jd$WorkerId, 
                   sent = sent,
                   rating = rating,
                   enjoy_target = jd$answers$data$enjoy_target,
                   enjoy_control = jd$answers$data$enjoy_control,
                   reading_ease_target = jd$answers$data$reading_ease_target,
                   reading_ease_control = jd$answers$data$reading_ease_control,
                   target_recall_1 = target_recall_1,
                   target_recall_2 = target_recall_2,
                   target_recall_3 = target_recall_3,
                   target_recall_4 = target_recall_4,
                   target_recall_5 = target_recall_5,
                   target_generalize_1 = target_generalize_1,
                   target_generalize_2 = target_generalize_2,
                   target_generalize_3 = target_generalize_3,
                   target_generalize_4 = target_generalize_4,
                   target_generalize_5 = target_generalize_5,
                   control_recall_1 = control_recall_1,
                   control_recall_2 = control_recall_2,
                   control_recall_3 = control_recall_3,
                   control_recall_4 = control_recall_4,
                   control_recall_5 = control_recall_5,
                   children = jd$answers$data$children,
                   language = jd$answers$data$homelang,
                   ses = jd$answers$data$ladder,
                   gender = jd$answers$data$gender,
                   age = jd$answers$data$age,
                   education = jd$answers$data$education,
                   ethnicity = jd$answers$data$ethnicity,
                   childAgeYoung = jd$answers$data$childAgeYoung,
                   childAgeOld = jd$answers$data$childAgeOld,
                   race = race,
                   reading_time_target = reading_time_target,
                   reading_time_control = reading_time_control,
                   time_questionnaire = time_questionnaire)
  d.raw <- bind_rows(d.raw, id)
}
```

Map on question short forms so that we can use these instead. 

```{r}
labels <- read.csv("../analysis/sent_forms_e7.csv")
labels$sent <- as.character(labels$sent)

answers <- read.csv("../analysis/uptake_key.csv")
answers$tar_gen <-as.character(answers$tar_gen)
answers$tar_rec <-as.character(answers$tar_rec)
answers$con_rec <-as.character(answers$con_rec)
```

Clean up labels.

```{r}
d.raw$sent <- as.character(d.raw$sent)
d.raw$sent <- str_replace_all(d.raw$sent, "'", "")
d.raw$sent <- str_replace_all(d.raw$sent, "’", "")
d.raw$sent <- str_replace_all(d.raw$sent, "“", "")
d.raw$sent <- str_replace_all(d.raw$sent, "”", "")
d.raw$sent <- str_replace_all(d.raw$sent, "‘", "")
d.raw$sent <- str_replace_all(d.raw$sent, "â", "")
```

Merge. Recode uptake answers by accuracy.  

```{r}
d <- left_join(d.raw, labels)
d$rating[d$reverse_code == 1] <- 6 - d$rating[d$reverse_code == 1]

d$target_generalize_1[d$target_generalize_1 != answers$tar_gen[1]] <- 0
d$target_generalize_1[d$target_generalize_1 == answers$tar_gen[1]] <- 1
d$target_generalize_2[d$target_generalize_2 != answers$tar_gen[2]] <- 0
d$target_generalize_2[d$target_generalize_2 == answers$tar_gen[2]] <- 1
d$target_generalize_3[d$target_generalize_3 != answers$tar_gen[3]] <- 0
d$target_generalize_3[d$target_generalize_3 == answers$tar_gen[3]] <- 1
d$target_generalize_4[d$target_generalize_4 != answers$tar_gen[4]] <- 0
d$target_generalize_4[d$target_generalize_4 == answers$tar_gen[4]] <- 1
d$target_generalize_5[d$target_generalize_5 != answers$tar_gen[5]] <- 0
d$target_generalize_5[d$target_generalize_5 == answers$tar_gen[5]] <- 1

d$target_recall_1[d$target_recall_1 != answers$tar_rec[1]] <- 0
d$target_recall_1[d$target_recall_1 == answers$tar_rec[1]] <- 1
d$target_recall_2[d$target_recall_2 != answers$tar_rec[2]] <- 0
d$target_recall_2[d$target_recall_2 == answers$tar_rec[2]] <- 1
d$target_recall_3[d$target_recall_3 != answers$tar_rec[3]] <- 0
d$target_recall_3[d$target_recall_3 == answers$tar_rec[3]] <- 1
d$target_recall_4[d$target_recall_4 != answers$tar_rec[4]] <- 0
d$target_recall_4[d$target_recall_4 == answers$tar_rec[4]] <- 1
d$target_recall_5[d$target_recall_5 != answers$tar_rec[5]] <- 0
d$target_recall_5[d$target_recall_5 == answers$tar_rec[5]] <- 1

d$control_recall_1[d$control_recall_1 != answers$con_rec[1]] <- 0
d$control_recall_1[d$control_recall_1 == answers$con_rec[1]] <- 1
d$control_recall_2[d$control_recall_2 != answers$con_rec[2]] <- 0
d$control_recall_2[d$control_recall_2 == answers$con_rec[2]] <- 1
d$control_recall_3[d$control_recall_3 != answers$con_rec[3]] <- 0
d$control_recall_3[d$control_recall_3 == answers$con_rec[3]] <- 1
d$control_recall_4[d$control_recall_4 != answers$con_rec[4]] <- 0
d$control_recall_4[d$control_recall_4 == answers$con_rec[4]] <- 1
d$control_recall_5[d$control_recall_5 != answers$con_rec[5]] <- 0
d$control_recall_5[d$control_recall_5 == answers$con_rec[5]] <- 1
```

Plot demographic info.

```{r}
subinfo <- d %>%
  group_by(workerid) %>%
  select(-short_sent, -category, -instrument, -reverse_code) %>%
  distinct 

questions <- subinfo %>%
  select(workerid, starts_with("target"), starts_with("control")) %>%
  gather(question, correct, starts_with("target"), starts_with("control")) %>%
  separate(question, c("passage","trial_type","q_num"), sep = "_") %>%
  group_by(workerid, passage, trial_type) %>%
  summarise(correct = mean(as.numeric(correct))) %>%
  unite(trialtype, passage, trial_type) %>%
  spread(trialtype, correct)

subinfo <- subinfo %>%
  select(-starts_with("target"), -starts_with("control")) %>%
  left_join(questions) %>%
  select(-sent, -rating)
```


```{r}
subinfo$education <- factor(subinfo$education, 
                            levels = c("highSchool","someCollege","4year","someGrad","Grad"))

subinfo$gender <- str_replace_all(subinfo$gender, 
                              "female|FEMALE|F$|f$|Femal$|Females|Females","Female")
subinfo$gender <- str_replace_all(subinfo$gender, 
                                  "^male|^Male|^MALE|^M$|^m$|^Maleq|Make", "Male")
subinfo$gender <- str_replace_all(subinfo$gender, 
                                  "29|24|25|28|32|33|45", "")
subinfo$gender <- str_replace_all(subinfo$gender, 
                                  "males", "male")
subinfo$gender <- str_replace_all(subinfo$gender, " ", "")

subinfo$language <- str_replace_all(subinfo$language, "english|eNGLISH|Engliah|ENGLISH|^eng$|Enlgish", "English")
subinfo$language <- str_replace_all(subinfo$language," ", "")
subinfo$language <- str_replace_all(subinfo$language,"arabic", "Arabic")
subinfo$language <- str_replace_all(subinfo$language,"chinese", "Chinese")
subinfo$language <- str_replace_all(subinfo$language,"german", "German")
subinfo$language <- str_replace_all(subinfo$language,"tagalog", "Tagalog")

subinfo$youngestChildAge <- factor(subinfo$childAgeYoung, levels = c("","0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

subinfo$oldestChildAge <- factor(subinfo$childAgeOld, levels = c("","0to6mo","7to12mo","1y","2y","3y","4y","5y","6y","7y","8y","9y","10y","olderthan10"))

subinfo$reading_ease_target <- factor(subinfo$reading_ease_target, levels = c("Very Difficult", "Somewhat Difficult", "Somewhat Easy", "Very Easy"))

subinfo$reading_ease_control <- factor(subinfo$reading_ease_control, levels = c("Very Difficult", "Somewhat Difficult", "Somewhat Easy", "Very Easy"))

subinfo$enjoy_target <- factor(subinfo$enjoy_target, levels = c("Very Unenjoyable", "Somewhat Unenjoyable", "Somewhat Enjoyable", "Very Enjoyable"))

subinfo$enjoy_control <- factor(subinfo$enjoy_control, levels = c("Very Unenjoyable", "Somewhat Unenjoyable", "Somewhat Enjoyable", "Very Enjoyable"))
```


```{r}
qplot(ses, data=subinfo)
qplot(children, data=subinfo)
qplot(gender, data=subinfo)
qplot(education, data=subinfo)
qplot(age, data=subinfo)
qplot(language, data=subinfo)
qplot(ethnicity, data=subinfo)
qplot(race, data=subinfo)
qplot(youngestChildAge, data=subinfo)
qplot(oldestChildAge, data=subinfo)
qplot(reading_ease_target, data=subinfo)
qplot(reading_ease_control, data=subinfo)
qplot(enjoy_target, data=subinfo)
qplot(enjoy_control, data=subinfo)
```

# Basic analyses

Now look at mean ratings across sentences.

```{r}
rating_count <- table(d$rating) 
rating_count
prop.table(rating_count) 

ms <- d %>%
  group_by(category, instrument, short_sent, reverse_code) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(instrument, category, desc(mean)) 

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)

```

Plot attitude.

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, pch = factor(reverse_code),
      geom = "pointrange",
      data = filter(ms, instrument == "attitudes")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,6)) + 
  scale_colour_solarized()

```

Plot mean subscale scores.

```{r}
mc <- d %>%
  group_by(category) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(category, desc(mean)) 

qplot(category, mean, 
      geom = "bar", stat = "identity", position = "dodge", 
      data=mc) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```

```{r}
mcl <- d %>%
  group_by(category, workerid) %>%
  multi_boot_standard(col = "rating") %>%
  arrange(category, desc(mean))%>%
  spread(category, mean) 
  
```

# Scale reliability

## Whole Scale

```{r}
wide.attitudes <- d %>% 
  filter(instrument == "attitudes") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.mat <- as.matrix(select(wide.attitudes, -workerid))
alpha(x = alpha.mat)
```

## Rules and Respect Subscale

```{r}
wide.rules_respect <- d %>% 
  filter(category == "rules_respect") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.rr <- as.matrix(select(wide.rules_respect, -workerid))
alpha(x = alpha.rr)
```

## Affection and Attachment Subscale

```{r}
wide.affection <- d %>% 
  filter(category == "affection") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.af <- as.matrix(select(wide.affection, -workerid))
alpha(x = alpha.af)

```

## Active Learning Subscale

```{r}
wide.active_learning <- d %>% 
  filter(category == "active_learning") %>%
  select(workerid, short_sent, rating) %>% 
  spread(short_sent, rating)
alpha.al <- as.matrix(select(wide.active_learning, -workerid))
alpha(x = alpha.al)
```

# Subscales by demographics

Create a data frame that has subscale scores. 
```{r}
ss <- d %>%
  group_by(workerid, category) %>%
  summarize(rating = mean(rating))

ss <- left_join(ss, subinfo)
```

## By SES

```{r}
ms <- ss %>% 
  filter(ses != "") %>%
  mutate(ses.level = cut(as.numeric(ses), c(0,3,6,10))) %>%
  group_by(ses.level, category) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=ses.level)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Race

Drop the sparsest groups. 

```{r}
ms <- ss %>% 
  filter(race != "NULL") %>%
  group_by(race, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating")
  
ggplot(ms, aes(category, mean, fill=race)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Gender

```{r}
ms <- ss %>% 
  filter(gender %in% c("Male","Female")) %>%
  group_by(gender, category) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=gender)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Education

Drop the sparsest groups. 

```{r}
ms <- ss %>% 
  filter(!is.na(education)) %>%
  group_by(education, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=education)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Age

Drop the sparsest groups again. 

```{r}
ms <- ss %>% 
  filter(!is.na(age)) %>%
  group_by(age, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=age)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## By Children

```{r}
ms <- ss %>% 
  filter(!is.na(children)) %>%
  group_by(children, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=children)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Ethnicity

```{r}
ms <- ss %>% 
  filter(ethnicity != "") %>%
  group_by(ethnicity, category) %>%
  filter(n() > 5) %>%
  multi_boot_standard(col = "rating") 

ggplot(ms, aes(category, mean, fill=ethnicity)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

# Factor analysis

Get eigenvalues for determining number of factors. 

```{r}
att.mat <- select(wide.attitudes, -workerid)

ev <- eigen(cor(x=att.mat)) # get eigenvalues

ap <- parallel(subject=nrow(att.mat), var=ncol(att.mat),
               rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```


```{r}
item.levels <- c("respect parents teachers", "wait when told","children should be grateful","punish for small rules", "dont impose structure", "kids should not decide", "safe loving environment", "holding and cradling", "give children comfort", "talk about emotions", "not spoiled with too much attention","too much affection does not harm", "can learn good and bad", "learn by playing", "learn from repetetive behaviors", "reasons for rules", "learn math before school", "reading before speaking")

n.factors <- 3

af <- factanal(x=att.mat, factors = n.factors, scores = "regression")
loadings <- data.frame(af$loadings[,1:n.factors]) %>%
  mutate(item = rownames(af$loadings)) %>%
  gather(factor, loading, starts_with("Factor"))
loadings$item <- factor(loadings$item, item.levels)

labels$item <- labels$short_sent
loadings <- join(loadings, labels, by = "item")

qplot(factor, item, fill=loading, geom="tile", data = loadings) + 
  scale_fill_continuous(low="#000000", high="#FFFFFF") + 
  facet_grid(category ~ ., scales = "free_y")

qplot(factor, item, fill=loading > .4, geom="tile", data = loadings) + 
  scale_fill_solarized() + 
  facet_grid(category ~ ., scales = "free_y")
```

Merge back in subject id info. 

```{r}
a.scores <- af$scores %>%
  data.frame %>%
  mutate(workerid = as.character(wide.attitudes$workerid)) %>%
  left_join(subinfo)
```

## Factors by SES

```{r}
a.factor.names <- c("Affection and Early Learning","Rules and Respect", "Affection 2")

mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ses != "") %>%
  mutate(ses.level = cut(as.numeric(ses), c(0,3,6,10)),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(ses.level, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=ses.level)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Gender

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(gender %in% c("Male","Female")) %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(gender, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=gender)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()

```
 
## Factors by Education

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(education != "") %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(education, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=education)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Age

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(age != "") %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(age, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=age)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Children

Do you have children?

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(children = children %in% c("1","2","3","4","5","morethan5"),
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(children, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=children)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

How many?

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(children != "") %>%
  mutate(n.children = children,
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(n.children, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=n.children)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
```

## Factors by Ethnicity

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(ethnicity != "") %>%
  mutate(hispanic = ethnicity== "Hispanic",
         factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(hispanic, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=hispanic)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
``` 
 
## Factors by Race

```{r}
mf <- a.scores %>% 
  gather(factor, score, starts_with("Factor")) %>%
  filter(race != "NULL") %>%
  mutate(factor.num = as.numeric(str_replace(factor,"Factor","")),
         factor.name = a.factor.names[factor.num]) %>%
  group_by(race, factor.name) %>%
  multi_boot_standard(col = "score") 

ggplot(mf, aes(factor.name, mean, fill=race)) +
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) + 
  scale_fill_solarized()
``` 


Alpha correlations within subscales were lower this time, perhaps because there were fewer items in each subscale (6).

The three factors are not separating out exactly as predicted, but getting closer. The main issue is that the Affection items (this time,"talk about emotions", "holding and cradling", and "safe loving environment") are loading onto the same factor as the Early Learning items. 


# Acknowledgements

This work supported by a gift from Kinedu, Inc. Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion. 

# References 

\small